### 2014-01-13 retweet_aaai.tex
20140112

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Resonation Elicits Diffusion: \\Modelling Subjectivity for Retweeting Analysis}
\author{AAAI Press\\
Association for the Advancement of Artificial Intelligence\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\
}
\maketitle
\begin{abstract}
\begin{quote}
Retweeting is the core mechanism of information diffusion on Twitter, and many factors have been proved to influence retweeting behavior, however few studies have investigated the subjective motivation of a user to retweet a message. 
Subjective nature of human is the underlying reason of diverse social behaviors including information diffusion, and subjective resonation triggered by topics and opinions similarity between tweets and users will elicit retweeting.
In this paper, in the light of psychological theory, we assume that a tweet is more likely to be retweeted by a user because of similar subjectivity, and propose a subjective model to combine both the topics and opinions to model subjectivity. 
With state-of-the-art topic model and sentiment analysis techniques, we establish subjective model by finding topics and determining opinions towards these topics from user-generated content simultaneously.
We evaluate our model in the retweeting analysis problem to verify its impact on retweeting and effectiveness in the retweeting prediction performance. 
Specifically, we demonstrate that subjective similarity is the most distinguishable feature with largest difference between retweeted and unretweeted users;
subjective model outperforms other models in rewteeting prediction; 
and features derived from subjective model give the most significant improvement over a off-the-shelf predicting model in a rewteeting classification framework.
\end{quote}
\end{abstract}

\noindent Congratulations on having a paper selected for inclusion in an AAAI Press proceedings or technical report! This document details the requirements necessary to get your accepted paper published using \LaTeX{}. If you are using Microsoft Word, instructions are provided in a different document. If you want to use some other formatting software, you must obtain permission from AAAI Press first.

The instructions herein are provided as a general guide for experienced \LaTeX{} users who would like to use that software to format their paper for an AAAI Press publication or report. If you are not an experienced \LaTeX{} user, do not use it to format your paper. AAAI cannot provide you with support and the accompanying style files are \textbf{not} guaranteed to work. If the results you obtain are not in accordance with the specifications you received, you must correct your source file to achieve the correct result.

These instructions are generic. Consequently, they do not include specific dates, page charges, and so forth. Please consult your specific written conference instructions for details regarding your submission. Please review the entire document for specific instructions that might apply to your particular situation. All authors must comply with the following:

\begin{itemize}
\item You must use the latest AAAI Press \LaTeX{} macro.
\item Download the author kit.
\item Complete, sign, and return by the deadline the AAAI copyright form (proceedings authors) or distribution license (technical report authors).
\item Read and format your paper source and PDF according to the formatting instructions for authors.
\item Submit your electronic files and abstract using our electronic submission form \textbf{on time.}
\item Submit your copyright form, and any required page or formatting charges to AAAI Press so that they are received by the deadline.
\item Check every page of your paper before submitting it.
\end{itemize}

\section{Copyright}
All papers submitted for publication by AAAI Press must be accompanied by a valid signed copyright form or, in the case of technical reports, by a valid signed permission to distribute form. There are no exceptions to this requirement. You must send us the original version of this form. However, to meet the deadline, you may fax (1-650-321-4457) or scan and e-mail the form (pubforms14@aaai.org) to AAAI by the submission deadline, and then mail the original via postal mail to the AAAI office. \textbf{If you fail to send in a signed copyright or permission form, your paper will not be published.} You will find PDF versions of the AAAI copyright and permission to distribute forms in the author kit.

\section{Formatting Requirements in Brief}
We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices. AAAI imposes some requirements on your source and PDF files that must be followed. Most of these requirements are based on our efforts to standardize conference manuscript properties and layout. These requirements are as follows, and all papers submitted to AAAI for publication must comply:

\begin{itemize}
\item Your .tex file must compile in PDF\LaTeX{} --- \textbf{ no .ps or .eps figure files.}
\item All fonts must be embedded in the PDF file --- \textbf{ this includes your figures.}
\item Modifications to the style sheet (or your document) in an effort to avoid extra page charges are NOT allowed.
\item No type 3 fonts may be used (even in illustrations).
\item Your title must follow US capitalization rules.
\item \LaTeX{} documents must use the Times or Nimbus font package (do not use Computer Modern for the text of your paper).
\item No \LaTeX{} 209 documents may be used or submitted.
\item Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or removed from the document (even if they are in a graphics file embedded in the document). 
\item Two-column format in AAAI style is required for all papers.
\item The paper size for final submission must be US letter. No exceptions.
\item The source file must exactly match the PDF.
\item The document margins must be as specified in the formatting instructions.
\item The number of pages and the file size must be as specified for your event.
\item No document may be password protected.
\item Neither the PDFs nor the source may contain any embedded links or bookmarks.
\item Your source and PDF must not have any page numbers, footers, or headers.
\item Your PDF must be compatible with Acrobat 5 or higher.
\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" command) .
\end{itemize}

If you do not follow the above requirements, it is likely that we will be unable to publish your paper.

\section{What Files to Submit}
You must submit the following items to ensure that your paper is published:
\begin{itemize}
\item A fully-compliant PDF file.
\item Your  \LaTeX{}  source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file). The only exception is the bibliography, which you may include separately. Your source must compile on our system, which includes the standard \LaTeX{} support files.
\item All your graphics files.
\item The \LaTeX{}-generated files (e.g. .aux and .bib file, etc.) for your compiled source.
\item All the nonstandard style files (ones not commonly found in standard \LaTeX{} installations) used in your document (including, for example, old algorithm style files). If in doubt, include it.
\end{itemize}

Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you may incur late fees).   \textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros. Accompanying this source file, you must also supply any nonstandard (or older) referenced style files and all your referenced graphics files.

Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution. Place your PDF and source files in a single tar, zipped, gzipped, stuffed, or compressed archive. Name your source file with your last (family) name.

\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, and so forth.  A shell script (created by an AAAI member --- it might not work without modification on your system) that might help you create the \LaTeX{} source package is included in the Author Kit.

\section{Using \LaTeX{} to Format Your Paper}

The latest version of the AAAI style file is available on AAAI's website. Download this file and place it in a file named ``aaai.sty" in the \TeX\ search path. Placing it in the same directory as the paper should also work. You must download the latest version of the complete author kit so that you will have the latest instruction set.

\subsection{Document Preamble}

In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection. This command set-up is for three authors. Add or subtract author and address lines as necessary, and uncomment the portions that apply to you. In most instances, this is all you need to do to format your paper in the Times font. The helvet package will cause Helvetica to be used for sans serif, and the courier package will cause Courier to be used for the typewriter font. These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).

Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper. If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers). The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.

\begin{quote}
\begin{small}
\textbackslash documentclass[letterpaper]{article}\\
\% \textit{Required Packages}\\
\textbackslash usepackage\{aaai\}\\
\textbackslash usepackage\{times\}\\
\textbackslash usepackage\{helvet\}\\
\textbackslash usepackage\{courier\}\\
\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{PDFINFO for PDF\LaTeX{}}\\
\% Uncomment and complete the following for metadata (your paper must compile with PDF\LaTeX{})\\
\textbackslash pdfinfo\{\\
/Title (Input Your Paper Title Here)\\
/Author (John Doe, Jane Doe)\\
/Keywords (Input your paper's keywords in this optional area)\\
\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Section Numbers}\\
\% Uncomment if you want to use section numbers\\
\% and change the 0 to a 1 or 2\\
\% \textbackslash setcounter\{secnumdepth\}\{0\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Title, Author, and Address Information}\\
\textbackslash title\{Title\}\\
\textbackslash author\{Author 1 \textbackslash and Author 2\textbackslash\textbackslash \\ 
Address line\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash \\
\textbackslash And\\
Author 3\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash\\ Address line\}\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{Body of Paper Begins}\\
\textbackslash begin\{document\}\\
\textbackslash maketitle\\
...\\
\%\%\%\%\%\%\%\%\%\%\\
\% \textit{References and End of Paper}\\
\textbackslash bibliography\{Bibliography-File\}\\
\textbackslash bibliographystyle\{aaai\}\\
\textbackslash end\{document\}
\end{small}
\end{quote}

\subsection{Inserting Document Metadata with \LaTeX{}}
PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately. \textbf{Document Metadata  for Author and Title are REQUIRED.}

If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them. The epstopdf package will usually work for eps files. You will need to convert your ps files to PDF however.

\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata. The data in the metadata must be completely plain ascii. It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands. Type the title exactly as it appears on the paper (minus all formatting). Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma. You may also include keywords in the Keywords field.

\subsection{Preparing Your Paper}

After the preamble above, you should prepare your paper as follows:

\begin{quote}
\begin{small}
\textbackslash begin\{document\}\\
\textbackslash maketitle\\
...\\
\textbackslash bibliography\{Bibliography-File\}\\
\textbackslash bibliographystyle\{aaai\}\\
\textbackslash end\{document\}\\
\end{small}
\end{quote}
\subsection{Incompatible Packages}
The following packages are incompatible with aaai.sty and/or aaai.bst and must not be used (this list is not exhaustive --- there are others as well):
\begin{itemize}
\item hyperref
\item natbib
\item geometry
\item titlesec
\item layout
\item caption
\item titlesec
\item T1 fontenc package (install the CM super fonts package instead)
\end{itemize}

\subsection{Illegal Commands}
The following commands may not be used in your paper:
\begin{itemize}
\item \textbackslash input
\item \textbackslash vspace (when used before or after a section or subsection)
\item \textbackslash addtolength 
\item \textbackslash columnsep
\item \textbackslash top margin (or text height or addsidemargin or even side margin)
\end{itemize}

\subsection{Paper Size, Margins, and Column Width}
Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
\begin{itemize}
\item Top margin: .75 inches
\item Left margin: .75 inches
\item Right margin: .75 inches
\item Bottom margin: 1.25 inches
\end{itemize}

The default paper size in most installations of \LaTeX{} is A4. However, because we require that your electronic paper be formatted in US letter size, you will need to alter the default for this paper to US letter size. Assuming you are using the 2e version of \LaTeX{}, you can do this by including the [letterpaper] option at the beginning of your file: 
\textbackslash documentclass[letterpaper]{article}.

This command is usually sufficient to change the format. Sometimes, however, it may not work. Use PDF\LaTeX{} and include
\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}
in your preamble.

\textbf{Do not use the Geometry package to alter the page size.} Use of this style file alters aaai.sty and will result in your paper being rejected.

\subsubsection{Column Width and Margins.}
To ensure maximum readability, your paper must include two columns. Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns. The aaai.sty file will automatically create these columns for you.

\subsection{Overlength Papers}
If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods. Next,  shrink the size of your graphics. Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment. If these two methods don't work, you may minimally use the following. For floats (tables and figures), you may minimally reduce \textbackslash floatsep, \textbackslash textfloatsep, \textbackslash abovecaptionskip, and \textbackslash belowcaptionskip. For mathematical environments, you may minimally reduce \textbackslash abovedisplayskip, \textbackslash belowdisplayskip, and \textbackslash arraycolsep. You may also alter the size of your bibliography by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
right before the bibliography.

Commands that alter page layout are forbidden. These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive). If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee. Other commands that are questionable and may cause your paper to be rejected include  \textbackslash parindent, and \textbackslash parskip. Commands that alter the space between sections are also questionable. The title sec package is not allowed. Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted. Before using every trick you know to make your paper a certain length, try reducing the size of your graphics or cutting text instead or (if allowed) paying the extra page charge. It will be cheaper in the long run.

\subsection{Figures}
Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use the .gif (the resolution is too low), .ps, or .eps file format for your figures.

When you include your figures, you must crop them \textbf{outside} of \LaTeX{}. The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear when page numbers are applied or color space is standardized.

\subsection{Type Font and Size}
Your paper must be formatted in Times Roman or Nimbus. We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface. Sans serif, when used, should be Courier. Use Symbol or Lucida or Computer Modern for \textit{mathematics only. }

Do not use type 3 fonts for any portion of your paper, including graphics. Type 3 bitmapped fonts are designed for fixed resolution printers. Most print at 300 dpi even if the printer resolution is 1200 dpi or higher. They also often cause high resolution imagesetter devices and our PDF indexing software to crash. Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts. Files containing those fonts (even in graphics) will be rejected.

Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts. The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e. (Note that papers formatted in this way will still use Computer Modern for the mathematics. To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")

If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader. The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document. If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.

The default size for your type should be ten-point with twelve-point leading (line spacing). Start all pages (except the first) directly under the top margin. (See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.

\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}

If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts. They are available without charge from the American Mathematical Society:
http://www.ams.org/tex/type1-fonts.html.

\subsection{Title and Authors}
Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading). This style is called ``mixed case." Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading). (If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.

\subsubsection{Formatting Author Information}
Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display. For several authors from the same institution, use \textbackslash and:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1 \textbackslash and  ...  \textbackslash and Author \textit{n}\textbackslash \textbackslash  \\
Address line \textbackslash \textbackslash ~... \textbackslash \textbackslash ~Address line\}
\end{small}
\end{quote}

\noindent If the names do not fit well on one line use:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1\}\textbackslash \textbackslash \\ \{\textbackslash bf Author 2\}\textbackslash \textbackslash ~ 
... \textbackslash \textbackslash ~\{\textbackslash bf Author \textit{n}\}\textbackslash \textbackslash \\
Address line \textbackslash \textbackslash ~ ... \textbackslash \textbackslash ~ Address line\}
\end{small}
\end{quote}

\noindent For authors from different institutions, use \textbackslash And:

\begin{quote}
\begin{small}
\textbackslash author\{Author 1\textbackslash \textbackslash ~ Address line \textbackslash \textbackslash ~...  \textbackslash \textbackslash ~ Address line
\textbackslash And  ...  
\textbackslash And
Author \textit{n}\textbackslash \textbackslash \\ Address line\textbackslash \textbackslash ~
... \textbackslash \textbackslash ~
Address line\}
\end{small}
\end{quote}

\noindent To start a separate ``row" of authors, use \textbackslash AND:
\begin{quote}
\begin{small}
\textbackslash author\{Author 1\textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
\textbackslash AND\\
Author 2 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
\textbackslash And\\
Author 3 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\\}
\end{small}
\end{quote}

\noindent If the title and author information does not fit in the area allocated, place
\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
after the \textbackslash documentclass line where \{\textit{height}\} is something like 2.5in.

\subsection{\LaTeX{} Copyright Notice}
The copyright notice automatically appears if you use aaai.sty. If you are creating a technical report, it is not necessary to include this notice. You may disable the copyright line using the \verb+\+nocopyrightcommand. To change the entire text of the copyright slug, use:
\textbackslash copyrighttext \{\emph{text}\}.
Either of these must appear before \textbackslash maketitle. Please be advised, however, that \textit{if you disable or change the copyright line and transfer of copyright is required, your paper will not be published.}

\subsection{Credits}
Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
For example:
\begin{quote}
\begin{small}
\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
 supported by everybody.\}\}
\end{small}
\end{quote}
Multiple \textbackslash thanks commands can be given. Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document. Note that the \textbackslash thanks command is fragile. You will need to use \textbackslash protect.

Please do not include \textbackslash pubnote commands in your document.

\subsection{Abstract}
The abstract must be placed at the beginning of the first column, indented ten points from the left and right margins. The title “Abstract” should appear in ten-point bold type, centered above the body of the abstract. The abstract should be set in nine-point type with ten-point leading. This concise, one-paragraph summary should describe the general thesis and conclusion of your paper. A reader should be able to learn the purpose of the paper and the reason for its importance from the abstract. The abstract should be no more than two hundred words in length. (Authors who are submitting short one- or two-page extended extracts should provide a short abstract of only a sentence or so.) \textbf{Do not include references in your abstract!}

\subsection{Page Numbers}

Do not \textbf{ever} print any page numbers on your paper.

\subsection{Text }
The main body of the paper must be formatted in ten-point with twelve-point leading (line spacing).

\subsection{Citations}
Citations within the text should include the author's last name and year, for example (Newell 1980). Append lower-case letters to the year in cases of ambiguity. Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992). In the case of four or more authors, list only the first author, followed by et al. (Ford et al. 1997).

\subsection{Extracts}
Long quotations and extracts should be indented ten points from the left and right margins.

\begin{quote}
This is an example of an extract or quotation. Note the indent on both sides. Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.

\end{quote}

\subsection{Footnotes}
Avoid footnotes as much as possible; they interrupt the reading of the text. When essential, they should be consecutively numbered throughout with superscript Arabic numbers. Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.

\subsection{Headings and Sections}
When necessary, headings should be used to separate major sections of your paper. Remember, you are writing a short paper, not a lengthy book! An overabundance of headings will tend to make your paper look more like an outline than a paper.

First-level heads should be twelve-point Times Roman bold type, mixed case (initial capitals followed by lower case on all words except articles, conjunctions, and prepositions, which should appear entirely in lower case), with fifteen-point leading, centered, with one blank line preceding them and three additional points of leading following them. Second-level headings should be eleven-point Times Roman bold type, mixed case, with thirteen-point leading, flush left, with one blank line preceding them and three additional points of leading following them. Do not skip a line between paragraphs. Third-level headings should be run in with the text, ten-point Times Roman bold type, mixed case, with twelve-point leading, flush left, with six points of additional space preceding them and no additional points of leading following them.

\subsubsection{Section Numbers}
The use of section numbers in AAAI Press papers is optional. To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2. Section numbers should not be used in short poster papers.

\subsubsection{Section Headings.}
Sections should be arranged and headed as follows:

\subsubsection{Acknowledgments.}
The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish. Please acknowledge other contributors, grant support, and so forth, in this section. Do not put acknowledgments in a footnote on the first page. If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back. Please try to limit acknowledgments to no more than three sentences.

\subsubsection{Appendices.}
Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.

\subsubsection{References}
The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page). A sample list of references is given later on in these instructions. Please use a consistent format for references. Poorly prepared or sloppy references reflect badly on the quality of your paper and your research. Please prepare complete and accurate citations.

\subsection{Illustrations and Figures}
Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed. Do not group them together at the end of the paper. If placed at the top or bottom of the paper, illustrations may run across both columns. Figures must not invade the top, bottom, or side margin areas. Figures must be inserted using the \textbackslash usepackage\{graphicx\}. Number figures sequentially, for example, figure 1, and so on.

The illustration number and caption should appear under the illustration. Labels, and other text in illustrations must be at least nine-point type.

\subsubsection{Low-Resolution Bitmaps.}
You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed. If they are color, they will become an indecipherable mess when converted to black and white. This is always the case with gif files, which should never be used. The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels. You can also enlarge files by manipulating them in software such as PhotoShop. Your figures should be a minimum of 266 dpi when incorporated into your document.

\subsubsection{\LaTeX{} Overflow.}
\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin. If this happens, you need to scale the figure or table down, or reformat the equation. Check your log file! You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}). If you don't, the overflow text will simply be eliminated. \textbf{Nothing is permitted to intrude into the margins.}

\subsubsection{Using Color.}
Your paper will be printed in black and white and grayscale. Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document. Of course, any reference to color will be indecipherable to your reader.

\subsubsection{Drawings.}
We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations. Do not use Microsoft Publisher. These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas. Shading should be 133 lines per inch if possible. Use Times Roman or Helvetica for all figure call-outs. \textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt. Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.

\subsubsection{Photographs and Images.}
Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 266 dpi. Do not prescreen images.

\subsubsection{Resizing Graphics.}
Resize your graphics \textbf{before} you include them with LaTeX. You may \textbf{not} use trim or clip options as part of your \textbackslash includgraphics command. Resize the media box of your PDF using a graphics program instead.

\subsubsection{Fonts in Your Illustrations}
You must embed all fonts in your graphics before including them in your LaTeX document.

\subsection{References} 
The aaai.sty file includes a set of definitions for use in formatting references with BibTeX. These definitions make the bibliography style fairly close to the one specified below. To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the author kit on the AAAI web site. Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:

\begin{quote}
\begin{small}
\textbackslash bibliographystyle\{aaai\}
\textbackslash bibliography\{bibfile1,bibfile2,...\}
\end{small}
\end{quote}

The list of files in the \textbackslash  bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).

The following commands are available for your use in citing references:
\begin{quote}
\begin{small}
\textbackslash cite: Cites the given reference(s) with a full citation. This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\\
\textbackslash shortcite: Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\\
\textbackslash citeauthor: Cites the given reference(s) with just the author name(s) and no parentheses.\\
\textbackslash citeyear: Cites the given reference(s) with just the date(s) and no parentheses.
\end{small}
\end{quote}

\textbf{Warning:} The aaai.sty file is incompatible with the hyperref and natbib packages. If you use either, your references will be garbled.

Formatted bibliographies should look like the following examples.

\smallskip \noindent \textit{Book with Multiple Authors}\\
Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.

\smallskip \noindent \textit{Journal Article}\\
Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.

\smallskip \noindent \textit{Magazine Article}\\
Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.

\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
Clancey, W. J. 1983b. Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education. In Proceedings of the Eighth International Joint Conference on Artificial Intelligence, 556--560. Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.

\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.

\smallskip \noindent \textit{University Technical Report}\\
Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.

\smallskip \noindent \textit{Dissertation or Thesis}\\
Clancey, W. J. 1979b. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.

\smallskip \noindent \textit{Forthcoming Publication}\\
Clancey, W. J. 1986a. The Engineering of Qualitative Models. Forthcoming.

\section{Producing Reliable PDF\\Documents with \LaTeX{}}
Generally speaking, PDF files are platform independent and accessible to everyone. When creating a paper for a proceedings or publication in which many PDF documents must be merged and then printed on high-resolution PostScript RIPs, several requirements must be met that are not normally of concern. Thus to ensure that your paper will look like it does when printed on your own machine, you must take several precautions:
\begin{itemize}
\item Use type 1 fonts (not type 3 fonts)
\item Use only standard Times, Nimbus, and CMR font packages (not fonts like F3 or fonts with tildes in the names or fonts---other than Computer Modern---that are created for specific point sizes, like Times\~{}19) or fonts with strange combinations of numbers and letters
\item Embed all fonts when producing the PDF
\item Do not use the [T1]{fontenc} package (install the CM super fonts package instead)
\end{itemize}

\subsection{Creating Output Using PDF\LaTeX{} Is Required}
By using the PDF\TeX{} program instead of straight \LaTeX{} or \TeX{}, you will probably avoid the type 3 font problem altogether (unless you use a package that calls for metafont). PDF\LaTeX{} enables you to create a PDF document directly from \LaTeX{} source. The one requirement of this software is that all your graphics and images must be available in a format that PDF\LaTeX{} understands (normally PDF).

PDF\LaTeX{}'s default is to create documents with type 1 fonts. If you find that it is not doing so in your case, it is likely that one or more fonts are missing from your system or are not in a path that is known to PDF\LaTeX{}.

\subsubsection{dvipdf Script}
Scripts such as dvipdf which ostensibly bypass the Postscript intermediary should not be used since they generally do not instruct dvips to use the config.pdf file.

\subsubsection{dvipdfm}
Do not use this dvi-PDF conversion package if your document contains graphics (and we recommend you avoid it even if your document does not contain graphics).

\subsection{Ghostscript}
\LaTeX{} users should not use GhostScript to create their PDFs.

\subsection{Graphics}
If you are still finding type 3 fonts in your PDF file, look at your graphics! \LaTeX{} users should check all their imported graphics files as well for font problems.

\section{Proofreading Your PDF}
Please check all the pages of your PDF file. Is the page size A4? Are there any type 3, Identity-H, or CID fonts? Are all the fonts embedded? Are there any areas where equations or figures run into the margins? Did you include all your figures? Did you follow mixed case capitalization rules for your title? Did you include a copyright notice? Do any of the pages scroll slowly (because the graphics draw slowly on the page)? Are URLs underlined and in color? You will need to fix these common errors before submitting your file.

\section{Improperly Formatted Files }
In the past, AAAI has corrected improperly formatted files submitted by the authors. Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb. Consequently, if your file is improperly formatted, it may not be possible to include your paper in the publication. If time allows, however, you will be notified via e-mail (with a copy to the program chair) of the problems with your file and given the option of correcting the file yourself (and paying a late fee) or asking that AAAI have the file corrected for you, for an additional fee. If you opt to correct the file yourself, please note that we cannot provide you with any additional advice beyond that given in your packet. Files that are not corrected after a second attempt will be withdrawn.

\subsection{\LaTeX{} 209 Warning}
If you use \LaTeX{} 209 we will not be able to publish your paper. Convert your paper to \LaTeX{}2e.

\section{Naming Your Electronic File}
We request that you name your \LaTeX{} source file with your last name (family name) so that it can easily be differentiated from other submissions. If you name your files with the name of the event or ``aaai" or ``paper" or ``camera-ready" or some other generic or indecipherable name, you bear all risks of loss --- it is extremely likely that your file may be overwritten.

\section{Submitting Your Electronic Files to AAAI}
Submitting your files to AAAI is a two-step process. It is explained fully in the author registration and submission instructions. Please consult this document for details on how to submit your paper.

\section{Inquiries} 
If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below. If you have technical questions about implementation of the aaai style file, please contact an expert at your site. We do not provide technical support for \LaTeX{} or any other software package. To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.

\begin{quote}
\noindent AAAI Press\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\ 
\textit{Telephone:} (650) 328-3123\\ 
\textit{E-mail:} See the submission instructions for your particular conference or event.
\end{quote}

\section{Additional Resources}
\LaTeX{} is a difficult program to master. If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems. (It was written for another purpose, but it has general application as well). It is available at www.ctan.org in the tex-archive.

\section{ Acknowledgments}
AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton. We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document  --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.

The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press. Bibliography style changes were added by Sunil Issar. \verb+\+pubnote was added by J. Scott Penberthy. George Ferguson added support for printing the AAAI copyright slug. Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.

\bigskip
\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!

\end{document}

### 2014-01-20 retweet_aaai.tex
First version

@@
 \usepackage{courier}
+\usepackage{url}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{latexsym}
+\usepackage{amssymb}
+\usepackage{multirow}
+\newtheorem{definition}{Definition}
 \frenchspacing
@@
 \title{Resonation Elicits Diffusion: \\Modelling Subjectivity for Retweeting Analysis}
-\author{AAAI Press\\
-Association for the Advancement of Artificial Intelligence\\
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\
-}
+%\author{AAAI Press\\
+%Association for the Advancement of Artificial Intelligence\\
+%2275 East Bayshore Road, Suite 160\\
+%Palo Alto, California 94303\\
+%}
 \maketitle
@@
 \begin{quote}
-Retweeting is the core mechanism of information diffusion on Twitter, and many factors have been proved to influence retweeting behavior, however few studies have investigated the subjective motivation of a user to retweet a message.
-Subjective nature of human is the underlying reason of diverse social behaviors including information diffusion, and subjective resonation triggered by topics and opinions similarity between tweets and users will elicit retweeting.
-In this paper, in the light of psychological theory, we assume that a tweet is more likely to be retweeted by a user because of similar subjectivity, and propose a subjective model to combine both the topics and opinions to model subjectivity.
-With state-of-the-art topic model and sentiment analysis techniques, we establish subjective model by finding topics and determining opinions towards these topics from user-generated content simultaneously.
-We evaluate our model in the retweeting analysis problem to verify its impact on retweeting and effectiveness in the retweeting prediction performance. 
-Specifically, we demonstrate that subjective similarity is the most distinguishable feature with largest difference between retweeted and unretweeted users;
-subjective model outperforms other models in rewteeting prediction; 
-and features derived from subjective model give the most significant improvement over a off-the-shelf predicting model in a rewteeting classification framework.
+Retweeting is the core mechanism of information diffusion on Twitter.
+User modelling has been proved effective in  retweeting behavior analysis, however none studies have investigated the subjectivity of users.
+In this paper, we propose a subjective model by combining both topics of interest and opinions to model users, and demonstrate that a user is more likely to retweet a message because of subjective similarity.
+We define a novel weighting function to measure the subjective similarity. 
+By means of ANOVA test, the subjective similarity is verified to be correlated with  retweeting behavior;  
+we compare our model with other content-based models in retweeting prediction and results show that our model  outperforms other models for predicting retweeting behavior; 
+when combining with other factors, subjective similarities give significant improvement over a off-the-shelf predicting model.
 \end{quote}
@@
 
-\noindent Congratulations on having a paper selected for inclusion in an AAAI Press proceedings or technical report!
-This document details the requirements necessary to get your accepted paper published using \LaTeX{}.
-If you are using Microsoft Word, instructions are provided in a different document.
-If you want to use some other formatting software, you must obtain permission from AAAI Press first.
+\section{Introduction}
+\label{introduction}
+\noindent Microblogging has become a center of attention in the area of social networking due to the amount of users it has attracted and the volume of messages it produces daily. 
+Microblogging services such as Twitter appear to play an important role in the process of information dissemination on the Internet, making it possible for messages to spread virally in a matter of minutes.
+Retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message(tweet) \cite{Jenders:2013APV}. 
+Actually almost a quarter of the tweets are retweeted from others \cite{conf/cikm/YangGCTLZS10}. 
+Understanding how retweeting behavior works can help explaining information dissemination on Twitter.
 
-The instructions herein are provided as a general guide for experienced \LaTeX{} users who would like to use that software to format their paper for an AAAI Press publication or report.
-If you are not an experienced \LaTeX{} user, do not use it to format your paper.
-AAAI cannot provide you with support and the accompanying style files are \textbf{not} guaranteed to work.
-If the results you obtain are not in accordance with the specifications you received, you must correct your source file to achieve the correct result.
+Studies have tried to find factors that influence whether a tweet will be retweeted \cite{Boyd2010,Kwak:2010TSN,Suh2010}. 
+Users receive thousands of tweets on different topics every day, whether a tweet will be retweeted will depend on the subjective choice of users. 
+From the point of a user, retweeting is a process that includes reading the tweet, estimating the content and deciding to share.
+The crucial part is to estimate whether a tweet contains information interesting to the user who might find it worthy to be shared.
+Therefore modelling the motivation of users provides an important perspective for retweeting behavior analysis. 
+This research is motivated by a desire to understand what drives users of social networks to disseminate information they come across.
 
-These instructions are generic.
-Consequently, they do not include specific dates, page charges, and so forth.
-Please consult your specific written conference instructions for details regarding your submission.
-Please review the entire document for specific instructions that might apply to your particular situation.
-All authors must comply with the following:
+Previous studies on retweeting behavior have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{conf/icwsm/MacskassyM11,conf/wsdm/FengW13}. 
+Specifically, researchers have tried to model users from four types of information:
+profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Who you tweet}") \cite{Pennacchiotti:icwsm11}.
+Subjective initiative nature of human determines that his behavior pattern is subjectivity driven. 
+According to theory of Biased Assimilation, people are prone to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
+Therefore, we can understand the underlying reason why a user retweet a message by modelling the subjectivity of the user.
 
+Twitter has become a platform where different opinions are presented and exchanged by allowing users publish subjective messages on topics they are interested in. 
+Therefore subjectivity of a user is encoded in the millions of User-Generated Content(UGC) on Twitter. 
+In this study we explore the big text data with state-of-the-art Natural Language Processing techniques to model the subjectivity of users, and investigate whether the subjective model could benefit the retweeting behavior analysis.
+Intuitively, we put forwards that subjectivity can be represented as topics and opinions articulated in the tweets generated by users on Twitter. 
+And the probabilty a user retweets a message could be evaluated by measuring the subjective similarity between the tweet and the subjective model of the user.
+
+\section{Subjective Model}
+\label{subjectivemodel}
+
+Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historic behaviors and remarks \cite{Engbert2007}. 
+Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their languistic content \cite{stein2005subjectivity}.
+How to computationally model subjectivity of a user is still a challenging problem for many applications. 
+The advent of online social networking such as Twitter has given a new layout to the challenge.  
+Twitter allows users to show their personal subjectivity by publishing short messages, which give researchers resources to model the subjectivity of users.
+First of all, we give an formal definition for subjective model under context of Twitter.
+
+\subsection{Definition}
+\label{definition}
+
+Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of directed relationships between users.
+For each user $ u \in V $, there is a tweets collection $ M_{u} $ denotes his message history.
+We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ for evaluating their opinions towards these topics.
+For the ``subjectivity'' of a user $ u $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
+\begin{definition}[Subjective Model]
+The subjective model $ P \left( u \right) $ of a user $u \in V $, is the combination of a set of topics $\left\lbrace  t_{i} \left( i \in \lbrace1 \cdots n \rbrace \right)  \right\rbrace $ the user talks about in a topic space $T$ and the user's opinion $o_{i}$ towards each topic $ t_{i} $.
+\begin{equation}
+\label{usermodel}
+P \left( u \right) = \lbrace \left( t_{i}, w_{u} \left( t_{i} \right), d_{u,t_{i}} \left( o_{i} \right) \right) \,\vert  t_{i} \in T, \, o_{i} \in O \rbrace
+\end{equation}
+where:
 \begin{itemize}
-\item You must use the latest AAAI Press \LaTeX{} macro.
-\item Download the author kit.
-\item Complete, sign, and return by the deadline the AAAI copyright form (proceedings authors) or distribution license (technical report authors).
-\item Read and format your paper source and PDF according to the formatting instructions for authors.
-\item Submit your electronic files and abstract using our electronic submission form \textbf{on time.}
-\item Submit your copyright form, and any required page or formatting charges to AAAI Press so that they are received by the deadline.
-\item Check every page of your paper before submitting it.
+\item with respect to the given user $ u $,  for each topic $t_{i} \in T$, its  weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, with $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
+\item opinion of the user towards topic $t_{i}$ is modeled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
+\end{itemize}
+\end{definition}
+The definition of subjective model given above is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from message history of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$
+
+\subsection{Establishment of Subjective Model}
+\label{establishment}
+According to the definition, subjective model of a user can be represented as two distributions: the topic distribution and the sentiment distribution for each topic. 
+With state-of-the-art topic model and sentiment analysis techniques, we can establish subjective model by finding topics and opinions simultaneously. 
+\subsubsection{Topic Analysis}
+\label{topic}
+Previous studies have tried to identify topics by finding key words \cite{Chen:2010STE}, extracting  entities \cite{Abel:2011AUM} or linking tweets to external knowledge categories \cite{conf/icwsm/MacskassyM11}.
+Recent works show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} have been efficient ways to characterize latent topics of large volume corpus.
+Topics of LDA are broader in concept, since a single topic consists of the whole collection of related words, so we adopt the LDA topic model for topic analysis.  
+Topic analysis for all users in a global network on Twitter is a nontrivial task. 
+There are millions of users and billions of tweets associcated with these users, and the effectiveness and efficiency of topic model is a big problem.
+However, the ``following'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily", which has been observed in many social networks \cite{mcpherson2001birds}.
+Homophily implies that a user follows another user because of sharing common topics of interest. 
+According to the principle of homophily, we put forwards the concept of \textbf{Local Topic Space}: 
+\begin{definition}[Local Topic Space]
+\label{local}
+Let $G=\left( V,E \right) $ denotes a global social network, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
+to denote $ u $'s $ \tau $-ego network, where $ \tau $ -ego network means a subnetwork formed by $ u $'s $ \tau $-hop 
+friends in the network $ G $, and $ \tau \geqslant 1 $ is a tunable integer parameter to control the scale of the ego network. 
+In the $ \tau $-ego network of user $ u $, all users concentrate on a few topics derived from the content generated by them, and these topics form a local topic space $ T_{u} $.
+\end{definition}
+The relatively tiny size and topic homophily of ego network lower the impact of data sparsity and degrade the complexity of calculation.
+
+Therefore we adopt a user-level LDA model to find latent topics in Local Topic Space by aggregating all tweets generated by a user into a single document just as \cite{Hong:2010EST}. 
+The result of LDA produces two multinomial distributions, with distribution $ \theta_{u} $ representing the probability distribution of a user over each topic, and distribution $ \beta_{k} $ representing the probability distribution of a topic over whole vocabulary used by all users in ego network.
+
+\subsubsection{Opinion Analysis}
+\label{opinion}
+
+Users often express opinions towards topics of interest by publishing topic-related tweets. 
+Sentiment analysis or opinion mining is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}.
+Opinions are regulated as sequential discrete values to represent sentiment strength(for example: 0 stands for negtive and 1 for positive).
+Recently, researchers began to pay more and more attention to social media such as Twitter \cite{Thelwall:2010SSS,Thelwall:2012SSD,Hu:2013www} and provide effective sentiment analysis tools.
+
+SentiStrength package has been built especially to cope with sentiment analysis in short informal text of social media \cite{Thelwall:2010SSS}. 
+It combines lexicon-based approaches with sophisticated linguistic rules adapted to social media, which is suitable for analyzing sentiment of tweets.
+SentiStrength assigns two values to each tweet standing for sentiment strengths: a positive and a negative sentiment measurement, with $ \left[ -5,-1 \right]  $ denoting negative and $ \left[ 1,5 \right]  $ denoting positive sentiment strength.
+Sentiment assigned by SentiStrength is a fine-grained strength, which can catch fine opinion distributions in a user's subjective model.  
+For the convenience of distribution calculation, we map the output of SentiStrength to single-scaled sentiment valence space $ \left[ 0, 8 \right] $ as follows:
+\begin{equation}
+\label{opinionmap}
+o= \left\{ 
+\begin{array}{lll}
+{p+3} & if \vert p \vert > \vert n \vert \\
+{n+5} & \text{if } \vert n \vert > \vert p \vert \\
+{4}  & \text{if } \vert p \vert = \vert n \vert
+\end{array}
+\right.
+\end{equation}
+Where $ p $ denotes the positive setiment strength and $ n $ denotes negative sentment strength.
+In the sentiment valence space, value 4 indicates neutral sentiment, while values above 4 indicate positive sentiment and values below 4 indicate negative sentiment.
+
+\subsubsection{Concrete Subjective Model}
+\label{concrete}
+
+As Definition~\ref{local} describes, for a user $ u $ in a global netwotk, we can extract a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $. 
+And the subjective model of each user $ u \in G_{u} $ can be concreted within the ego network. 
+We denote tweets set published by a user $ u $ as $ M_{u}=\left\lbrace m_{i} \vert i \in \left[ 1, \cdots, N \right]  \right\rbrace$.
+All tweets in $ M_{u} $ is concatenated to a single document $ d_{u} $ to construct Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ with LDA topic model.
+The topic model is built with parameter $ \theta_{u} $\ representing the distribution of user $ u $ over topics he talks about, and parameter $ \beta_{k} $ represents the distribution of each topic over the vocabulary of all tweets.
+SentiStrength is applied to each tweet $ m $ in collection $ M_{u} $ and outputs sentiment strength $ s_{m} $ for tweet $ m $.
+Subjective model of user $ u $ is built the  as follows:
+\begin{itemize}
+\item Firstly, for user $ u $, the corresponding $ \theta_{u} $ can be regarded as his topic distribution in the Local Topic Space $ T_{u} $, and topics he cares about are $ Z_{u}= \left\lbrace z \vert p\left( z \vert \theta_{u}\left( z \right)  \right)>0 \right\rbrace $.
+\item Secondly, in order to identify the target of opinion in each tweet, the topic model is applied to each tweet $ m $ to find topics it talks about, which are $ Z_{m} =\left\lbrace z_{m} \vert p\left( z_{m} \vert \theta, \beta, Z_{u} \right)>0 \right\rbrace $.
+\item Thirdly, the opinion distribution of user $ u $ towards topic $ t \in Z_{u} $ could be calculated as: 
+\begin{equation}
+\label{opinionall}
+d_{u,t}\left( o \right) = \left\lbrace \dfrac{N_{o}}{\sum_{o \in O} N_{o}} \vert O=\left[ 0, \cdots, 8 \right] \right\rbrace 
+\end{equation}
+where $ N_{o} $ is the number of times user $ u $ expresses an opinion towards topic $ t $ with sentiment strength $ o $, which could be calculated as:
+\begin{equation}
+\label{opinion1}
+N_{o}=\sum_{m \in Mu} I\left( s_{m} \right) , \text{ if } s_{m}=o \& t \in Z_{m}
+\end{equation}
+\begin{equation}
+\label{opinion2}
+I\left( s_{m} \right)=\left\{
+\begin{array}{ll}
+{1} & \text{if } s_{m}=o \& t \in Z_{m}\\
+{0} & \text{else}
+\end{array}
+\right.
+\end{equation}
+where $ s_{m} $ denotes the sentiment strength of tweet $ m $. For simplicity, we assume the sentiment of tweet $ m $ is related to every topic it talks about in $ Z_{m} $.
 \end{itemize}
 
-\section{Copyright}
-All papers submitted for publication by AAAI Press must be accompanied by a valid signed copyright form or, in the case of technical reports, by a valid signed permission to distribute form.
-There are no exceptions to this requirement.
-You must send us the original version of this form.
-However, to meet the deadline, you may fax (1-650-321-4457) or scan and e-mail the form (pubforms14@aaai.org) to AAAI by the submission deadline, and then mail the original via postal mail to the AAAI office.
-\textbf{If you fail to send in a signed copyright or permission form, your paper will not be published.} You will find PDF versions of the AAAI copyright and permission to distribute forms in the author kit.
+Totally, we build subjective model $ P\left( u \right) $ for user $ u $ as:
+\begin{equation}
+\label{subuser}
+P\left( u \right)= \left\lbrace \left( t, p\left( z \vert \theta_{u} \right), d_{u,t}\left( o \right) \right)  \vert t \in Z_{u}, o \in O  \right\rbrace  
+\end{equation}
 
-\section{Formatting Requirements in Brief}
-We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices.
-AAAI imposes some requirements on your source and PDF files that must be followed.
-Most of these requirements are based on our efforts to standardize conference manuscript properties and layout.
-These requirements are as follows, and all papers submitted to AAAI for publication must comply:
+\section{Retweeting Analysis With Subjective Model}
 
+Many factors have been proved to influence retweeting behavior \cite{Suh2010,conf/icwsm/MacskassyM11,Comarela:2012UFA}, however few researches have investigated the subjective motivation of a user to retweet a message.
+Therefore we will study whether subjective model can help understand underlying reasons of a user's retweeting behavior.
+Apart from the context constraints, a tweet is more likely to be retweeted by subjective users who find it worth to. 
+Therefore, we are not interested in modelling the tweet by itself as other researches \cite{Naveed:2011SMC,2011:NaveedGKC,conf/icwsm/PfitznerGS12}, but how the tweet resonate with the users who might want to disseminate it.
+We assume the motivation of a user to retweet a message lies in that the user considers only the tweet content arousing his resonation without context perturbation. 
+If a tweet is published, all followers of its author will receive it in time, and followers are likely to retweet it if they find it worthwhile. 
+Under such assumption, we investigate the problem in 1-ego network for the author of target tweet. 
+The relation between tweet, author and followers can be illustrated as Figure~\ref{fig1}.
+\begin{figure}[htb]
+%\setlength{\belowcaptionskip}{-0.2cm} 
+\centering
+\includegraphics[width=2.1in,height=2.0in]{ego.pdf}
+%\vspace{-4em}
+\caption{Illustration of relations between tweet, author and followers.
+Author is denoted as $ u_{a} $, tweet as $ m $, followers as $ f_{i} $ and tweets of follower $ f_{i} $ as $ m_{i} $.
+An directed edge $ \left( f_{i},u_{a} \right)  $ means that $ f_{i} $ is exposed to the messages published by $ u_{a} $.}
+\label{fig1}
+\end{figure}
+
+\subsection{Problem Formulation}
+\label{formulation}
+
+Retweeting analysis problem can be formulated as follows:
+For each target tweet $ m $, let $ F $ denotes the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denotes   tweets the user has published.
+For each follower $ u_{f} \in F $, we can define a quadruple $ <u_{f}, u_{a}, m, r_{f}>  $: 
 \begin{itemize}
-\item Your .tex file must compile in PDF\LaTeX{} --- \textbf{ no .ps or .eps figure files.}
-\item All fonts must be embedded in the PDF file --- \textbf{ this includes your figures.}
-\item Modifications to the style sheet (or your document) in an effort to avoid extra page charges are NOT allowed.
-\item No type 3 fonts may be used (even in illustrations).
-\item Your title must follow US capitalization rules.
-\item \LaTeX{} documents must use the Times or Nimbus font package (do not use Computer Modern for the text of your paper).
-\item No \LaTeX{} 209 documents may be used or submitted.
-\item Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or removed from the document (even if they are in a graphics file embedded in the document). 
-\item Two-column format in AAAI style is required for all papers.
-\item The paper size for final submission must be US letter. No exceptions.
-\item The source file must exactly match the PDF.
-\item The document margins must be as specified in the formatting instructions.
-\item The number of pages and the file size must be as specified for your event.
-\item No document may be password protected.
-\item Neither the PDFs nor the source may contain any embedded links or bookmarks.
-\item Your source and PDF must not have any page numbers, footers, or headers.
-\item Your PDF must be compatible with Acrobat 5 or higher.
-\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
-\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" command) .
+\item $ r_{f} $ is a binary label indicating whether $ m $ is retweeted by $ u_{f} $.
+\item Firstly our work focuses on building subjective model $ P\left( u \right)  $ for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace $ in the ego network with all tweets collections $ M=\left\lbrace M_{u} | u \in F \cup \left\lbrace u_{a} \right\rbrace  \right\rbrace  $.
+\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjective similarities between tweet $ m $, its author $ u_{a} $ and follower $ u_{f} $.
 \end{itemize}
 
-If you do not follow the above requirements, it is likely that we will be unable to publish your paper.
+\subsection{Subjective Similarity}
+\label{similarity}
 
-\section{What Files to Submit}
-You must submit the following items to ensure that your paper is published:
-\begin{itemize}
-\item A fully-compliant PDF file.
-\item Your  \LaTeX{}  source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file).
-The only exception is the bibliography, which you may include separately.
-Your source must compile on our system, which includes the standard \LaTeX{} support files.
-\item All your graphics files.
-\item The \LaTeX{}-generated files (e.g. .aux and .bib file, etc.) for your compiled source.
-\item All the nonstandard style files (ones not commonly found in standard \LaTeX{} installations) used in your document (including, for example, old algorithm style files). If in doubt, include it.
-\end{itemize}
+In order o understand the underlying reasons why a user retweet a message, we try to simulate the subjective decision-making procedure by investigating the relationship among a tweets and subjective models of its author and followers.
+We assume that if a tweet and the subjective models of a user are similar enough in terms of topics and opinions, the user will have a very high probability to retweet the tweet. 
+We call this phenomenon as ``resonation'', and assume resonation between tweets and users will elicit retweeting behavior.
+With subjective models built for users, we can define a similarity measurement to quantify the resonation among them.
 
-Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you may incur late fees).
-\textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros.
-Accompanying this source file, you must also supply any nonstandard (or older) referenced style files and all your referenced graphics files.
+\subsubsection{Topic Similarity}
+\label{topsim}
 
-Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution.
-Place your PDF and source files in a single tar, zipped, gzipped, stuffed, or compressed archive.
-Name your source file with your last (family) name.
+Topic distribution of a tweet can be inferenced by applying topic model estimated from the tweets collections of users.
+The topic similarity between tweet and user can be calculated with methods such as the cosine distance \cite{cha2007comprehensive} or the Jensen-Shannon Divergence \cite{weng2010twitterrank} with satisfactory results.
+In our research, we adopt cosine distance to measure the topic similarity, which is defined as:
+\begin{equation}
+sim_{topic}=\dfrac{\theta_{m} \cdot \theta_{u}}{\parallel \theta_{m} \parallel \parallel \theta_{u} \parallel}
+\end{equation}
+where $ \theta_{u}$ denotes topic distribution of user $ u $ and $\theta_{m}$ denotes topic distribution of tweet $ m $.
 
-\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, and so forth.
-A shell script (created by an AAAI member --- it might not work without modification on your system) that might help you create the \LaTeX{} source package is included in the Author Kit.
+\subsubsection{Opinion Similarity}
+\label{opsim}
 
-\section{Using \LaTeX{} to Format Your Paper}
+Opinions of a tweet can be analyzed with SenStrength and the values are transformed to range $ \left[ 0,8 \right]  $  with Equation~\ref{opinionmap}.
+Opinions of a tweet towards each topic it talks about can be regarded as a distribution with 1.0 probability on a single sentiment value just as opinion dsitribution of subjective model. 
+Therefore opinion similarity between tweets and users is the same with similarity between two users.   
+We treate opinion as distribution over sentiment valence space with each element of the distribution represents the propotion of the corresponding strength values in the user's all sentiment values. 
+However ,values in sentiment valence space are not independent. 
+They are sequential and represent strength of the sentiment, for example value 8 represents more positive sentiment than value 5, and their sentiment distance is 3.
+Therefore, opinion similarity can not be calculated as the distance between two distributions.
+Illustrated as Table~\ref{tab1}, $ user_{1} $ holds most negative opinion on a topic(with 100\% sentiment value 0), while $ user_{2} $(100\% positive sentiment value 7) and $ user_{3} $(100\% positive sentiment value 8) hold positive opinion.
+If cosine similarity measurement is adopted to calculate opinion similarity, all similarities are 0.
+In fact $ user_{2} $ is more similar with $ user_{3} $ than $ user_{1} $ because they both hold positive opinion and their sentiment distance is much less than $ user_{1} $. 
+\begin{table}[h]
+\scriptsize
+\centering
+\caption{Illustration of opinion similarity calculation}
+\label{tab1}
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
+\hline
+ & 0 & 1& 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
+\hline
+$user_{1}$ & 1.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
+\hline
+$user_{2}$ & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1.0 & 0.0 \\
+\hline
+$user_{3}$ & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1.0 \\
+\hline
+\end{tabular}
+\end{table}  
+In order to accurately catch opinion similarity, we propose a novel similarity-calculating method by combining both sentiment distance and distribution similarity.
+The opinion similarity of two users or a tweet and a user on topic $ t $ can be calculated as: 
+\begin{equation}
+sim_{opinion}^{t}(O_{1},O_{2})=\dfrac{8-|\sum_{i=0}^{8}d_{i}v_{i}-\sum_{j=0}^{8}d_{j}v_{j}|}{8}
+\end{equation}
+where $ d_{i} $ denotes the $ ith $ distribution of opinion vector, and $ v_{i} $ denotes corresponding sentiment strength value.
+Accordingly, overall opinion similarity on all topics can be calculated as normalized similarity of all opinion similarities on their common topics of interest. 
+\begin{equation}
+sim_{opinion}(u_{1},u_{2})=\dfrac{\sum_{t=1}^{|T|}sim_{opinion}^{t}(O_{1},O_{2})}{|T|}
+\end{equation}
+where $ T $ denotes the common topics of interest between two users or a tweet and a user.
 
-The latest version of the AAAI style file is available on AAAI's website.
-Download this file and place it in a file named ``aaai.sty" in the \TeX\ search path.
-Placing it in the same directory as the paper should also work.
-You must download the latest version of the complete author kit so that you will have the latest instruction set.
+\subsubsection{Subjective Similarity}
 
-\subsection{Document Preamble}
+Given a tweet $ t $ and a user subjective model $ P\left( u \right)  $, we can define their subjective similarity by combining topic similarity and opinion similarity as follows:
+\begin{equation}
+Sim_{sub} \left( t,u \right) = \alpha * sim_{topic}+\left( 1-\alpha \right)*sim_{opinion}
+\end{equation}
+where $ \alpha $ is the coefficient used to control the proportions of topic similarity and opinion similarity in the holistic subjective similarity. 
+A user cares more about topics a tweet talks about with a larger $ \alpha $, and cares more about opinions with a samller $ \alpha $. 
+A personalized $ \alpha $ can be learned from the retweeting history of a user to represent his retweeting habit.
 
-In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection.
-This command set-up is for three authors.
-Add or subtract author and address lines as necessary, and uncomment the portions that apply to you.
-In most instances, this is all you need to do to format your paper in the Times font.
-The helvet package will cause Helvetica to be used for sans serif, and the courier package will cause Courier to be used for the typewriter font.
-These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).
+\subsection{Retweeting Analysis}
+\label{analysis}
+The motivation why a user retweet is complicated, and involves the tweet itself, its author and its receivers who is following its author. 
+Figure~\ref{fig1} illustrates their relation. 
+The idea behind this work is that taking into account user attitudes towards his own interests can yield benefits in explaining the subjective motivation of retweeting behavior. 
+Specifically, we consider this question from three aspects: 
+(i) how similar is the tweet to the subjective model of a user in terms of topics and opinions, i.e.
+$ sim_{sub} \left( m,u \right) $, (ii) are the author and user like-minded people considering similarity of their subjective models, i.e.
+$ sim_{sub}\left( u_{a},u \right)  $, and (iii) whether the tweet is novel or original judged from its similarity with subjective model of its author, i.e.
+$ sim_{sub}\left( m,u_{a} \right)  $.
+Intuitionally, a user might retweet a message if its content is close enough to his subjectivity, its author is a like-minded friend and it is original from inner subjectivity of its author. 
+In this work we will carry out a sery of experiments to demonstrate such intuition.
 
-Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper.
-If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers).
-The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.
+\section{Experiment}
+\label{experiment}
 
-\begin{quote}
-\begin{small}
-\textbackslash documentclass[letterpaper]{article}\\
-\% \textit{Required Packages}\\
-\textbackslash usepackage\{aaai\}\\
-\textbackslash usepackage\{times\}\\
-\textbackslash usepackage\{helvet\}\\
-\textbackslash usepackage\{courier\}\\
-\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
-\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{PDFINFO for PDF\LaTeX{}}\\
-\% Uncomment and complete the following for metadata (your paper must compile with PDF\LaTeX{})\\
-\textbackslash pdfinfo\{\\
-/Title (Input Your Paper Title Here)\\
-/Author (John Doe, Jane Doe)\\
-/Keywords (Input your paper's keywords in this optional area)\\
-\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Section Numbers}\\
-\% Uncomment if you want to use section numbers\\
-\% and change the 0 to a 1 or 2\\
-\% \textbackslash setcounter\{secnumdepth\}\{0\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Title, Author, and Address Information}\\
-\textbackslash title\{Title\}\\
-\textbackslash author\{Author 1 \textbackslash and Author 2\textbackslash\textbackslash \\ 
-Address line\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash \\
-\textbackslash And\\
-Author 3\textbackslash\textbackslash\\ Address line\textbackslash\textbackslash\\ Address line\}\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{Body of Paper Begins}\\
-\textbackslash begin\{document\}\\
-\textbackslash maketitle\\
-...\\
-\%\%\%\%\%\%\%\%\%\%\\
-\% \textit{References and End of Paper}\\
-\textbackslash bibliography\{Bibliography-File\}\\
-\textbackslash bibliographystyle\{aaai\}\\
-\textbackslash end\{document\}
-\end{small}
-\end{quote}
+\subsection{Dataset}
+We adopt the Twitter dataset of previous work \cite{Luo:2013RMF}, which was created using Twitter API \footnote{\url{https://dev.twitter.com/}}. 
+To form the dataset, 500 target English tweets published from September 14th, 2012 to October 1st, 2012 were monitored to find who would retweet it in the next few days. 
+And each tweet was chosen as starting point to collect at least recent 200 tweets for its author and followers.
+Overall, there are 4,5531 followers, 6,277,736 tweets, and 5214 followers who have retweeted at least one target tweet during the monitored period. 
+We extract 3,0876 users who have retweeted at least 20 times in their recent tweets to build their sujective model and study their retweeting motivations. 
+In order to determine the optimized values of $ \alpha $ in subjective similarities($ sim_{sub} \left( m,u \right) $, $ sim_{sub}\left( u_{a},u \right)  $, $ sim_{sub}\left( m,u_{a} \right)  $), we implemented a \textit{mini-batch gradient descent} algorithm with the users' retweeting history.
+As a result, all three subjective similarities are optimized to reflect the personalized retweeting habits of each users.
 
-\subsection{Inserting Document Metadata with \LaTeX{}}
-PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately.
-\textbf{Document Metadata  for Author and Title are REQUIRED.}
+\subsection{Correlation of Subjectivity and Retweeting Behavior}
 
-If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them.
-The epstopdf package will usually work for eps files.
-You will need to convert your ps files to PDF however.
+The first step of demonstrating our intuition is to assessing the existence of a correlation between subjective similarity and retweeting behaviour. 
+To test this correlation, we adopt a statistical hypothesis test called Analysis of Variance (ANOVA). 
+ANOVA tests the \textit{null hypothesis} that samples in two or more groups are derived from the same population by estimating the variance of their means.
+This test fits our goal of testing if the distinct sets of retweeters and non-retweeters do have the same subjective similarity to a tweet that both sets are exposed to.
+The ANOVA method produces two output values: the \textit{F-ratio} and the \textit{p-value}. 
+If the difference between the means is due to chance, the expected value of the \textit{F-ratio} is 1.00. 
+If ANOVA yields a p-value lower than the significance level $ \alpha $, the \textit{null hypothesis} is rejected. 
+The significance level is conventionally used at 0.01.
+At the same time, we carry out the test by varying the number of topics in LDA as 50, 100 , 150 and 200 to determine impact of topic number. 
+The results are listed in Table~\ref{tab2}, 
+\begin{table}[h]
+\scriptsize
+\centering
+\caption{ANOVA test for three subjective similarities}
+\label{tab2}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\multicolumn{2}{|c|}{Similarity}& $ sim_{sub} \left( m,u \right) $ & $ sim_{sub}\left( u_{a},u \right)  $ & $ sim_{sub}\left( m,u_{a} \right)  $\\
+\hline
+\multirow{2}{*}{50} & \textit{F} & \textbf{12.182} & 2.212 & 4.236 \\
+\cline{2-5}
+  & \textit{p} &  $\mathbf{4.44e^{-06}}$  & 0.140 & 0.272\\
+\hline
+\multirow{2}{*}{100} & \textit{F} & \textbf{22.356} & \textbf{12.240} & \textbf{14.664} \\
+\cline{2-5}
+  & \textit{p} &  $\mathbf{2.43e^{-08}}$  & $\mathbf{6.25e^{-06}}$ & $\mathbf{8.46e^{-07}}$\\
+\hline
+\multirow{2}{*}{150} & \textit{F} & \textbf{43.892} & \textbf{31.145} & \textbf{28.466} \\
+\cline{2-5}
+  & \textit{p} &  $\mathbf{8.65e^{-11}}$  & $\mathbf{3.55e^{-08}}$ & $\mathbf{1.32e^{-09}}$\\
+\hline
+\multirow{2}{*}{200} & \textit{F} & \textbf{31.675} & \textbf{20.616} & 6.145\\
+\cline{2-5}
+  & \textit{p} &  $\mathbf{4.22e^{-06}}$  & $\mathbf{2.92e^{-05}}$ & 0.26\\
+\hline
+\end{tabular}
+\end{table}
 
-\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata.
-The data in the metadata must be completely plain ascii.
-It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands.
-Type the title exactly as it appears on the paper (minus all formatting).
-Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma.
-You may also include keywords in the Keywords field.
+Note that for the number of topics 100 and 150, all similarities yield \textit{p-values} below $ \alpha $.
+This suggests that subjective similarities can be good indicators for modeling retweeting behavior.
+Therefore we reject the \textit{null hypothesis} and accept the alternative hypothesis.
+For the rest experiments, we simply set the number of topic as 100 for LDA.
 
-\subsection{Preparing Your Paper}
+\subsection{Comparison With Other Models}
+\label{Comparison}
 
-After the preamble above, you should prepare your paper as follows:
+Given that ANOVA indicated correlation between subjective similarities and retweeting behavior, we compare three similarities against other content-based similarity measurements such as TF-IDF model(modelling user with bag-of-words in his tweets) \cite{Luo:2013RMF}, entity-based model(model user with entities extracted from his tweets) and hashtag-based model(model user with hashtags used in his tweets) \cite{Abel:2011AUM}.
 
-\begin{quote}
-\begin{small}
-\textbackslash begin\{document\}\\
-\textbackslash maketitle\\
-...\\
-\textbackslash bibliography\{Bibliography-File\}\\
-\textbackslash bibliographystyle\{aaai\}\\
-\textbackslash end\{document\}\\
-\end{small}
-\end{quote}
-\subsection{Incompatible Packages}
-The following packages are incompatible with aaai.sty and/or aaai.bst and must not be used (this list is not exhaustive --- there are others as well):
-\begin{itemize}
-\item hyperref
-\item natbib
-\item geometry
-\item titlesec
-\item layout
-\item caption
-\item titlesec
-\item T1 fontenc package (install the CM super fonts package instead)
-\end{itemize}
+We take 5,214 retweeters in our dataset who retweet at least one target tweet as positive instances, and randomly sample 5,214 negative instances from the 40,317 followers who do not retweet any target tweet.
+The balance dataset of all positive and negative instances is randomly divided into five parts for 5-fold cross-validation. 
+We use the logistic regression classifier of Scikit-learn machine learning package \cite{scikit-learn} for training and testing.
+Accuracy is our evaluation metric, and the result is listed in Table~\ref{tab3}.
+\begin{table}[h]
+\centering
+\caption{Comparison of prediction accuracy for different models. }
+\label{tab3}
+\begin{tabular}{|c|c|}
+\hline
+Feature & Accuracy(\%) \\
+\hline
+TF-IDF & 60.85  \\
+entity & 68.76 \\
+hashtag & 59.12  \\
+$ sim_{sub} \left( m,u \right) $ & 73.88\\
+$ sim_{sub}\left( u_{a},u \right)  $ & 70.04\\
+$ sim_{sub}\left( m,u_{a} \right)  $ &69.64\\
+$ sim_{all}  $ &\textbf{75.64}\\
+\hline
+\end{tabular}
+\end{table}
 
-\subsection{Illegal Commands}
-The following commands may not be used in your paper:
-\begin{itemize}
-\item \textbackslash input
-\item \textbackslash vspace (when used before or after a section or subsection)
-\item \textbackslash addtolength 
-\item \textbackslash columnsep
-\item \textbackslash top margin (or text height or addsidemargin or even side margin)
-\end{itemize}
+The best accuracy(75.64\%) is achieved by the $ sim_{all}  $, for which We put all three subjective similarities into classifier to test impact of their combination.
+The perfromance of TF-IDF model(60.85\%) is moderate.  
+Entity-based model(68.76\%) is very close to  $ sim_{sub}\left( u_{a},u \right)$(70.04\%) and $ sim_{sub}\left( m,u_{a} \right)  $(69.64\%), and their difference is not significant.
+While for hashtag-based model, its accuracy is the lowest(59.12\%), the reason might lie in a very low usage of hashtag in users' tweets. 
+The performance of $ sim_{sub} \left( m,u \right) $(73.88\%) is better than others except for $ sim_{all}  $.
+The results above show that subjective model can better help understand retweeting behavior than other user models.
 
-\subsection{Paper Size, Margins, and Column Width}
-Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
-\begin{itemize}
-\item Top margin: .75 inches
-\item Left margin: .75 inches
-\item Right margin: .75 inches
-\item Bottom margin: 1.25 inches
-\end{itemize}
+\subsubsection{Combining Evaluation With Other Factors}
+\label{combining}
+Subjective model tries to catch the subjective motivation of users based on their tweets content, whereas other important factors associated with retweeting behavior are not considered, such as network topology and metadata of the user, etc.
+In this section, we combine subjective similarities with other important factors that other researches have demonstrated. 
+Firstly we compare the performance of our method with model of Luo \emph{et al.}~\shortcite{Luo:2013RMF}.
+In their work they use four feature families: ``Retweet History''(follower who retweeted a user before is likely to retweet the user again), ``Follower Status''(the number of tweets, followers, friends, listed times and being verified), ``Follower Active Time''(interaction with others) and ``Follower Interests''(bag-of-words used to model users).
+Secondly we demonstrate that performance of retweeting prediction could be improved significantly by using subjective model instead of bag-of-words model in their feature set. 
+We use the same logistic regression classifier, dataset and settings as last experiment. The feature set of Luo \emph{et al.}~\shortcite{Luo:2013RMF} is marked as ``LUO''.
+In addition, we set a baseline (marked as ``RB''), which simply predicts followers who have retweeted the author's previous tweets as retweeters of target tweet. 
+The result is listed in Table~\ref{tab4}.
+\begin{table}[h]
+\centering
+\caption{Prediction Accuracy of Different Models. Significant improvement over baseline with star($ \ast $) and LUO' model with dagger($ \ddagger $) (p$ < $0.05).}
+\label{tab4}
+\begin{tabular}{|l|l|}
+\hline
+Feature Set & Accuracy(\%) \\
+\hline
+RB & 60.85  \\
+LUO & 71.76 $ \ast  $\\
+$ sim_{sub} \left( m,u \right) $ & 73.88 $ \ast \quad \ddagger $\\
+$ sim_{sub}\left( u_{a},u \right)  $ & 70.04 $ \ast  $\\
+$ sim_{sub}\left( m,u_{a} \right)  $ &69.64 $ \ast  $\\
+$ sim_{all}  $ & 75.64 $ \ast  \quad \ddagger $\\
+LUO+$ sim_{sub} \left( m,u \right)$ & 74.04  $ \ast \quad \ddagger $ \\
+LUO+$ sim_{sub}\left( u_{a},u \right)$ & 70.27  $ \ast $ \\
+LUO+$ sim_{sub}\left( m,u_{a} \right)$ & 71.86  $ \ast $ \\
+LUO+$ sim_{all}  $ & \textbf{78.15}  $ \ast \quad \ddagger $ \\
+\hline
+\end{tabular}
+\end{table}
 
-The default paper size in most installations of \LaTeX{} is A4.
-However, because we require that your electronic paper be formatted in US letter size, you will need to alter the default for this paper to US letter size.
-Assuming you are using the 2e version of \LaTeX{}, you can do this by including the [letterpaper] option at the beginning of your file:
-\textbackslash documentclass[letterpaper]{article}.
+The accuracy of baseline is 60.85\%, and two prediction methods(``LUO'' and our model) both outperform the baseline significantly. 
+$ sim_{sub} \left( m,u \right) $ and $ sim_{all}  $ outperform ``LUO'' significatantly.
 
-This command is usually sufficient to change the format. Sometimes, however, it may not work. Use PDF\LaTeX{} and include
-\textbackslash setlength\{\textbackslash pdfpagewidth\}\{8.5in\}
-\textbackslash setlength\{\textbackslash pdfpageheight\}\{11in\}
-in your preamble.
+After combining subjective similarities, the accuracy are changing. 
+Noticing that, the most significant improvement(LUO+$ sim_{all}  $, 6.39\% improvement) is achieved by adding all three subjectivie similarities, which verifies our intuition. 
+Subjective similarity between tweet and followers also gives significant improvement(LUO+$ sim_{sub} \left( m,u \right) $, 2.12\% improvement), which indicates that subjective resonation between tweet and followers can be considered as the underlying reason that elicits retweeting behavior.
+Adding other two subjective similarities can not improve performance significantly.
 
-\textbf{Do not use the Geometry package to alter the page size.} Use of this style file alters aaai.sty and will result in your paper being rejected.
+\subsection{Case Study}
+\label{example}
+In this section we give an vivid description about subjective model and its ability in explaining the retweeting behavior with an example. 
+Topic and opinion of one target tweet, subjective models for its author, and two followers (one retweet it while the other does not) are shown as Figure~\ref{fig2}. 
+The right part of each sub-figure illustrates topic distribution and the left part illustrates opinion distribution. 
+It is clear that the tweet talks about the 14th topic of the local topic space. 
+\begin{figure*}[htb]
+%\setlength{\belowcaptionskip}{-0.2cm} 
+\centering%,bb=0 0 1280 960
+\includegraphics[width=6.0in,height=3.5in]{tweets10.pdf}
+%\vspace{-4em}
+\caption{Subjective model examples.}
+\label{fig2}
+\end{figure*}
+Figure~\ref{fig3} shows top words of the 14th topic, the tweets of author and followers with word cloud\footnote{We use TagCrowd (\url{http://tagcrowd.com/}) to produce word cloud.}.
+\begin{figure}[htb]
+%\setlength{\belowcaptionskip}{-0.2cm} 
+\centering
+\includegraphics[width=3.5in,height=2.2in]{text_cloud.pdf}
+%\vspace{-3em}
+\caption{Word cloud of 14th topic, publisher and followers}
+\label{fig3}
+\end{figure}
+Content of the tweet is:\\
+\textit{Tweet: ``Sometimes the right person for you was there all along. You just didn’t see it because the wrong one was blocking the sight''} \\
+The topic of this tweet is about ``love between people'' and the opinion is neutral, which is in accordance with the 14th topic word cloud in Figure~\ref{fig3} and sub-figure of tweet in Firgure~\ref{fig2}.
+The author concentrates on the 14th topic, and his opinions are mainly neutral (as Figure~\ref{fig2},~\ref{fig3} show).
+As for two followers, the ``retweeter'', has published tweets about two topics (the 14th and 52nd topic) uniformly and his opinions towards the two topics are mainly neutral.
+While the ``unretweeter'', has also talked about two topics (14th and 56th topic), but he is mainly interested in 14th topic and has positive opinion.
+Although two followers have same interest (the 14th topic), their different opinions elicit their different decision, which verifies subjective model can help better understand the retweeting motivation by modelling not only topics but opinions.
 
-\subsubsection{Column Width and Margins.}
-To ensure maximum readability, your paper must include two columns.
-Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns.
-The aaai.sty file will automatically create these columns for you.
+\section{Related Work}
+\label{relatedwork}
 
-\subsection{Overlength Papers}
-If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods.
-Next,  shrink the size of your graphics.
-Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment.
-If these two methods don't work, you may minimally use the following.
-For floats (tables and figures), you may minimally reduce \textbackslash floatsep, \textbackslash textfloatsep, \textbackslash abovecaptionskip, and \textbackslash belowcaptionskip.
-For mathematical environments, you may minimally reduce \textbackslash abovedisplayskip, \textbackslash belowdisplayskip, and \textbackslash arraycolsep.
-You may also alter the size of your bibliography by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
-right before the bibliography.
+User modelling provides researchers with insights into user's online behaviors. 
+Hannon \emph{et al.}~\shortcite{Hannon:2010} proposed that Twitter users can be modeled by tweets content and the relation of Twitter social network, while content-based approach could find similar users who are "distant" without follow relations.
+Macskassy and Michelson~\shortcite{conf/icwsm/MacskassyM11} discover user's topics of interest by leveraging Wikipedia as external knowledge to determine a common set of high-level categories that covers entities in tweets.
+Ramage \emph{et al.}~\shortcite{RamageEtAl:10} made use of topic models to analyze Twitter content at the level of individual, showing improved performance on tasks such as post filtering and user recommendation.
+Xu \emph{et al.}~\shortcite{Xu:2012MUP} proposed a mixture model which incorporated three important factors, namely breaking news, friends' timeline and user interest, to explain user posting behavior.
+Pennacchiotti and Popescu~\shortcite{Pennacchiotti:icwsm11} proposed a most comprehensive method to model Twitter user for user classification, confirming the value of in-depth features by exploiting the UGC.
+A large body of studies have analyzed characteristics of retweeting \cite{conf/icwsm/MacskassyM11,Starbird:2012RRI}, examining factors that lead to increased retweetability \cite{Suh2010,Comarela:2012UFA} and designing models to estimate the probability of being retweeted \cite{Osborne_Lavrenko_2011,Jenders:2013APV,conf/icwsm/PfitznerGS12}.
 
-Commands that alter page layout are forbidden.
-These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive).
-If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee.
-Other commands that are questionable and may cause your paper to be rejected include  \textbackslash parindent, and \textbackslash parskip.
-Commands that alter the space between sections are also questionable.
-The title sec package is not allowed.
-Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted.
-Before using every trick you know to make your paper a certain length, try reducing the size of your graphics or cutting text instead or (if allowed) paying the extra page charge.
-It will be cheaper in the long run.
+\section{Conclusion}
+In this paper, we propose subjective model to model users, and demostrate its ability in retweeting behavior analysis.
+We assume that retweeting should be elicited by the subjective similarities among the tweet and its author and followers.
+We define subjective model formally as the combination of topic distribution and opinion distribution, and we concrete subjective model leveraging statistical topic model and sentiment analysis techniques.
+We demonstrate the effectiveness of our model for retweeting analysis problem and show that subjective model is able to reach better understanding of retweeting behavior.
 
-\subsection{Figures}
-Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use the .gif (the resolution is too low), .ps, or .eps file format for your figures.
+In the future, we will apply subjective model to other social network analysis task such as link prediction and friend recommendation.
 
-When you include your figures, you must crop them \textbf{outside} of \LaTeX{}.
-The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear when page numbers are applied or color space is standardized.
-
-\subsection{Type Font and Size}
-Your paper must be formatted in Times Roman or Nimbus.
-We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface.
-Sans serif, when used, should be Courier.
-Use Symbol or Lucida or Computer Modern for \textit{mathematics only.
-}
-
-Do not use type 3 fonts for any portion of your paper, including graphics.
-Type 3 bitmapped fonts are designed for fixed resolution printers.
-Most print at 300 dpi even if the printer resolution is 1200 dpi or higher.
-They also often cause high resolution imagesetter devices and our PDF indexing software to crash.
-Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts.
-Files containing those fonts (even in graphics) will be rejected.
-
-Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts.
-The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e.
-(Note that papers formatted in this way will still use Computer Modern for the mathematics.
-To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")
-
-If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader.
-The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document.
-If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.
-
-The default size for your type should be ten-point with twelve-point leading (line spacing).
-Start all pages (except the first) directly under the top margin.
-(See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.
-
-\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}
-
-If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts.
-They are available without charge from the American Mathematical Society:
-http://www.ams.org/tex/type1-fonts.html.
-
-\subsection{Title and Authors}
-Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading).
-This style is called ``mixed case." Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading).
-(If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.
-
-\subsubsection{Formatting Author Information}
-Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display.
-For several authors from the same institution, use \textbackslash and:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1 \textbackslash and  ...  \textbackslash and Author \textit{n}\textbackslash \textbackslash  \\
-Address line \textbackslash \textbackslash ~... \textbackslash \textbackslash ~Address line\}
-\end{small}
-\end{quote}
-
-\noindent If the names do not fit well on one line use:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\}\textbackslash \textbackslash \\ \{\textbackslash bf Author 2\}\textbackslash \textbackslash ~ 
-... \textbackslash \textbackslash ~\{\textbackslash bf Author \textit{n}\}\textbackslash \textbackslash \\
-Address line \textbackslash \textbackslash ~ ... \textbackslash \textbackslash ~ Address line\}
-\end{small}
-\end{quote}
-
-\noindent For authors from different institutions, use \textbackslash And:
-
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\textbackslash \textbackslash ~ Address line \textbackslash \textbackslash ~...  \textbackslash \textbackslash ~ Address line
-\textbackslash And  ...  
-\textbackslash And
-Author \textit{n}\textbackslash \textbackslash \\ Address line\textbackslash \textbackslash ~
-... \textbackslash \textbackslash ~
-Address line\}
-\end{small}
-\end{quote}
-
-\noindent To start a separate ``row" of authors, use \textbackslash AND:
-\begin{quote}
-\begin{small}
-\textbackslash author\{Author 1\textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
-\textbackslash AND\\
-Author 2 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\
-\textbackslash And\\
-Author 3 \textbackslash\textbackslash ~ Address line \textbackslash\textbackslash ~
-...  \textbackslash \textbackslash ~ Address line\textbackslash\textbackslash \\\}
-\end{small}
-\end{quote}
-
-\noindent If the title and author information does not fit in the area allocated, place
-\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
-after the \textbackslash documentclass line where \{\textit{height}\} is something like 2.5in.
-
-\subsection{\LaTeX{} Copyright Notice}
-The copyright notice automatically appears if you use aaai.sty.
-If you are creating a technical report, it is not necessary to include this notice.
-You may disable the copyright line using the \verb+\+nocopyrightcommand.
-To change the entire text of the copyright slug, use:
-\textbackslash copyrighttext \{\emph{text}\}.
-Either of these must appear before \textbackslash maketitle.
-Please be advised, however, that \textit{if you disable or change the copyright line and transfer of copyright is required, your paper will not be published.}
-
-\subsection{Credits}
-Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
-\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
-For example:
-\begin{quote}
-\begin{small}
-\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
- supported by everybody.\}\}
-\end{small}
-\end{quote}
-Multiple \textbackslash thanks commands can be given.
-Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document.
-Note that the \textbackslash thanks command is fragile.
-You will need to use \textbackslash protect.
-
-Please do not include \textbackslash pubnote commands in your document.
-
-\subsection{Abstract}
-The abstract must be placed at the beginning of the first column, indented ten points from the left and right margins.
-The title “Abstract” should appear in ten-point bold type, centered above the body of the abstract.
-The abstract should be set in nine-point type with ten-point leading.
-This concise, one-paragraph summary should describe the general thesis and conclusion of your paper.
-A reader should be able to learn the purpose of the paper and the reason for its importance from the abstract.
-The abstract should be no more than two hundred words in length.
-(Authors who are submitting short one- or two-page extended extracts should provide a short abstract of only a sentence or so.) \textbf{Do not include references in your abstract!}
-
-\subsection{Page Numbers}
-
-Do not \textbf{ever} print any page numbers on your paper.
-
-\subsection{Text }
-The main body of the paper must be formatted in ten-point with twelve-point leading (line spacing).
-
-\subsection{Citations}
-Citations within the text should include the author's last name and year, for example (Newell 1980).
-Append lower-case letters to the year in cases of ambiguity.
-Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992).
-In the case of four or more authors, list only the first author, followed by et al.
-(Ford et al.
-1997).
-
-\subsection{Extracts}
-Long quotations and extracts should be indented ten points from the left and right margins.
-
-\begin{quote}
-This is an example of an extract or quotation.
-Note the indent on both sides.
-Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.
-
-\end{quote}
-
-\subsection{Footnotes}
-Avoid footnotes as much as possible; they interrupt the reading of the text.
-When essential, they should be consecutively numbered throughout with superscript Arabic numbers.
-Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.
-
-\subsection{Headings and Sections}
-When necessary, headings should be used to separate major sections of your paper.
-Remember, you are writing a short paper, not a lengthy book!
-An overabundance of headings will tend to make your paper look more like an outline than a paper.
-
-First-level heads should be twelve-point Times Roman bold type, mixed case (initial capitals followed by lower case on all words except articles, conjunctions, and prepositions, which should appear entirely in lower case), with fifteen-point leading, centered, with one blank line preceding them and three additional points of leading following them.
-Second-level headings should be eleven-point Times Roman bold type, mixed case, with thirteen-point leading, flush left, with one blank line preceding them and three additional points of leading following them.
-Do not skip a line between paragraphs.
-Third-level headings should be run in with the text, ten-point Times Roman bold type, mixed case, with twelve-point leading, flush left, with six points of additional space preceding them and no additional points of leading following them.
-
-\subsubsection{Section Numbers}
-The use of section numbers in AAAI Press papers is optional.
-To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2.
-Section numbers should not be used in short poster papers.
-
-\subsubsection{Section Headings.}
-Sections should be arranged and headed as follows:
-
-\subsubsection{Acknowledgments.}
-The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish.
-Please acknowledge other contributors, grant support, and so forth, in this section.
-Do not put acknowledgments in a footnote on the first page.
-If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back.
-Please try to limit acknowledgments to no more than three sentences.
-
-\subsubsection{Appendices.}
-Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.
-
-\subsubsection{References}
-The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page).
-A sample list of references is given later on in these instructions.
-Please use a consistent format for references.
-Poorly prepared or sloppy references reflect badly on the quality of your paper and your research.
-Please prepare complete and accurate citations.
-
-\subsection{Illustrations and Figures}
-Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed.
-Do not group them together at the end of the paper.
-If placed at the top or bottom of the paper, illustrations may run across both columns.
-Figures must not invade the top, bottom, or side margin areas.
-Figures must be inserted using the \textbackslash usepackage\{graphicx\}.
-Number figures sequentially, for example, figure 1, and so on.
-
-The illustration number and caption should appear under the illustration. Labels, and other text in illustrations must be at least nine-point type.
-
-\subsubsection{Low-Resolution Bitmaps.}
-You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed.
-If they are color, they will become an indecipherable mess when converted to black and white.
-This is always the case with gif files, which should never be used.
-The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels.
-You can also enlarge files by manipulating them in software such as PhotoShop.
-Your figures should be a minimum of 266 dpi when incorporated into your document.
-
-\subsubsection{\LaTeX{} Overflow.}
-\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin.
-If this happens, you need to scale the figure or table down, or reformat the equation.
-Check your log file!
-You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}).
-If you don't, the overflow text will simply be eliminated.
-\textbf{Nothing is permitted to intrude into the margins.}
-
-\subsubsection{Using Color.}
-Your paper will be printed in black and white and grayscale.
-Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document.
-Of course, any reference to color will be indecipherable to your reader.
-
-\subsubsection{Drawings.}
-We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations.
-Do not use Microsoft Publisher.
-These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas.
-Shading should be 133 lines per inch if possible.
-Use Times Roman or Helvetica for all figure call-outs.
-\textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt.
-Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.
-
-\subsubsection{Photographs and Images.}
-Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 266 dpi.
-Do not prescreen images.
-
-\subsubsection{Resizing Graphics.}
-Resize your graphics \textbf{before} you include them with LaTeX.
-You may \textbf{not} use trim or clip options as part of your \textbackslash includgraphics command.
-Resize the media box of your PDF using a graphics program instead.
-
-\subsubsection{Fonts in Your Illustrations}
-You must embed all fonts in your graphics before including them in your LaTeX document.
-
-\subsection{References} 
-The aaai.sty file includes a set of definitions for use in formatting references with BibTeX.
-These definitions make the bibliography style fairly close to the one specified below.
-To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the author kit on the AAAI web site.
-Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:
-
-\begin{quote}
-\begin{small}
-\textbackslash bibliographystyle\{aaai\}
-\textbackslash bibliography\{bibfile1,bibfile2,...\}
-\end{small}
-\end{quote}
-
-The list of files in the \textbackslash  bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).
-
-The following commands are available for your use in citing references:
-\begin{quote}
-\begin{small}
-\textbackslash cite: Cites the given reference(s) with a full citation. This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\\
-\textbackslash shortcite: Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\\
-\textbackslash citeauthor: Cites the given reference(s) with just the author name(s) and no parentheses.\\
-\textbackslash citeyear: Cites the given reference(s) with just the date(s) and no parentheses.
-\end{small}
-\end{quote}
-
-\textbf{Warning:} The aaai.sty file is incompatible with the hyperref and natbib packages. If you use either, your references will be garbled.
-
-Formatted bibliographies should look like the following examples.
-
-\smallskip \noindent \textit{Book with Multiple Authors}\\
-Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.
-
-\smallskip \noindent \textit{Journal Article}\\
-Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.
-
-\smallskip \noindent \textit{Magazine Article}\\
-Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.
-
-\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
-Clancey, W.
-J.
-1983b.
-Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education.
-In Proceedings of the Eighth International Joint Conference on Artificial Intelligence, 556--560.
-Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.
-
-\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
-Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.
-
-\smallskip \noindent \textit{University Technical Report}\\
-Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.
-
-\smallskip \noindent \textit{Dissertation or Thesis}\\
-Clancey, W. J. 1979b. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.
-
-\smallskip \noindent \textit{Forthcoming Publication}\\
-Clancey, W. J. 1986a. The Engineering of Qualitative Models. Forthcoming.
-
-\section{Producing Reliable PDF\\Documents with \LaTeX{}}
-Generally speaking, PDF files are platform independent and accessible to everyone.
-When creating a paper for a proceedings or publication in which many PDF documents must be merged and then printed on high-resolution PostScript RIPs, several requirements must be met that are not normally of concern.
-Thus to ensure that your paper will look like it does when printed on your own machine, you must take several precautions:
-\begin{itemize}
-\item Use type 1 fonts (not type 3 fonts)
-\item Use only standard Times, Nimbus, and CMR font packages (not fonts like F3 or fonts with tildes in the names or fonts---other than Computer Modern---that are created for specific point sizes, like Times\~{}19) or fonts with strange combinations of numbers and letters
-\item Embed all fonts when producing the PDF
-\item Do not use the [T1]{fontenc} package (install the CM super fonts package instead)
-\end{itemize}
-
-\subsection{Creating Output Using PDF\LaTeX{} Is Required}
-By using the PDF\TeX{} program instead of straight \LaTeX{} or \TeX{}, you will probably avoid the type 3 font problem altogether (unless you use a package that calls for metafont).
-PDF\LaTeX{} enables you to create a PDF document directly from \LaTeX{} source.
-The one requirement of this software is that all your graphics and images must be available in a format that PDF\LaTeX{} understands (normally PDF).
-
-PDF\LaTeX{}'s default is to create documents with type 1 fonts.
-If you find that it is not doing so in your case, it is likely that one or more fonts are missing from your system or are not in a path that is known to PDF\LaTeX{}.
-
-\subsubsection{dvipdf Script}
-Scripts such as dvipdf which ostensibly bypass the Postscript intermediary should not be used since they generally do not instruct dvips to use the config.pdf file.
-
-\subsubsection{dvipdfm}
-Do not use this dvi-PDF conversion package if your document contains graphics (and we recommend you avoid it even if your document does not contain graphics).
-
-\subsection{Ghostscript}
-\LaTeX{} users should not use GhostScript to create their PDFs.
-
-\subsection{Graphics}
-If you are still finding type 3 fonts in your PDF file, look at your graphics! \LaTeX{} users should check all their imported graphics files as well for font problems.
-
-\section{Proofreading Your PDF}
-Please check all the pages of your PDF file.
-Is the page size A4?
-Are there any type 3, Identity-H, or CID fonts?
-Are all the fonts embedded?
-Are there any areas where equations or figures run into the margins?
-Did you include all your figures?
-Did you follow mixed case capitalization rules for your title?
-Did you include a copyright notice?
-Do any of the pages scroll slowly (because the graphics draw slowly on the page)?
-Are URLs underlined and in color?
-You will need to fix these common errors before submitting your file.
-
-\section{Improperly Formatted Files }
-In the past, AAAI has corrected improperly formatted files submitted by the authors.
-Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb.
-Consequently, if your file is improperly formatted, it may not be possible to include your paper in the publication.
-If time allows, however, you will be notified via e-mail (with a copy to the program chair) of the problems with your file and given the option of correcting the file yourself (and paying a late fee) or asking that AAAI have the file corrected for you, for an additional fee.
-If you opt to correct the file yourself, please note that we cannot provide you with any additional advice beyond that given in your packet.
-Files that are not corrected after a second attempt will be withdrawn.
-
-\subsection{\LaTeX{} 209 Warning}
-If you use \LaTeX{} 209 we will not be able to publish your paper. Convert your paper to \LaTeX{}2e.
-
-\section{Naming Your Electronic File}
-We request that you name your \LaTeX{} source file with your last name (family name) so that it can easily be differentiated from other submissions.
-If you name your files with the name of the event or ``aaai" or ``paper" or ``camera-ready" or some other generic or indecipherable name, you bear all risks of loss --- it is extremely likely that your file may be overwritten.
-
-\section{Submitting Your Electronic Files to AAAI}
-Submitting your files to AAAI is a two-step process. It is explained fully in the author registration and submission instructions. Please consult this document for details on how to submit your paper.
-
-\section{Inquiries} 
-If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below.
-If you have technical questions about implementation of the aaai style file, please contact an expert at your site.
-We do not provide technical support for \LaTeX{} or any other software package.
-To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.
-
-\begin{quote}
-\noindent AAAI Press\\
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\ 
-\textit{Telephone:} (650) 328-3123\\ 
-\textit{E-mail:} See the submission instructions for your particular conference or event.
-\end{quote}
-
-\section{Additional Resources}
-\LaTeX{} is a difficult program to master.
-If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems.
-(It was written for another purpose, but it has general application as well).
-It is available at www.ctan.org in the tex-archive.
-
-\section{ Acknowledgments}
-AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton.
-We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document  --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.
-
-The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press.
-Bibliography style changes were added by Sunil Issar.
-\verb+\+pubnote was added by J.
-Scott Penberthy.
-George Ferguson added support for printing the AAAI copyright slug.
-Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.
-
-\bigskip
-\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!
+\bibliographystyle{aaai}
+\bibliography{resonate_tweet}
 

### 2014-01-25 retweet_aaai.tex
20140125

@@
 \begin{quote}
-Retweeting is the core mechanism of information diffusion on Twitter.
-User modelling has been proved effective in  retweeting behavior analysis, however none studies have investigated the subjectivity of users.
-In this paper, we propose a subjective model by combining both topics of interest and opinions to model users, and demonstrate that a user is more likely to retweet a message because of subjective similarity.
+Retweeting is one of the key mechanisms of information diffusion on Twitter.
+User modelling has been proved to be effective in retweeting behavior analysis.
+However no studies have investigated the subjectivity of users.
+In this paper, we propose a novel subjective model by combining both topics of interest and opinions to model users, and demonstrate that a user is more likely to retweet a message because of subjective similarity.
 We define a novel weighting function to measure the subjective similarity. 
 By means of ANOVA test, the subjective similarity is verified to be correlated with retweeting behavior;  
-we compare our model with other content-based models in retweeting prediction and results show that our model  outperforms other models for predicting retweeting behavior; 
+we compare our model with other content-based models in retweeting prediction and the comparison results show that our model outperforms other models for predicting retweeting behavior; 
 when combining with other factors, subjective similarities give significant improvement over a off-the-shelf predicting model.
@@
 Microblogging services such as Twitter appear to play an important role in the process of information dissemination on the Internet, making it possible for messages to spread virally in a matter of minutes.
-Retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message(tweet) \cite{Jenders:2013APV}. 
+Retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message(tweet). 
 Actually almost a quarter of the tweets are retweeted from others \cite{conf/cikm/YangGCTLZS10}. 
@@
 
-Studies have tried to find factors that influence whether a tweet will be retweeted \cite{Boyd2010,Kwak:2010TSN,Suh2010}. 
-Users receive thousands of tweets on different topics every day, whether a tweet will be retweeted will depend on the subjective choice of users. 
-From the point of a user, retweeting is a process that includes reading the tweet, estimating the content and deciding to share.
-The crucial part is to estimate whether a tweet contains information interesting to the user who might find it worthy to be shared.
+Existing studies try to find factors that whether a tweet will be retweeted \cite{Boyd2010,Kwak:2010TSN,Suh2010}. 
+Users receive thousands of tweets on different topics every day, however whether a tweet will be retweeted will depend on the subjective choice of users. 
+From the point of a user, retweeting is a process that includes reading the tweet, evaluating the content and deciding whether to share.
+The crucial part is to evaluate whether a tweet contains information interesting to the user who might find that it is worthy to be shared.
 Therefore modelling the motivation of users provides an important perspective for retweeting behavior analysis. 
@@
 
-Previous studies on retweeting behavior have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{conf/icwsm/MacskassyM11,conf/wsdm/FengW13}. 
+Previous studies on retweeting analysis have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{conf/icwsm/MacskassyM11,conf/wsdm/FengW13}. 
 Specifically, researchers have tried to model users from four types of information:
 profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Who you tweet}") \cite{Pennacchiotti:icwsm11}.
-Subjective initiative nature of human determines that his behavior pattern is subjectivity driven. 
-According to theory of Biased Assimilation, people are prone to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
-Therefore, we can understand the underlying reason why a user retweet a message by modelling the subjectivity of the user.
+The subjective initiative nature of human determines that his behavior pattern is subjectivity driven. 
+According to theory of \textbf{Biased Assimilation}, people tend to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
+Therefore, we can understand the underlying reason why a user retweets a message by modelling the subjectivity of the user.
 
 Twitter has become a platform where different opinions are presented and exchanged by allowing users publish subjective messages on topics they are interested in. 
-Therefore subjectivity of a user is encoded in the millions of User-Generated Content(UGC) on Twitter. 
-In this study we explore the big text data with state-of-the-art Natural Language Processing techniques to model the subjectivity of users, and investigate whether the subjective model could benefit the retweeting behavior analysis.
-Intuitively, we put forwards that subjectivity can be represented as topics and opinions articulated in the tweets generated by users on Twitter. 
-And the probabilty a user retweets a message could be evaluated by measuring the subjective similarity between the tweet and the subjective model of the user.
+Therefore, the subjectivity of a user is encoded in the millions of User-Generated Content(UGC) on Twitter. 
+In this study we explore the big text data with state-of-the-art Natural Language Processing techniques to model the subjectivity of users, and investigate whether the subjective model can benefit the retweeting behavior analysis.
+Intuitively, we put forwards that subjectivity can be represented as topics and opinions articulated in the tweets generated by users. 
+Also the probability that a user retweets a message could be evaluated by measuring the subjective similarity between the tweet and the subjective model of the user.
 
@@
 Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historic behaviors and remarks \cite{Engbert2007}. 
-Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their languistic content \cite{stein2005subjectivity}.
+Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their linguistic contents \cite{stein2005subjectivity}.
 How to computationally model subjectivity of a user is still a challenging problem for many applications. 
@@
 Twitter allows users to show their personal subjectivity by publishing short messages, which give researchers resources to model the subjectivity of users.
-First of all, we give an formal definition for subjective model under context of Twitter.
+First of all, we give a formal definition of the subjective model under the context of Twitter.
 
@@
 \end{definition}
-The definition of subjective model given above is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from message history of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$
+Figure~\ref{fig0} is a visualized subjective model of a user. 
+\begin{figure}[htb]
+%\centering
+\includegraphics[width=3.8in,height=2.5in]{fig1.pdf}
+\caption{The left subgraph denotes two topics a user tweets about with weights $ \left( w_{u}\left( t_{23} \right)=0.43, w_{u}\left( t_{86} \right)=0.57\right)  $.
+the right subgraph denotes opinions towards two topics: for topic 23, $ ( d_{u,t_{23}} \left( o_{2} \right)=0.1, d_{u,t_{23}} \left( o_{4} \right)=0.5,d_{u,t_{23}} \left( o_{5} \right)=0.3,d_{u,t_{23}} \left( o_{6} \right)=0.1) $; for topic 86, $ \left( d_{u,t_{86}} \left( o_{4} \right)=0.66, d_{u,t_{86}} \left( o_{5} \right)=0.34 \right) $.}
+\label{fig0}
+\end{figure}
+
+The definition of a subjective model given above is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from the message histories of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$
 
@@
 \label{establishment}
-According to the definition, subjective model of a user can be represented as two distributions: the topic distribution and the sentiment distribution for each topic. 
-With state-of-the-art topic model and sentiment analysis techniques, we can establish subjective model by finding topics and opinions simultaneously. 
+According to the definition, a subjective model of a user can be represented as two distributions: the topic distribution and the sentiment distribution for each topic. 
+With the state-of-the-art topic model and sentiment analysis techniques, we can establish a subjective model by finding topics and opinions simultaneously. 
 \subsubsection{Topic Analysis}
@@
 Previous studies have tried to identify topics by finding key words \cite{Chen:2010STE}, extracting  entities \cite{Abel:2011AUM} or linking tweets to external knowledge categories \cite{conf/icwsm/MacskassyM11}.
-Recent works show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} have been efficient ways to characterize latent topics of large volume corpus.
+Recent works show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} have been efficient ways to characterize latent topics of a large volume corpus.
 Topics of LDA are broader in concept, since a single topic consists of the whole collection of related words, so we adopt the LDA topic model for topic analysis.  
 Topic analysis for all users in a global network on Twitter is a nontrivial task. 
-There are millions of users and billions of tweets associcated with these users, and the effectiveness and efficiency of topic model is a big problem.
-However, the ``following'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily", which has been observed in many social networks \cite{mcpherson2001birds}.
+There are millions of users and billions of tweets associated with these users, and the effectiveness and efficiency of the topic model is a big problem.
+However, the ``following'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily'', which has been observed in many social networks \cite{mcpherson2001birds}.
 Homophily implies that a user follows another user because of sharing common topics of interest. 
@@
 \end{definition}
-The relatively tiny size and topic homophily of ego network lower the impact of data sparsity and degrade the complexity of calculation.
+The relatively tiny size and topic homophily of an ego network lower the impact of data sparsity and degrade the complexity of calculation.
 
-Therefore we adopt a user-level LDA model to find latent topics in Local Topic Space by aggregating all tweets generated by a user into a single document just as \cite{Hong:2010EST}. 
-The result of LDA produces two multinomial distributions, with distribution $ \theta_{u} $ representing the probability distribution of a user over each topic, and distribution $ \beta_{k} $ representing the probability distribution of a topic over whole vocabulary used by all users in ego network.
+Therefore we adopt a user-level LDA model to find latent topics in a Local Topic Space by aggregating all tweets generated by a user into a single document just as \cite{Hong:2010EST}. 
+The result of LDA produces two multinomial distributions, with distribution $ \theta_{u} $ representing the probability distribution of a user over each topic, and distribution $ \beta_{k} $ representing the probability distribution of a topic over whole vocabulary used by all users in an ego network.
 
@@
 Sentiment analysis or opinion mining is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}.
-Opinions are regulated as sequential discrete values to represent sentiment strength(for example: 0 stands for negtive and 1 for positive).
+Opinions are regulated as sequential discrete values to represent sentiment strength (for example: 0 stands for negative and 1 for positive).
 Recently, researchers began to pay more and more attention to social media such as Twitter \cite{Thelwall:2010SSS,Thelwall:2012SSD,Hu:2013www} and provide effective sentiment analysis tools.
 
-SentiStrength package has been built especially to cope with sentiment analysis in short informal text of social media \cite{Thelwall:2010SSS}. 
+The SentiStrength package has been built especially to cope with sentiment analysis in short informal text in social media \cite{Thelwall:2010SSS}. 
 It combines lexicon-based approaches with sophisticated linguistic rules adapted to social media, which is suitable for analyzing sentiment of tweets.
@@
 \end{equation}
-Where $ p $ denotes the positive setiment strength and $ n $ denotes negative sentment strength.
+where $ p $ denotes the positive sentiment strength and $ n $ denotes negative sentiment strength.
 In the sentiment valence space, value 4 indicates neutral sentiment, while values above 4 indicate positive sentiment and values below 4 indicate negative sentiment.
@@
 
-As Definition~\ref{local} describes, for a user $ u $ in a global netwotk, we can extract a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $. 
-And the subjective model of each user $ u \in G_{u} $ can be concreted within the ego network. 
+As Definition~\ref{local} describes, for a user $ u $ in a global network, we can extract a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $. 
+Also the subjective model of each user $ u \in G_{u} $ can be concreted within the ego network. 
 We denote tweets set published by a user $ u $ as $ M_{u}=\left\lbrace m_{i} \vert i \in \left[ 1, \cdots, N \right]  \right\rbrace$.
-All tweets in $ M_{u} $ is concatenated to a single document $ d_{u} $ to construct Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ with LDA topic model.
+All tweets in $ M_{u} $ is concatenated to a single document $ d_{u} $ to construct Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ with the LDA topic model.
 The topic model is built with parameter $ \theta_{u} $\ representing the distribution of user $ u $ over topics he talks about, and parameter $ \beta_{k} $ represents the distribution of each topic over the vocabulary of all tweets.
 SentiStrength is applied to each tweet $ m $ in collection $ M_{u} $ and outputs sentiment strength $ s_{m} $ for tweet $ m $.
-Subjective model of user $ u $ is built the  as follows:
+Subjective model of user $ u $ is built as follows:
 \begin{itemize}
@@
 
-Many factors have been proved to influence retweeting behavior \cite{Suh2010,conf/icwsm/MacskassyM11,Comarela:2012UFA}, however few researches have investigated the subjective motivation of a user to retweet a message.
-Therefore we will study whether subjective model can help understand underlying reasons of a user's retweeting behavior.
+Many factors have been proved to affect retweeting behavior \cite{Suh2010,conf/icwsm/MacskassyM11,Comarela:2012UFA}, however few researches have investigated the subjective motivation of a user to retweet a message.
+Therefore we will study whether the subjective model can help understand underlying reasons of a user's retweeting behavior.
 Apart from the context constraints, a tweet is more likely to be retweeted by subjective users who find it worth to. 
@@
 If a tweet is published, all followers of its author will receive it in time, and followers are likely to retweet it if they find it worthwhile. 
-Under such assumption, we investigate the problem in 1-ego network for the author of target tweet. 
+Under such assumption, we investigate the problem in a 1-ego network for the author of target tweets. 
 The relation between tweet, author and followers can be illustrated as Figure~\ref{fig1}.
@@
 
-Retweeting analysis problem can be formulated as follows:
+The retweeting analysis problem can be formulated as follows:
 For each target tweet $ m $, let $ F $ denotes the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denotes   tweets the user has published.
@@
 
-In order o understand the underlying reasons why a user retweet a message, we try to simulate the subjective decision-making procedure by investigating the relationship among a tweets and subjective models of its author and followers.
+In order to understand the underlying reasons why a user retweets a message, we try to simulate the subjective decision-making procedure by investigating the relationship among a tweet and subjective models of its author and followers.
 We assume that if a tweet and the subjective models of a user are similar enough in terms of topics and opinions, the user will have a very high probability to retweet the tweet. 
@@
 
-Topic distribution of a tweet can be inferenced by applying topic model estimated from the tweets collections of users.
+A topic distribution of a tweet can be obtained by applying the topic model estimated from the tweets collections of users.
 The topic similarity between tweet and user can be calculated with methods such as the cosine distance \cite{cha2007comprehensive} or the Jensen-Shannon Divergence \cite{weng2010twitterrank} with satisfactory results.
-In our research, we adopt cosine distance to measure the topic similarity, which is defined as:
+In our research, we adopt a cosine distance to measure the topic similarity, which is defined as:
 \begin{equation}
@@
 Opinions of a tweet can be analyzed with SenStrength and the values are transformed to range $ \left[ 0,8 \right]  $  with Equation~\ref{opinionmap}.
-Opinions of a tweet towards each topic it talks about can be regarded as a distribution with 1.0 probability on a single sentiment value just as opinion dsitribution of subjective model. 
+Opinions of a tweet towards each topic it talks about can be regarded as a distribution with 1.0 probability on a single sentiment value just as opinion distribution of the subjective model. 
 Therefore opinion similarity between tweets and users is the same with similarity between two users.   
-We treate opinion as distribution over sentiment valence space with each element of the distribution represents the propotion of the corresponding strength values in the user's all sentiment values. 
-However ,values in sentiment valence space are not independent. 
+We treat opinion as distribution over sentiment valence space with each element of the distribution represents the proportion of the corresponding strength values in the user's all sentiment values. 
+However, values in sentiment valence space are not independent. 
 They are sequential and represent strength of the sentiment, for example value 8 represents more positive sentiment than value 5, and their sentiment distance is 3.
-Therefore, opinion similarity can not be calculated as the distance between two distributions.
+Therefore, opinion similarity can't be calculated as the distance between two distributions.
 Illustrated as Table~\ref{tab1}, $ user_{1} $ holds most negative opinion on a topic(with 100\% sentiment value 0), while $ user_{2} $(100\% positive sentiment value 7) and $ user_{3} $(100\% positive sentiment value 8) hold positive opinion.
@@
 \label{analysis}
-The motivation why a user retweet is complicated, and involves the tweet itself, its author and its receivers who is following its author. 
+The motivation why a user retweets is complicated, and involves the tweet itself, its author and its receivers who is following its author. 
 Figure~\ref{fig1} illustrates their relation. 
@@
 Intuitionally, a user might retweet a message if its content is close enough to his subjectivity, its author is a like-minded friend and it is original from inner subjectivity of its author. 
-In this work we will carry out a sery of experiments to demonstrate such intuition.
+In this work we will carry out a set of experiments to demonstrate such theory.
 
-\section{Experiment}
-\label{experiment}
+\section{Experiments}
+\label{experiments}
 
@@
 To form the dataset, 500 target English tweets published from September 14th, 2012 to October 1st, 2012 were monitored to find who would retweet it in the next few days. 
-And each tweet was chosen as starting point to collect at least recent 200 tweets for its author and followers.
+Also each tweet was chosen as starting point to collect at least recent 200 tweets for its author and followers.
 Overall, there are 4,5531 followers, 6,277,736 tweets, and 5214 followers who have retweeted at least one target tweet during the monitored period. 
-We extract 3,0876 users who have retweeted at least 20 times in their recent tweets to build their sujective model and study their retweeting motivations. 
+We extract 3,0876 users who have retweeted at least 20 times in their recent tweets to build their subjective model and study their retweeting motivations. 
 In order to determine the optimized values of $ \alpha $ in subjective similarities($ sim_{sub} \left( m,u \right) $, $ sim_{sub}\left( u_{a},u \right)  $, $ sim_{sub}\left( m,u_{a} \right)  $), we implemented a \textit{mini-batch gradient descent} algorithm with the users' retweeting history.
-As a result, all three subjective similarities are optimized to reflect the personalized retweeting habits of each users.
+As a result, all three subjective similarities are optimized to reflect the personalized retweeting habits of each user.
 
@@
 The significance level is conventionally used at 0.01.
-At the same time, we carry out the test by varying the number of topics in LDA as 50, 100 , 150 and 200 to determine impact of topic number. 
+At the same time, we carry out the test by varying the number of topics in LDA as 50, 100, 150 and 200 to determine impact of topic number. 
 The results are listed in Table~\ref{tab2}, 
@@
 Subjective model tries to catch the subjective motivation of users based on their tweets content, whereas other important factors associated with retweeting behavior are not considered, such as network topology and metadata of the user, etc.
-In this section, we combine subjective similarities with other important factors that other researches have demonstrated. 
+In this section, we combine subjective similarities with other important factors that other studies have demonstrated. 
 Firstly we compare the performance of our method with model of Luo \emph{et al.}~\shortcite{Luo:2013RMF}.
@@
 After combining subjective similarities, the accuracy are changing. 
-Noticing that, the most significant improvement(LUO+$ sim_{all}  $, 6.39\% improvement) is achieved by adding all three subjectivie similarities, which verifies our intuition. 
+Noticing that, the most significant improvement(LUO+$ sim_{all}  $, 6.39\% improvement) is achieved by adding all three subjective similarities, which verifies our intuition. 
 Subjective similarity between tweet and followers also gives significant improvement(LUO+$ sim_{sub} \left( m,u \right) $, 2.12\% improvement), which indicates that subjective resonation between tweet and followers can be considered as the underlying reason that elicits retweeting behavior.
@@
 \label{example}
-In this section we give an vivid description about subjective model and its ability in explaining the retweeting behavior with an example. 
-Topic and opinion of one target tweet, subjective models for its author, and two followers (one retweet it while the other does not) are shown as Figure~\ref{fig2}. 
+In this section we give a vivid description about the subjective model and its ability in explaining the retweeting behavior with an example. 
+The topic and opinion of one target tweet, subjective models for its author, and two followers (one retweet it while the other does not) are shown as Figure~\ref{fig2}. 
 The right part of each sub-figure illustrates topic distribution and the left part illustrates opinion distribution. 
@@
 Content of the tweet is:\\
-\textit{Tweet: ``Sometimes the right person for you was there all along. You just didn’t see it because the wrong one was blocking the sight''} \\
+\textit{Tweet: ``Sometimes the right person for you was there all along. You just didn't see it because the wrong one was blocking the sight''} \\
 The topic of this tweet is about ``love between people'' and the opinion is neutral, which is in accordance with the 14th topic word cloud in Figure~\ref{fig3} and sub-figure of tweet in Firgure~\ref{fig2}.
@@
 While the ``unretweeter'', has also talked about two topics (14th and 56th topic), but he is mainly interested in 14th topic and has positive opinion.
-Although two followers have same interest (the 14th topic), their different opinions elicit their different decision, which verifies subjective model can help better understand the retweeting motivation by modelling not only topics but opinions.
+Although two followers have same interest (the 14th topic), their different opinions elicit their different decisions, which verify the subjective model can help better understand the retweeting motivation by modelling not only topics but opinions.
 
@@
 
-User modelling provides researchers with insights into user's online behaviors. 
-Hannon \emph{et al.}~\shortcite{Hannon:2010} proposed that Twitter users can be modeled by tweets content and the relation of Twitter social network, while content-based approach could find similar users who are "distant" without follow relations.
-Macskassy and Michelson~\shortcite{conf/icwsm/MacskassyM11} discover user's topics of interest by leveraging Wikipedia as external knowledge to determine a common set of high-level categories that covers entities in tweets.
-Ramage \emph{et al.}~\shortcite{RamageEtAl:10} made use of topic models to analyze Twitter content at the level of individual, showing improved performance on tasks such as post filtering and user recommendation.
+User modelling provides insights into user's online behaviors. 
+Hannon \emph{et al.}~\shortcite{Hannon:2010} proposed that Twitter users can be modeled by tweets contents and the relation of Twitter social networks, while content-based approach can find similar users who are "distant" without follow relations.
+Macskassy and Michelson~\shortcite{conf/icwsm/MacskassyM11} discovered user's topics of interest by leveraging Wikipedia as external knowledge to determine a common set of high-level categories that covers entities in tweets.
+Ramage \emph{et al.}~\shortcite{RamageEtAl:10} made use of topic models to analyze Twitter contents at the level of individual, showing improved performance on tasks such as post filtering and user recommendation.
 Xu \emph{et al.}~\shortcite{Xu:2012MUP} proposed a mixture model which incorporated three important factors, namely breaking news, friends' timeline and user interest, to explain user posting behavior.
@@
 \section{Conclusion}
-In this paper, we propose subjective model to model users, and demostrate its ability in retweeting behavior analysis.
+In this paper, we propose the subjective model to predict user's behavior, and demonstrate its ability in retweeting behavior analysis.
 We assume that retweeting should be elicited by the subjective similarities among the tweet and its author and followers.
-We define subjective model formally as the combination of topic distribution and opinion distribution, and we concrete subjective model leveraging statistical topic model and sentiment analysis techniques.
-We demonstrate the effectiveness of our model for retweeting analysis problem and show that subjective model is able to reach better understanding of retweeting behavior.
+We define the subjective model formally as the combination of a topic distribution and opinion distributions over each topic, and we develop the subjective model based on the statistical topic model and sentiment analysis techniques.
+We demonstrate the effectiveness of our model for the retweeting analysis problem and show that subjective model is able to reach better understanding of retweeting behavior.
 
-In the future, we will apply subjective model to other social network analysis task such as link prediction and friend recommendation.
+In the future, we will apply the subjective model to other social network analysis task such as link prediction and friend recommendation.
 

### 2014-01-25 retweet_aaai.tex
20140127

@@
 \item with respect to the given user $ u $,  for each topic $t_{i} \in T$, its  weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, with $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
-\item opinion of the user towards topic $t_{i}$ is modeled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
+\item opinion of the user towards topic $t_{i}$ is modelled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
 \end{itemize}
 \end{definition}
-Figure~\ref{fig0} is a visualized subjective model of a user. 
+Figure~\ref{fig0} is a visualized subjective model of a user in a 100 topics space and a $ [0,8] $ sentiment valence space. 
 \begin{figure}[htb]
@@
 \hline
-TF-IDF & 60.85  \\
+TF-IDF & 62.85  \\
 entity & 68.76 \\

### 2014-01-31 retweet_aaai.tex
version2

@@
 %
-\title{Resonation Elicits Diffusion: \\Modelling Subjectivity for Retweeting Analysis}
-%\author{AAAI Press\\
-%Association for the Advancement of Artificial Intelligence\\
-%2275 East Bayshore Road, Suite 160\\
-%Palo Alto, California 94303\\
-%}
+\title{From Interests to Opinions: \\Modelling Subjectivity for Retweeting Analysis}
+\author{Songxian Xie, Jintao Tang \and Ting Wang\\
+School of Computer, National University of Defense Technology, Changsha, P.R. China\\
+\AND Ruili Wang\\
+School of Engineering and Advanced Technology, Massey University, Auckland, New Zealand\\
+\AND Kewen Wang\\
+School of Information and Communication Technology, Griffith University, Brisbane, QLD 4111 Australia\\
+}
 \maketitle
@@
 \begin{quote}
-Retweeting is one of the key mechanisms of information diffusion on Twitter.
-User modelling has been proved to be effective in retweeting behavior analysis.
-However no studies have investigated the subjectivity of users.
-In this paper, we propose a novel subjective model by combining both topics of interest and opinions to model users, and demonstrate that a user is more likely to retweet a message because of subjective similarity.
-We define a novel weighting function to measure the subjective similarity. 
-By means of ANOVA test, the subjective similarity is verified to be correlated with retweeting behavior;  
-we compare our model with other content-based models in retweeting prediction and the comparison results show that our model outperforms other models for predicting retweeting behavior; 
-when combining with other factors, subjective similarities give significant improvement over a off-the-shelf predicting model.
+Social media such as Twitter provides researchers with abundant User-Generated Content (UGC) for analyzing users' online behaviors.
+In this paper, we focus on retweeting behavior, which is one of the key mechanisms of information dissemination on Twitter.
+User modelling has been proved to be effective in previous researches. However few studies have investigated the subjectivity of users. 
+Motivated by psychological researches, we propose a novel subjectivity model by combining both topic-of-interests and opinions articulated in UGC. 
+We also define a novel weighting function to measure the subjectivity similarity, and demonstrate that a user is more likely to retweet a message because of approximate subjectivity similarity.  
+In the experiments, the subjectivity similarity is verified to be correlated with retweeting behavior by means of ANOVA test. 
+When comparing with other topic-based models in retweeting prediction, our model outperforms other models with best accuracy.
+Our model gives significant accuracy improvement over an off-the-shelf predicting model considering other factors.
 \end{quote}
@@
 Microblogging services such as Twitter appear to play an important role in the process of information dissemination on the Internet, making it possible for messages to spread virally in a matter of minutes.
-Retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message(tweet). 
-Actually almost a quarter of the tweets are retweeted from others \cite{conf/cikm/YangGCTLZS10}. 
+The retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message (i.e. tweet). 
+Actually almost a quarter of the tweets are retweeted from other users \cite{yang2010understanding}. 
 Understanding how retweeting behavior works can help explaining information dissemination on Twitter.
 
-Existing studies try to find factors that whether a tweet will be retweeted \cite{Boyd2010,Kwak:2010TSN,Suh2010}. 
-Users receive thousands of tweets on different topics every day, however whether a tweet will be retweeted will depend on the subjective choice of users. 
+There have been many studies trying to identify factors that influence whether a tweet will be retweeted \cite{boyd2010tweet,kwak2010twitter}.
+However few studies have investigated the subjective motivation of a user to retweet a message.
+The subjective initiative nature of human determines that his behavior pattern is subjectivity driven.
+Psychological researchers have identified subjectivity as the underlying factor that influences human's behaviors \cite{moore2008awareness}.
+Also according to theory of \textbf{Biased Assimilation}, people tend to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
+Users receive thousands of tweets on different topics every day, whether a tweet will be retweeted will depend on the subjective choice of users. 
 From the point of a user, retweeting is a process that includes reading the tweet, evaluating the content and deciding whether to share.
 The crucial part is to evaluate whether a tweet contains information interesting to the user who might find that it is worthy to be shared.
-Therefore modelling the motivation of users provides an important perspective for retweeting behavior analysis. 
-This research is motivated by a desire to understand what drives users of social networks to disseminate information they come across.
+Therefore modelling the subjective motivation of users will provide an important perspective for retweeting behavior analysis. 
+This research is motivated by a desire to find what drives the subjective users of social networks to disseminate information they come across.
 
-Previous studies on retweeting analysis have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{conf/icwsm/MacskassyM11,conf/wsdm/FengW13}. 
+Previous studies on retweeting analysis have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{macskassy2011people,feng2013retweet}. 
 Specifically, researchers have tried to model users from four types of information:
-profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Who you tweet}") \cite{Pennacchiotti:icwsm11}.
-The subjective initiative nature of human determines that his behavior pattern is subjectivity driven. 
-According to theory of \textbf{Biased Assimilation}, people tend to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
-Therefore, we can understand the underlying reason why a user retweets a message by modelling the subjectivity of the user.
+profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Whom you connect}") \cite{pennacchiotti2011machine}.
+Especially topics encapsulated in rich linguistic content of a user have been proved consistently dependable for behavior analysis \cite{petrovic2011rt}.
+However no studies have considered how to model the subjective aspect (``\textbf{what's your opinions}") when modelling a user.
+In this paper, we propose a novel method to model sujectivity of a user(we name it subjectivity model) by combining both the topics and opinions.
 
-Twitter has become a platform where different opinions are presented and exchanged by allowing users publish subjective messages on topics they are interested in. 
-Therefore, the subjectivity of a user is encoded in the millions of User-Generated Content(UGC) on Twitter. 
-In this study we explore the big text data with state-of-the-art Natural Language Processing techniques to model the subjectivity of users, and investigate whether the subjective model can benefit the retweeting behavior analysis.
-Intuitively, we put forwards that subjectivity can be represented as topics and opinions articulated in the tweets generated by users. 
-Also the probability that a user retweets a message could be evaluated by measuring the subjective similarity between the tweet and the subjective model of the user.
+Social media is a platform where different opinions are presented by allowing users gennerate contents on topics they are interested in. 
+The subjectivity of a user is encoded in the User-Generated Content (UGC) on Twitter. 
+Therefore, we explore the tweets a user has published to establish the subjectivity model. 
+For the retweeting analysis problem, we assume the probability a user retweets a message could be evaluated with subjectivity similarity measurement. 
+We design a novel weighting function to measure the subjectivity similarity, and propose three subjectivity similarities among a tweet, its author and followers to analyze the motivation of retweeting behaviors.
+Expertiments on Twitter dataset show that retweeting behaviors are correlated with all three subjectivity similarities, our subjectivity model outperforms topic-based user model for retweeting prediction, and the subjectivity similarities significantly improve the performance of an off-the-shelf predicting model considering other factors.
 
-\section{Subjective Model}
+The rest of the paper is organized as follows: we give the definition and establishment details of the proposed subjectivity model in the next section, and in section 3 the subjectivity similarity is defined and specified for the retweeting analysis problem, experiments of quantitative evaluation is carried out in section 4, the related works are described in section 5 and Section 6 summarizes the paper and points out future work.
+
+\section{Subjectivity Model}
 \label{subjectivemodel}
 
-Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historic behaviors and remarks \cite{Engbert2007}. 
+Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historic behaviors and remarks \cite{engbert2007agency}. 
 Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their linguistic contents \cite{stein2005subjectivity}.
-How to computationally model subjectivity of a user is still a challenging problem for many applications. 
-The advent of online social networking such as Twitter has given a new layout to the challenge.  
-Twitter allows users to show their personal subjectivity by publishing short messages, which give researchers resources to model the subjectivity of users.
-First of all, we give a formal definition of the subjective model under the context of Twitter.
+How to computationally model the subjectivity of a user is still a challenging problem. 
+The advent of online social media such as Twitter has given a new layout to the challenge.  
+Twitter allows users to show their personal subjectivity by publishing short messages, which provides researchers with data resources to model the subjectivity of users.
+First of all, we give a formal definition of the subjectivity model under the context of Twitter.
 
@@
 
-Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of directed relationships between users.
+Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of following relationships between users.
 For each user $ u \in V $, there is a tweets collection $ M_{u} $ denotes his message history.
-We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ for evaluating their opinions towards these topics.
-For the ``subjectivity'' of a user $ u $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
-\begin{definition}[Subjective Model]
-The subjective model $ P \left( u \right) $ of a user $u \in V $, is the combination of a set of topics $\left\lbrace  t_{i} \left( i \in \lbrace1 \cdots n \rbrace \right)  \right\rbrace $ the user talks about in a topic space $T$ and the user's opinion $o_{i}$ towards each topic $ t_{i} $.
+We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ to evaluate their opinions towards these topics.
+For the ``subjectivity'' of a user $ u  \in V $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
+\begin{definition}[Subjectivity Model]
+The subjectivity model $ P \left( u \right) $ of user $ u $, is the combination of topics $\left\lbrace  t_{i} \right\rbrace $ the user talks about in topic space $T$ and the user's opinions ${o_{i}}$ towards each topic evaluated in sentiment valence space $ O $.
 \begin{equation}
@@
 \begin{itemize}
-\item with respect to the given user $ u $,  for each topic $t_{i} \in T$, its  weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, with $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
+\item with respect to user $ u $, for each topic $t_{i} \in T$, its weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, subject to $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
 \item opinion of the user towards topic $t_{i}$ is modelled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
@@
 \end{definition}
-Figure~\ref{fig0} is a visualized subjective model of a user in a 100 topics space and a $ [0,8] $ sentiment valence space. 
+Figure~\ref{fig0} is a visualized subjectivity model of a user in a $ [0,100] $ topics space and a $ [0,8] $ sentiment valence space. 
 \begin{figure}[htb]
 %\centering
-\includegraphics[width=3.8in,height=2.5in]{fig1.pdf}
+\includegraphics[width=3.8in,height=2.0in]{fig1.pdf}
 \caption{The left subgraph denotes two topics a user tweets about with weights $ \left( w_{u}\left( t_{23} \right)=0.43, w_{u}\left( t_{86} \right)=0.57\right)  $.
@@
 
-The definition of a subjective model given above is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from the message histories of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$
+\subsection{Establishment of Subjectivity Model}
+\label{establishment}
 
-\subsection{Establishment of Subjective Model}
-\label{establishment}
-According to the definition, a subjective model of a user can be represented as two distributions: the topic distribution and the sentiment distribution for each topic. 
-With the state-of-the-art topic model and sentiment analysis techniques, we can establish a subjective model by finding topics and opinions simultaneously. 
+The definition of a subjectivity model is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from the message histories of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$
+
 \subsubsection{Topic Analysis}
 \label{topic}
-Previous studies have tried to identify topics by finding key words \cite{Chen:2010STE}, extracting  entities \cite{Abel:2011AUM} or linking tweets to external knowledge categories \cite{conf/icwsm/MacskassyM11}.
-Recent works show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} have been efficient ways to characterize latent topics of a large volume corpus.
-Topics of LDA are broader in concept, since a single topic consists of the whole collection of related words, so we adopt the LDA topic model for topic analysis.  
+
 Topic analysis for all users in a global network on Twitter is a nontrivial task. 
-There are millions of users and billions of tweets associated with these users, and the effectiveness and efficiency of the topic model is a big problem.
-However, the ``following'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily'', which has been observed in many social networks \cite{mcpherson2001birds}.
-Homophily implies that a user follows another user because of sharing common topics of interest. 
-According to the principle of homophily, we put forwards the concept of \textbf{Local Topic Space}: 
+There are millions of users and billions of tweets associated with these users. The effectiveness and efficiency of the topic analysis algorithm is a big problem.
+However, the ``follow'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily'', which has been observed in many social networks \cite{mcpherson2001birds}.
+Homophily implies that a user follows another user because of sharing common interests. 
+According to the principle of homophily, we put forwards the concept of \textbf{Local Topic Space} by combining topic analysis and network topology on Twitter: 
 \begin{definition}[Local Topic Space]
 \label{local}
-Let $G=\left( V,E \right) $ denotes a global social network, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
-to denote $ u $'s $ \tau $-ego network, where $ \tau $ -ego network means a subnetwork formed by $ u $'s $ \tau $-hop 
+Let $G=\left( V,E \right) $ denotes global social network, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
+to denote $ u $'s $ \tau $-ego network, where $ \tau $-ego network means subnetwork formed by $ u $'s $ \tau $-hop 
 friends in the network $ G $, and $ \tau \geqslant 1 $ is a tunable integer parameter to control the scale of the ego network. 
-In the $ \tau $-ego network of user $ u $, all users concentrate on a few topics derived from the content generated by them, and these topics form a local topic space $ T_{u} $.
+In the $ \tau $-ego network of $ u $, all users concentrate on limited topics derived from the content generated by them, and these topics form a local topic space $ T_{u} $.
 \end{definition}
-The relatively tiny size and topic homophily of an ego network lower the impact of data sparsity and degrade the complexity of calculation.
 
-Therefore we adopt a user-level LDA model to find latent topics in a Local Topic Space by aggregating all tweets generated by a user into a single document just as \cite{Hong:2010EST}. 
-The result of LDA produces two multinomial distributions, with distribution $ \theta_{u} $ representing the probability distribution of a user over each topic, and distribution $ \beta_{k} $ representing the probability distribution of a topic over whole vocabulary used by all users in an ego network.
+Previous studies have tried to identify topics from tweets by finding key words \cite{chen2010short}, extracting  entities \cite{abel2011analyzing} or linking tweets to external knowledge categories \cite{macskassy2011people}.
+Works also show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} are more effective in identifying topics from short and informal social media language \cite{hong2010empirical}, so we adopt the user-level LDA model for topic analysis.
+However, the LDA model is adapted to our local topic space assumption, and the relatively tiny size and topic homophily of an ego network lower the impact of data sparsity and degrade the calculation complexity of LDA.
 
-\subsubsection{Opinion Analysis}
+\subsubsection{Opinion Mining}
 \label{opinion}
 
-Users often express opinions towards topics of interest by publishing topic-related tweets. 
-Sentiment analysis or opinion mining is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}.
-Opinions are regulated as sequential discrete values to represent sentiment strength (for example: 0 stands for negative and 1 for positive).
-Recently, researchers began to pay more and more attention to social media such as Twitter \cite{Thelwall:2010SSS,Thelwall:2012SSD,Hu:2013www} and provide effective sentiment analysis tools.
-
-The SentiStrength package has been built especially to cope with sentiment analysis in short informal text in social media \cite{Thelwall:2010SSS}. 
-It combines lexicon-based approaches with sophisticated linguistic rules adapted to social media, which is suitable for analyzing sentiment of tweets.
-SentiStrength assigns two values to each tweet standing for sentiment strengths: a positive and a negative sentiment measurement, with $ \left[ -5,-1 \right]  $ denoting negative and $ \left[ 1,5 \right]  $ denoting positive sentiment strength.
-Sentiment assigned by SentiStrength is a fine-grained strength, which can catch fine opinion distributions in a user's subjective model.  
-For the convenience of distribution calculation, we map the output of SentiStrength to single-scaled sentiment valence space $ \left[ 0, 8 \right] $ as follows:
+In the Natural Language Processing area, opinion mining or sentiment analysis is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}.
+Opinions are often regulated as sequential discrete values to represent sentiment strength (for example: 0 stands for negative and 1 for positive).
+Sentiment analysis researches have dived into the social media language and provided effective sentiment analysis tools \cite{thelwall2010sentiment,hu2013unsupervised}.
+In this work,we just make use of the off-the-shelf work of sentiment analysis.
+The SentiStrength package has been built to cope with sentiment analysis in short informal text of social media \cite{thelwall2010sentiment}. 
+It assigns two values to each tweet standing for sentiment strengths: a positive and a negative sentiment measurement, with $ \left[ -5,-1 \right]  $ denoting negative and $ \left[ 1,5 \right]  $ denoting positive sentiment strength, which can be used to catch fine opinion distributions in a user's subjectivity model.
+For the convenience of distribution calculation, we map the output of SentiStrength to a single value in sentiment valence space $ \left[ 0, 8 \right] $ as follows:
 \begin{equation}
@@
 where $ p $ denotes the positive sentiment strength and $ n $ denotes negative sentiment strength.
-In the sentiment valence space, value 4 indicates neutral sentiment, while values above 4 indicate positive sentiment and values below 4 indicate negative sentiment.
 
-\subsubsection{Concrete Subjective Model}
+\subsubsection{Concreting Subjectivity Model}
 \label{concrete}
 
-As Definition~\ref{local} describes, for a user $ u $ in a global network, we can extract a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $. 
-Also the subjective model of each user $ u \in G_{u} $ can be concreted within the ego network. 
-We denote tweets set published by a user $ u $ as $ M_{u}=\left\lbrace m_{i} \vert i \in \left[ 1, \cdots, N \right]  \right\rbrace$.
-All tweets in $ M_{u} $ is concatenated to a single document $ d_{u} $ to construct Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ with the LDA topic model.
-The topic model is built with parameter $ \theta_{u} $\ representing the distribution of user $ u $ over topics he talks about, and parameter $ \beta_{k} $ represents the distribution of each topic over the vocabulary of all tweets.
-SentiStrength is applied to each tweet $ m $ in collection $ M_{u} $ and outputs sentiment strength $ s_{m} $ for tweet $ m $.
-Subjective model of user $ u $ is built as follows:
+As Definition~\ref{local} describes, a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $ for a user $ u $ can be extracted from global network. 
+Then the subjectivity model of each user $ u \in G_{u} $ can be concreted within the ego network. 
+$ M_{u}=\left\lbrace m_{i} \vert i \in \left[ 1, \cdots, N \right]  \right\rbrace$ denotes tweets set published by user $ u $.
+A Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ can be constructed using LDA topic model with a single document representing all concatenated tweets in $ M_{u} $.
+The topic model is built with the parameter $ \theta_{u} $\ representing the distribution of user $ u $ over topics he talks about.
+Simultaneously SentiStrength is applied to each tweet $ m \in M_{u} $ and outputs sentiment strength $ s_{m} $.
+subjectivity model of user $ u $ is built as follows:
 \begin{itemize}
-\item Firstly, for user $ u $, the corresponding $ \theta_{u} $ can be regarded as his topic distribution in the Local Topic Space $ T_{u} $, and topics he cares about are $ Z_{u}= \left\lbrace z \vert p\left( z \vert \theta_{u}\left( z \right)  \right)>0 \right\rbrace $.
-\item Secondly, in order to identify the target of opinion in each tweet, the topic model is applied to each tweet $ m $ to find topics it talks about, which are $ Z_{m} =\left\lbrace z_{m} \vert p\left( z_{m} \vert \theta, \beta, Z_{u} \right)>0 \right\rbrace $.
+\item Firstly, the corresponding parameter $ \theta_{u} $ of topic model for user $ u $ can be regarded as his topic distribution in the Local Topic Space $ T_{u} $, and the topics he talks about are $ Z_{u}= \left\lbrace z \vert p\left( z \vert \theta_{u}\left( z \right)  \right)>0 \right\rbrace $.
+\item Secondly, the topic model is applied to each tweet $ m $ to identify topics it talks about, denoted as $ Z_{m} =\left\lbrace z_{m} \vert p\left( z_{m} \vert \theta, \beta, Z_{u} \right)>0 \right\rbrace $.
 \item Thirdly, the opinion distribution of user $ u $ towards topic $ t \in Z_{u} $ could be calculated as: 
@@
 \label{opinionall}
-d_{u,t}\left( o \right) = \left\lbrace \dfrac{N_{o}}{\sum_{o \in O} N_{o}} \vert O=\left[ 0, \cdots, 8 \right] \right\rbrace 
+d_{u,t}\left( o \right) = \left\lbrace \dfrac{N_{o}}{\sum_{o \in O} N_{o}} \vert O=\left[ 0,8 \right] \right\rbrace 
 \end{equation}
@@
 \end{equation}
-where $ s_{m} $ denotes the sentiment strength of tweet $ m $. For simplicity, we assume the sentiment of tweet $ m $ is related to every topic it talks about in $ Z_{m} $.
+For simplicity, it is postulated that the sentiment of each tweet $ s_{m} $ is related to all topics it talks about in $ Z_{m} $.
+As a future work, we will adopt more sophisticated method to identify opinion towards each topic in a tweet.
 \end{itemize}
 
-Totally, we build subjective model $ P\left( u \right) $ for user $ u $ as:
-\begin{equation}
-\label{subuser}
-P\left( u \right)= \left\lbrace \left( t, p\left( z \vert \theta_{u} \right), d_{u,t}\left( o \right) \right)  \vert t \in Z_{u}, o \in O  \right\rbrace  
-\end{equation}
+\section{Retweeting Analysis With Subjectivity Model}
 
-\section{Retweeting Analysis With Subjective Model}
-
-Many factors have been proved to affect retweeting behavior \cite{Suh2010,conf/icwsm/MacskassyM11,Comarela:2012UFA}, however few researches have investigated the subjective motivation of a user to retweet a message.
-Therefore we will study whether the subjective model can help understand underlying reasons of a user's retweeting behavior.
-Apart from the context constraints, a tweet is more likely to be retweeted by subjective users who find it worth to. 
-Therefore, we are not interested in modelling the tweet by itself as other researches \cite{Naveed:2011SMC,2011:NaveedGKC,conf/icwsm/PfitznerGS12}, but how the tweet resonate with the users who might want to disseminate it.
-We assume the motivation of a user to retweet a message lies in that the user considers only the tweet content arousing his resonation without context perturbation. 
-If a tweet is published, all followers of its author will receive it in time, and followers are likely to retweet it if they find it worthwhile. 
-Under such assumption, we investigate the problem in a 1-ego network for the author of target tweets. 
-The relation between tweet, author and followers can be illustrated as Figure~\ref{fig1}.
+Many factors have been proved to affect retweeting behavior \cite{suh2010want,macskassy2011people,comarela2012understanding}, however few researches have investigated the subjective motivation of a user to retweet a message.
+Apart from the context constraints, a tweet is more likely to be retweeted by a user who find its content worth to. 
+Therefore, we are not interested in modelling the tweet by itself as other researches \cite{naveed2011searching,pfitzner2012emotional}, but the underlying reasons why a user want to disseminate it based on his subjective initiative.
+We assume that if a tweet is published, all followers of its author will receive it in time, and followers are likely to retweet it if they find it worthwhile. 
+Under such assumption, we investigate the retweeting problem within a 1-ego network for the author of target tweets. 
+In the ego network, the relation among the tweet, its author and followers can be illustrated as Figure~\ref{fig1}.
 \begin{figure}[htb]
@@
 \centering
-\includegraphics[width=2.1in,height=2.0in]{ego.pdf}
+\includegraphics[width=1.8in,height=1.6in]{ego.pdf}
 %\vspace{-4em}
-\caption{Illustration of relations between tweet, author and followers.
+\caption{Illustration of relations among tweet, author and followers.
 Author is denoted as $ u_{a} $, tweet as $ m $, followers as $ f_{i} $ and tweets of follower $ f_{i} $ as $ m_{i} $.
@@
 The retweeting analysis problem can be formulated as follows:
-For each target tweet $ m $, let $ F $ denotes the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denotes   tweets the user has published.
+For each target tweet $ m $, let $ F $ denotes the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denotes a tweet collection $ u $ has published.
 For each follower $ u_{f} \in F $, we can define a quadruple $ <u_{f}, u_{a}, m, r_{f}>  $: 
@@
 \item $ r_{f} $ is a binary label indicating whether $ m $ is retweeted by $ u_{f} $.
-\item Firstly our work focuses on building subjective model $ P\left( u \right)  $ for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace $ in the ego network with all tweets collections $ M=\left\lbrace M_{u} | u \in F \cup \left\lbrace u_{a} \right\rbrace  \right\rbrace  $.
-\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjective similarities between tweet $ m $, its author $ u_{a} $ and follower $ u_{f} $.
+\item Firstly our work focuses on building subjectivity model $ P\left( u \right)  $ for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace $ in the ego network with all tweets collections $ M=\left\lbrace M_{u} | u \in F \cup \left\lbrace u_{a} \right\rbrace  \right\rbrace  $.
+\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjectivity similarities between tweet $ m $, its author $ u_{a} $ and follower $ u_{f} $.
 \end{itemize}
 
-\subsection{Subjective Similarity}
+\subsection{Subjectivity Similarity}
 \label{similarity}
 
-In order to understand the underlying reasons why a user retweets a message, we try to simulate the subjective decision-making procedure by investigating the relationship among a tweet and subjective models of its author and followers.
-We assume that if a tweet and the subjective models of a user are similar enough in terms of topics and opinions, the user will have a very high probability to retweet the tweet. 
-We call this phenomenon as ``resonation'', and assume resonation between tweets and users will elicit retweeting behavior.
-With subjective models built for users, we can define a similarity measurement to quantify the resonation among them.
+We assume that if the tweet content and the subjectivity of a user are similar enough in terms of topics and opinions, the user will have a very high probability to adopt retweeting behavior. 
+With the subjectivity models estabilshed for the author and followers, the subjective decision-making procedure can be simulated by calculating the subjectivity similarity between the tweet and users.
+In this section, we define a novel similarity measurement to quantify the subjectivity similarity, which can be divided into topic similarity and opinion similarity. 
+For the calculating convenience, the tweet $ m $ is analyzed and a ``subjectivity model'' is established for  $ m $ according to the procedure for users. 
+Thus the subjectivity similarity calculation for tweet and user is identical with subjectivity similarity calculation between users.
 
@@
 
-A topic distribution of a tweet can be obtained by applying the topic model estimated from the tweets collections of users.
-The topic similarity between tweet and user can be calculated with methods such as the cosine distance \cite{cha2007comprehensive} or the Jensen-Shannon Divergence \cite{weng2010twitterrank} with satisfactory results.
-In our research, we adopt a cosine distance to measure the topic similarity, which is defined as:
+The similarity between two topic distributions can be calculated with methods such as the cosine distance \cite{cha2007comprehensive} or the Jensen-Shannon Divergence \cite{weng2010twitterrank} with satisfactory results.
+We adopt a cosine distance to measure the topic similarity because it performs better than other measurements in our research settings. It is defined as:
 \begin{equation}
@@
 \end{equation}
-where $ \theta_{u}$ denotes topic distribution of user $ u $ and $\theta_{m}$ denotes topic distribution of tweet $ m $.
+where $ \theta_{u}$ denotes the topic distribution of user $ u $ and $\theta_{m}$ denotes the topic distribution of tweet $ m $.
 
@@
 
-Opinions of a tweet can be analyzed with SenStrength and the values are transformed to range $ \left[ 0,8 \right]  $  with Equation~\ref{opinionmap}.
-Opinions of a tweet towards each topic it talks about can be regarded as a distribution with 1.0 probability on a single sentiment value just as opinion distribution of the subjective model. 
-Therefore opinion similarity between tweets and users is the same with similarity between two users.   
-We treat opinion as distribution over sentiment valence space with each element of the distribution represents the proportion of the corresponding strength values in the user's all sentiment values. 
-However, values in sentiment valence space are not independent. 
-They are sequential and represent strength of the sentiment, for example value 8 represents more positive sentiment than value 5, and their sentiment distance is 3.
-Therefore, opinion similarity can't be calculated as the distance between two distributions.
+Opinion in subjectivity model is treated  as a distribution over sentiment valence space with each entry of the distribution representing the proportion of the corresponding value in the overall sentiment values.
+However, values in the sentiment valence space are not independent. 
+They are sequential and represent strength of the sentiment.
 Illustrated as Table~\ref{tab1}, $ user_{1} $ holds most negative opinion on a topic(with 100\% sentiment value 0), while $ user_{2} $(100\% positive sentiment value 7) and $ user_{3} $(100\% positive sentiment value 8) hold positive opinion.
 If cosine similarity measurement is adopted to calculate opinion similarity, all similarities are 0.
-In fact $ user_{2} $ is more similar with $ user_{3} $ than $ user_{1} $ because they both hold positive opinion and their sentiment distance is much less than $ user_{1} $. 
+In fact $ user_{2} $ is more similar with $ user_{3} $ than $ user_{1} $ because they both hold positive opinion and their sentiment distance is much less than $ user_{1} $
 \begin{table}[h]
@@
 \end{table}  
-In order to accurately catch opinion similarity, we propose a novel similarity-calculating method by combining both sentiment distance and distribution similarity.
-The opinion similarity of two users or a tweet and a user on topic $ t $ can be calculated as: 
+Therefore, opinion similarity can't be calculated simply as the similarity between two distributions. 
+To accurately catch opinion similarity, we propose a novel method by combining both sentiment distance and distribution similarity.
+The opinion similarity between two users or a tweet and a user on topic $ t $ can be calculated as: 
 \begin{equation}
@@
 \end{equation}
-where $ d_{i} $ denotes the $ ith $ distribution of opinion vector, and $ v_{i} $ denotes corresponding sentiment strength value.
-Accordingly, overall opinion similarity on all topics can be calculated as normalized similarity of all opinion similarities on their common topics of interest. 
+where $ d_{i} $ denotes the $ i^{th} $ entry of opinion distribution vector, and $ v_{i} $ denotes corresponding sentiment strength value.
+Accordingly, overall opinion similarity on all topics can be calculated as normalized similarity of all opinion similarities on common topics. 
 \begin{equation}
@@
 \end{equation}
-where $ T $ denotes the common topics of interest between two users or a tweet and a user.
+where $ T $ denotes the common topics between two users or a tweet and a user, which can be regarded as the intersection between their topic-of-interests.
 
-\subsubsection{Subjective Similarity}
+\subsubsection{subjectivity similarity}
 
-Given a tweet $ t $ and a user subjective model $ P\left( u \right)  $, we can define their subjective similarity by combining topic similarity and opinion similarity as follows:
+By combining topic similarity and opinion similarity, the subjectivity similarity can be defined as follows:
 \begin{equation}
-Sim_{sub} \left( t,u \right) = \alpha * sim_{topic}+\left( 1-\alpha \right)*sim_{opinion}
+Sim_{sub} \left( t,u \right) = \lambda * sim_{topic}+\left( 1-\lambda \right)*sim_{opinion}
 \end{equation}
-where $ \alpha $ is the coefficient used to control the proportions of topic similarity and opinion similarity in the holistic subjective similarity. 
-A user cares more about topics a tweet talks about with a larger $ \alpha $, and cares more about opinions with a samller $ \alpha $. 
-A personalized $ \alpha $ can be learned from the retweeting history of a user to represent his retweeting habit.
+where $ \lambda $ is the coefficient used to control the proportions of topic similarity and opinion similarity in the holistic subjectivity similarity. 
+A user cares more about topics with a larger $ \alpha $, and cares more about opinions with a samller $ \lambda $. 
+A personalized $ \lambda $ can be learned from the retweeting history of a user, which enable us to catch subtle retweeting habit for each user and improve retweeting prediction performance of our model.
 
@@
 \label{analysis}
-The motivation why a user retweets is complicated, and involves the tweet itself, its author and its receivers who is following its author. 
-Figure~\ref{fig1} illustrates their relation. 
-The idea behind this work is that taking into account user attitudes towards his own interests can yield benefits in explaining the subjective motivation of retweeting behavior. 
-Specifically, we consider this question from three aspects: 
-(i) how similar is the tweet to the subjective model of a user in terms of topics and opinions, i.e.
-$ sim_{sub} \left( m,u \right) $, (ii) are the author and user like-minded people considering similarity of their subjective models, i.e.
-$ sim_{sub}\left( u_{a},u \right)  $, and (iii) whether the tweet is novel or original judged from its similarity with subjective model of its author, i.e.
+
+The motivation of retweeting behavior is complicated, which involves the target tweet, its author and followers who is following its author with relations illustrated as Figure~\ref{fig1}. 
+The idea behind this work is that taking into account opinions towards interests can yield benefits in explaining the subjective motivation of retweeting behavior. 
+Specifically, given a tweet $ m $, we consider this question from three aspects: 
+(i) how similar is the tweet to the subjectivity of a user in terms of topics and opinions, i.e.
+$ sim_{sub} \left( m,u \right) $, (ii) who is the like-minded people for its author among all followers considering similarity of subjectivity, i.e.
+$ sim_{sub}\left( u_{a},u \right)  $, and (iii) whether the tweet is novel or original judged from its similarity with subjectivity of its author, i.e.
 $ sim_{sub}\left( m,u_{a} \right)  $.
-Intuitionally, a user might retweet a message if its content is close enough to his subjectivity, its author is a like-minded friend and it is original from inner subjectivity of its author. 
-In this work we will carry out a set of experiments to demonstrate such theory.
+From the point of motivation, a user might retweet a message if its content is approximate to his subjectivity, its author is a like-minded friend and it is original from inner subjectivity of its author.
+In next section we carry out a set of experiments to demonstrate such motivation with the three subjectivity similarities.
 
@@
 
-\subsection{Dataset}
+\subsection{Dataset and Settings}
 We adopt the Twitter dataset of previous work \cite{Luo:2013RMF}, which was created using Twitter API \footnote{\url{https://dev.twitter.com/}}. 
-To form the dataset, 500 target English tweets published from September 14th, 2012 to October 1st, 2012 were monitored to find who would retweet it in the next few days. 
+To form the dataset, 500 target English tweets published from September 14th, 2012 to October 1st, 2012 were monitored to find who would retweet it in the next day. 
 Also each tweet was chosen as starting point to collect at least recent 200 tweets for its author and followers.
 Overall, there are 4,5531 followers, 6,277,736 tweets, and 5214 followers who have retweeted at least one target tweet during the monitored period. 
-We extract 3,0876 users who have retweeted at least 20 times in their recent tweets to build their subjective model and study their retweeting motivations. 
-In order to determine the optimized values of $ \alpha $ in subjective similarities($ sim_{sub} \left( m,u \right) $, $ sim_{sub}\left( u_{a},u \right)  $, $ sim_{sub}\left( m,u_{a} \right)  $), we implemented a \textit{mini-batch gradient descent} algorithm with the users' retweeting history.
-As a result, all three subjective similarities are optimized to reflect the personalized retweeting habits of each user.
+3,0876 users were extract who have retweeted at least 20 times in their recent tweets to build their subjectivity model and study their retweeting motivations. 
+In order to determine the optimized values of $ \lambda $ for each of the 3,0876 users in subjectivity similarities($ sim_{sub} \left( m,u \right) $, $ sim_{sub}\left( u_{a},u \right)  $, $ sim_{sub}\left( m,u_{a} \right)  $), we implemented a \textit{mini-batch gradient descent} algorithm with the user's retweeting history.
+As a result, all three subjectivity similarities are optimized to reflect the personalized retweeting habits of each user.
 
@@
 
-The first step of demonstrating our intuition is to assessing the existence of a correlation between subjective similarity and retweeting behaviour. 
-To test this correlation, we adopt a statistical hypothesis test called Analysis of Variance (ANOVA). 
+The first step of demonstrating our assumption is to assessing the existence of a correlation between subjectivity similarity and retweeting behavior. 
+To verify such correlation, we adopt a statistical hypothesis test called Analysis of Variance (ANOVA) \cite{fisher1970statistical}. 
 ANOVA tests the \textit{null hypothesis} that samples in two or more groups are derived from the same population by estimating the variance of their means. 
-This test fits our goal of testing if the distinct sets of retweeters and non-retweeters do have the same subjective similarity to a tweet that both sets are exposed to.
+This test fits our goal of testing whether the retweeters and non-retweeters have the same subjectivity similarity means. 
 The ANOVA method produces two output values: the \textit{F-ratio} and the \textit{p-value}. 
-If the difference between the means is due to chance, the expected value of the \textit{F-ratio} is 1.00. 
-If ANOVA yields a p-value lower than the significance level $ \alpha $, the \textit{null hypothesis} is rejected. 
+If the difference between the means is due to chance, the expected value of the \textit{F-ratio} is 1.00, otherwise it is larger than 1.00. 
+If ANOVA yields a p-value lower than the significance level $ \alpha $, the \textit{null hypothesis} is rejected, which means the results is considered statistically significant. 
 The significance level is conventionally used at 0.01.
 At the same time, we carry out the test by varying the number of topics in LDA as 50, 100, 150 and 200 to determine impact of topic number. 
-The results are listed in Table~\ref{tab2}, 
+The results are listed in Table~\ref{tab2}, The bold-faced entries mean that the \textit{p-value} is lower than the target significance level $ \alpha = 0.01 $.
 \begin{table}[h]
@@
 \centering
-\caption{ANOVA test for three subjective similarities}
+\caption{ANOVA test for three subjectivity similarities}
 \label{tab2}
@@
 
-Note that for the number of topics 100 and 150, all similarities yield \textit{p-values} below $ \alpha $.
-This suggests that subjective similarities can be good indicators for modeling retweeting behavior.
-Therefore we reject the \textit{null hypothesis} and accept the alternative hypothesis.
+Note that for the number of topics 100 and 150, all similarities yield \textit{p-values} below $ \alpha $ and \textit{F-ratio} above 1.00.
+This suggests that subjectivity similarities can be good indicators for modeling retweeting behavior.
 For the rest experiments, we simply set the number of topic as 100 for LDA.
@@
 
-Given that ANOVA indicated correlation between subjective similarities and retweeting behavior, we compare three similarities against other content-based similarity measurements such as TF-IDF model(modelling user with bag-of-words in his tweets) \cite{Luo:2013RMF}, entity-based model(model user with entities extracted from his tweets) and hashtag-based model(model user with hashtags used in his tweets) \cite{Abel:2011AUM}.
+In this section, we compare our model against other content-based user models such as TF-IDF model(modelling user with bag-of-words) \cite{Luo:2013RMF}, entity-based model(model user with entities extracted from the tweets) and hashtag-based model(model user with hashtags used in the tweets) \cite{abel2011analyzing}.
 
-We take 5,214 retweeters in our dataset who retweet at least one target tweet as positive instances, and randomly sample 5,214 negative instances from the 40,317 followers who do not retweet any target tweet.
-The balance dataset of all positive and negative instances is randomly divided into five parts for 5-fold cross-validation. 
-We use the logistic regression classifier of Scikit-learn machine learning package \cite{scikit-learn} for training and testing.
-Accuracy is our evaluation metric, and the result is listed in Table~\ref{tab3}.
+To avoid the bias introduced by imbalance of dataset,a dataset was constructed by taking 5,214 retweeters who retweet at least one target tweet as positive instances, and randomly sampling 5,214 negative instances from the 2,5662 followers who do not retweet any target tweet.
+The balanced dataset of all positive and negative instances was randomly divided into five parts for 5-fold cross-validation. 
+The logistic regression classifier of Scikit-learn machine learning package \cite{scikit-learn} is used for training and testing.
+The accuracy measurement is our evaluation metric, and the result is listed in Table~\ref{tab3}.
 \begin{table}[h]
 \centering
-\caption{Comparison of prediction accuracy for different models. }
+\caption{Comparison of Accuracy Performance  for Different Models.
+Significant improvement over hashtag model with $ \ast $, TF-IDF model with $ \dagger $ and entity model with $ \ddagger $ ($p < 0.05$).}
 \label{tab3}
-\begin{tabular}{|c|c|}
+\begin{tabular}{|l|l|}
 \hline
@@
 hashtag & 59.12  \\
-$ sim_{sub} \left( m,u \right) $ & 73.88\\
-$ sim_{sub}\left( u_{a},u \right)  $ & 70.04\\
-$ sim_{sub}\left( m,u_{a} \right)  $ &69.64\\
-$ sim_{all}  $ &\textbf{75.64}\\
+$ sim_{sub} \left( m,u \right) $ & 73.88   $\ast \quad \dagger \quad \ddagger $\\
+$ sim_{sub}\left( u_{a},u \right)  $ & 70.04   $\ast \quad \dagger $\\
+$ sim_{sub}\left( m,u_{a} \right)  $ & 69.64   $\ast \quad \dagger $\\
+$ sim_{all}  $ & \textbf{75.64}   $\ast \quad \dagger \quad \ddagger $\\
 \hline
@@
 
-The best accuracy(75.64\%) is achieved by the $ sim_{all}  $, for which We put all three subjective similarities into classifier to test impact of their combination.
+The best performance (75.64\%) is achieved by the $ sim_{all}  $, for which We feed all three subjectivity similarities into classifier to test the impact of their combination.
 The perfromance of TF-IDF model(60.85\%) is moderate.  
-Entity-based model(68.76\%) is very close to  $ sim_{sub}\left( u_{a},u \right)$(70.04\%) and $ sim_{sub}\left( m,u_{a} \right)  $(69.64\%), and their difference is not significant.
-While for hashtag-based model, its accuracy is the lowest(59.12\%), the reason might lie in a very low usage of hashtag in users' tweets. 
+Entity-based model (68.76\%) is very close to  $ sim_{sub}\left( u_{a},u \right)$ (70.04\%) and $ sim_{sub}\left( m,u_{a} \right)  $ (69.64\%), and their difference is not significant.
+While for hashtag-based model, its accuracy is the lowest (59.12\%), the reason might lie in a very low usage of hashtag in users' tweets. 
 The performance of $ sim_{sub} \left( m,u \right) $(73.88\%) is better than others except for $ sim_{all}  $.
-The results above show that subjective model can better help understand retweeting behavior than other user models.
+The results above show that subjectivity model can better help predicting retweeting behavior than other content-based user models.
 
-\subsubsection{Combining Evaluation With Other Factors}
+\subsubsection{Evaluation Considering Other Factors}
 \label{combining}
-Subjective model tries to catch the subjective motivation of users based on their tweets content, whereas other important factors associated with retweeting behavior are not considered, such as network topology and metadata of the user, etc.
-In this section, we combine subjective similarities with other important factors that other studies have demonstrated. 
-Firstly we compare the performance of our method with model of Luo \emph{et al.}~\shortcite{Luo:2013RMF}.
-In their work they use four feature families: ``Retweet History''(follower who retweeted a user before is likely to retweet the user again), ``Follower Status''(the number of tweets, followers, friends, listed times and being verified), ``Follower Active Time''(interaction with others) and ``Follower Interests''(bag-of-words used to model users).
-Secondly we demonstrate that performance of retweeting prediction could be improved significantly by using subjective model instead of bag-of-words model in their feature set. 
-We use the same logistic regression classifier, dataset and settings as last experiment. The feature set of Luo \emph{et al.}~\shortcite{Luo:2013RMF} is marked as ``LUO''.
-In addition, we set a baseline (marked as ``RB''), which simply predicts followers who have retweeted the author's previous tweets as retweeters of target tweet. 
+Subjectivity model tries to catch the subjective motivation of users based on their UGC, whereas other important factors associated with retweeting behavior are not considered, such as network topology and metadata of the user, etc.
+In this section, we firstly compare the performance of our method with model of Luo \emph{et al.}~\shortcite{Luo:2013RMF}.
+In their work they use four feature families: ``Retweet History''(follower who retweeted a user before is likely to retweet the user again), ``Follower Status''(the number of tweets, followers, friends, listed times and verified state), ``Follower Active Time''(interaction with other users) and ``Follower Interests''(bag-of-words model for users).
+Then we demonstrate that performance of their method could be improved by using our subjectivity model instead of bag-of-words model in their feature set. 
+We use the same classifier, dataset and settings as last section. The feature set of Luo \emph{et al.}~\shortcite{Luo:2013RMF} is marked as ``LUO''.
+In addition,as we note that followers who previously had a history of retweeting might do this in the future.
+we set a baseline (marked as ``RB''), which simply predicts followers who have retweeted the author's previous tweets as retweeters of target tweet.
 The result is listed in Table~\ref{tab4}.
@@
 \centering
-\caption{Prediction Accuracy of Different Models. Significant improvement over baseline with star($ \ast $) and LUO' model with dagger($ \ddagger $) (p$ < $0.05).}
+\caption{Prediction Accuracy of Different Models. Significant improvement over baseline with $ \ast $ and LUO' model with $ \ddagger $ ($p < 0.05$).}
 \label{tab4}
@@
 
-The accuracy of baseline is 60.85\%, and two prediction methods(``LUO'' and our model) both outperform the baseline significantly. 
+The accuracy of baseline is 60.85\%, and two prediction methods (``LUO'' and our model) both outperform the baseline significantly. 
 $ sim_{sub} \left( m,u \right) $ and $ sim_{all}  $ outperform ``LUO'' significatantly.
 
-After combining subjective similarities, the accuracy are changing. 
-Noticing that, the most significant improvement(LUO+$ sim_{all}  $, 6.39\% improvement) is achieved by adding all three subjective similarities, which verifies our intuition. 
-Subjective similarity between tweet and followers also gives significant improvement(LUO+$ sim_{sub} \left( m,u \right) $, 2.12\% improvement), which indicates that subjective resonation between tweet and followers can be considered as the underlying reason that elicits retweeting behavior.
-Adding other two subjective similarities can not improve performance significantly.
+After combining the ``LUO'' feature set with subjectivity similarities, the accuracy are changing. 
+$ sim_{sub} \left( m,u \right) $ gives a significant improvement (LUO+$ sim_{sub} \left( m,u \right) $, 2.12\% improvement) over ``LUO'' , which indicates that subjectivity similarity between tweet and followers can be considered as the underlying reason that elicits retweeting behavior.
+Adding other two subjectivity similarities ( $ sim_{sub}\left( u_{a},u \right)$ and $ sim_{sub}\left( m,u_{a} \right)$) can not improve performance significantly. 
+But noticing that, the most significant improvement(LUO+$ sim_{all}  $, 6.39\% improvement) is achieved by combining all three subjectivity similarities, which verifies our assumption that a user is more prone to retweet a message with similar subjectivity, like-minded author and original content.
 
-\subsection{Case Study}
-\label{example}
-In this section we give a vivid description about the subjective model and its ability in explaining the retweeting behavior with an example. 
-The topic and opinion of one target tweet, subjective models for its author, and two followers (one retweet it while the other does not) are shown as Figure~\ref{fig2}. 
-The right part of each sub-figure illustrates topic distribution and the left part illustrates opinion distribution. 
-It is clear that the tweet talks about the 14th topic of the local topic space. 
-\begin{figure*}[htb]
-%\setlength{\belowcaptionskip}{-0.2cm} 
-\centering%,bb=0 0 1280 960
-\includegraphics[width=6.0in,height=3.5in]{tweets10.pdf}
-%\vspace{-4em}
-\caption{Subjective model examples.}
-\label{fig2}
-\end{figure*}
-Figure~\ref{fig3} shows top words of the 14th topic, the tweets of author and followers with word cloud\footnote{We use TagCrowd (\url{http://tagcrowd.com/}) to produce word cloud.}.
-\begin{figure}[htb]
-%\setlength{\belowcaptionskip}{-0.2cm} 
-\centering
-\includegraphics[width=3.5in,height=2.2in]{text_cloud.pdf}
-%\vspace{-3em}
-\caption{Word cloud of 14th topic, publisher and followers}
-\label{fig3}
-\end{figure}
-Content of the tweet is:\\
-\textit{Tweet: ``Sometimes the right person for you was there all along. You just didn't see it because the wrong one was blocking the sight''} \\
-The topic of this tweet is about ``love between people'' and the opinion is neutral, which is in accordance with the 14th topic word cloud in Figure~\ref{fig3} and sub-figure of tweet in Firgure~\ref{fig2}.
-The author concentrates on the 14th topic, and his opinions are mainly neutral (as Figure~\ref{fig2},~\ref{fig3} show).
-As for two followers, the ``retweeter'', has published tweets about two topics (the 14th and 52nd topic) uniformly and his opinions towards the two topics are mainly neutral.
-While the ``unretweeter'', has also talked about two topics (14th and 56th topic), but he is mainly interested in 14th topic and has positive opinion.
-Although two followers have same interest (the 14th topic), their different opinions elicit their different decisions, which verify the subjective model can help better understand the retweeting motivation by modelling not only topics but opinions.
+%\subsection{Case Study}
+%\label{example}
+%In this section we give a vivid description about the subjectivity model and its ability in explaining the retweeting behavior with an example. 
+%The topic and opinion of one target tweet, subjectivity models for its author, and two followers (one retweet it while the other does not) are shown as Figure~\ref{fig2}. 
+%The right part of each sub-figure illustrates topic distribution and the left part illustrates opinion distribution. 
+%It is clear that the tweet talks about the 14th topic of the local topic space. 
+%\begin{figure*}[htb]
+%%\setlength{\belowcaptionskip}{-0.2cm} 
+%\centering%,bb=0 0 1280 960
+%\includegraphics[width=6.0in,height=3.5in]{tweets10.pdf}
+%%\vspace{-4em}
+%\caption{subjectivity model examples.}
+%\label{fig2}
+%\end{figure*}
+%Figure~\ref{fig3} shows top words of the 14th topic, the tweets of author and followers with word cloud\footnote{We use TagCrowd (\url{http://tagcrowd.com/}) to produce word cloud.}.
+%\begin{figure}[htb]
+%%\setlength{\belowcaptionskip}{-0.2cm} 
+%\centering
+%\includegraphics[width=3.5in,height=2.2in]{text_cloud.pdf}
+%%\vspace{-3em}
+%\caption{Word cloud of 14th topic, publisher and followers}
+%\label{fig3}
+%\end{figure}
+%Content of the tweet is:\\
+%\textit{Tweet: ``Sometimes the right person for you was there all along. You just didn't see it because the wrong one was blocking the sight''} \\
+%The topic of this tweet is about ``love between people'' and the opinion is neutral, which is in accordance with the 14th topic word cloud in Figure~\ref{fig3} and sub-figure of tweet in Firgure~\ref{fig2}.
+%The author concentrates on the 14th topic, and his opinions are mainly neutral (as Figure~\ref{fig2},~\ref{fig3} show).
+%As for two followers, the ``retweeter'', has published tweets about two topics (the 14th and 52nd topic) uniformly and his opinions towards the two topics are mainly neutral.
+%While the ``unretweeter'', has also talked about two topics (14th and 56th topic), but he is mainly interested in 14th topic and has positive opinion.
+%Although two followers have same interest (the 14th topic), their different opinions elicit their different decisions, which verify the subjectivity model can help better understand the retweeting motivation by modelling not only topics but opinions.
 
@@
 User modelling provides insights into user's online behaviors. 
-Hannon \emph{et al.}~\shortcite{Hannon:2010} proposed that Twitter users can be modeled by tweets contents and the relation of Twitter social networks, while content-based approach can find similar users who are "distant" without follow relations.
-Macskassy and Michelson~\shortcite{conf/icwsm/MacskassyM11} discovered user's topics of interest by leveraging Wikipedia as external knowledge to determine a common set of high-level categories that covers entities in tweets.
-Ramage \emph{et al.}~\shortcite{RamageEtAl:10} made use of topic models to analyze Twitter contents at the level of individual, showing improved performance on tasks such as post filtering and user recommendation.
-Xu \emph{et al.}~\shortcite{Xu:2012MUP} proposed a mixture model which incorporated three important factors, namely breaking news, friends' timeline and user interest, to explain user posting behavior.
-Pennacchiotti and Popescu~\shortcite{Pennacchiotti:icwsm11} proposed a most comprehensive method to model Twitter user for user classification, confirming the value of in-depth features by exploiting the UGC.
-A large body of studies have analyzed characteristics of retweeting \cite{conf/icwsm/MacskassyM11,Starbird:2012RRI}, examining factors that lead to increased retweetability \cite{Suh2010,Comarela:2012UFA} and designing models to estimate the probability of being retweeted \cite{Osborne_Lavrenko_2011,Jenders:2013APV,conf/icwsm/PfitznerGS12}.
+Hannon \emph{et al.}~\shortcite{hannon2010recommending} proposed that Twitter users can be modeled by tweets contents and the relation of Twitter social networks, while content-based approach can find similar users who are "distant" without following relations.
+Macskassy and Michelson~\shortcite{macskassy2011people} discovered user's topic-of-interest by leveraging Wikipedia as external knowledge to determine a common set of high-level categories that covers entities in tweets.
+Ramage \emph{et al.}~\shortcite{ramage10microblogs} made use of topic models to analyze Twitter contents at the level of individual, showing improved performance on tasks such as post filtering and user recommendation.
+Xu \emph{et al.}~\shortcite{xu2012modeling} proposed a mixture model which incorporated three important factors, namely breaking news, friends' timeline and user interest, to explain user posting behavior.
+Pennacchiotti and Popescu~\shortcite{pennacchiotti2011machine} proposed a most comprehensive method to model Twitter user for user classification, confirming the value of in-depth features by exploiting the UGC.
+A large body of studies have analyzed characteristics of retweeting \cite{macskassy2011people,Luo:2013RMF}, examining factors that lead to increased retweetability \cite{suh2010want,comarela2012understanding} and designing models to estimate the probability of being retweeted \cite{petrovic2011rt,jenders2013analyzing,pfitzner2012emotional}.
+However, none of the above works have considered the subjectivity of users, who are subjective initiative individuals in behavior-taking.
+We have fisrtly proposed a novel subjectivity model for users' retweeting behavior analysis.
 
 \section{Conclusion}
-In this paper, we propose the subjective model to predict user's behavior, and demonstrate its ability in retweeting behavior analysis.
-We assume that retweeting should be elicited by the subjective similarities among the tweet and its author and followers.
-We define the subjective model formally as the combination of a topic distribution and opinion distributions over each topic, and we develop the subjective model based on the statistical topic model and sentiment analysis techniques.
-We demonstrate the effectiveness of our model for the retweeting analysis problem and show that subjective model is able to reach better understanding of retweeting behavior.
+In this paper, from the point of motivation, we postulate that online behaviors of social media users are impacted by their subjectivity.
+Therefore, we propose a novel model by combining topics and opinions to model the subjectivity of users, which we name as subjectivity model.
+We design an algorithm for the establishment of subjectivity model, and to make it more efficiently, we consider only the users in an ego network instead of global network and propose a Local Topic Space concept according to the homophily principle.
+We design novel subjectivity similarity measurement in terms of topic simlarity and opinion similarity.
+The subjectivity model is applied to the retweeting behavior analysis with three subjecivity similarities among a tweet, its author and followers.
+Experiment results demonstrate the effectiveness of our model for the retweeting analysis problem and show that subjectivity model is able to reach better understanding of retweeting behavior.
 
-In the future, we will apply the subjective model to other social network analysis task such as link prediction and friend recommendation.
+In the future, we will apply the subjectivity model to other social network analysis task such as link prediction and friend recommendation.
 
 \bibliographystyle{aaai}
-\bibliography{resonate_tweet}
+\bibliography{subjectivity}
 

### 2014-02-04 retweet_aaai.tex
version3

@@
 \usepackage{url}
-\usepackage{graphicx}
+\usepackage[pdftex]{graphicx}
 \usepackage{amsmath}
@@
 \pdfinfo{
-/Title (Insert Your Title Here)
-/Author (Put All Your Authors Here, Separated by Commas)}
+/Title (From Topics to Opinions: Modelling Subjectivity for Retweeting Analysis on Twitter)
+/Author (Songxian Xie, Jintao Tang, Ting Wang, Ruili Wang, Kewen Wang)}
 \setcounter{secnumdepth}{0}  
@@
 %
-\title{From Interests to Opinions: \\Modelling Subjectivity for Retweeting Analysis}
-\author{Songxian Xie, Jintao Tang \and Ting Wang\\
-School of Computer, National University of Defense Technology, Changsha, P.R. China\\
-\AND Ruili Wang\\
-School of Engineering and Advanced Technology, Massey University, Auckland, New Zealand\\
-\AND Kewen Wang\\
-School of Information and Communication Technology, Griffith University, Brisbane, QLD 4111 Australia\\
-}
+\title{From Topics to Opinions: \\Modelling Subjectivity for Retweeting Analysis on Twitter}
+%\author{Songxian Xie, Jintao Tang \and Ting Wang\\
+%School of Computer, National University of Defense Technology, Changsha, P.R. China\\
+%\AND Ruili Wang\\
+%School of Engineering and Advanced Technology, Massey University, Auckland, New Zealand\\
+%\AND Kewen Wang\\
+%School of Information and Communication Technology, Griffith University, Brisbane, QLD 4111 Australia\\
+%}
+\nocopyright
 \maketitle
@@
 In this paper, we focus on retweeting behavior, which is one of the key mechanisms of information dissemination on Twitter.
-User modelling has been proved to be effective in previous researches. However few studies have investigated the subjectivity of users. 
-Motivated by psychological researches, we propose a novel subjectivity model by combining both topic-of-interests and opinions articulated in UGC. 
-We also define a novel weighting function to measure the subjectivity similarity, and demonstrate that a user is more likely to retweet a message because of approximate subjectivity similarity.  
-In the experiments, the subjectivity similarity is verified to be correlated with retweeting behavior by means of ANOVA test. 
-When comparing with other topic-based models in retweeting prediction, our model outperforms other models with best accuracy.
-Our model gives significant accuracy improvement over an off-the-shelf predicting model considering other factors.
+To understand the motivation of retweeting behavior, previous studies have committed to modelling interests of users with topics derived from UGC, but few have investigated opinions of users. 
+Inspired by psychological research, we propose a novel subjectivity model by combining both topics and opinions articulated in UGC. 
+We also put forward a new way to measure the subjectivity similarity between two subjectivity models, and demonstrate that a user is more likely to retweet a message with approximate subjectivity similarity.
+In the experiments, the subjectivity similarity is verified to be correlated with retweeting behavior by a statistical hypothesis test. 
+Comparing with other topic-based models in retweeting prediction, our model obtains the best evaluation performance in terms of accuracy. 
+Furthermore the proposed model gives significant accuracy improvement over an off-the-shelf predicting model considering other factors.
 \end{quote}
@@
 \label{introduction}
-\noindent Microblogging has become a center of attention in the area of social networking due to the amount of users it has attracted and the volume of messages it produces daily. 
+\noindent Microblogging has become a center of attention in the area of social media due to the amount of users it has attracted and the volume of messages it produces. 
 Microblogging services such as Twitter appear to play an important role in the process of information dissemination on the Internet, making it possible for messages to spread virally in a matter of minutes.
@@
 Psychological researchers have identified subjectivity as the underlying factor that influences human's behaviors \cite{moore2008awareness}.
-Also according to theory of \textbf{Biased Assimilation}, people tend to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
+Also according to theory of Biased Assimilation, people tend to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
 Users receive thousands of tweets on different topics every day, whether a tweet will be retweeted will depend on the subjective choice of users. 
@@
 Therefore modelling the subjective motivation of users will provide an important perspective for retweeting behavior analysis. 
-This research is motivated by a desire to find what drives the subjective users of social networks to disseminate information they come across.
+This research is motivated by a desire to find what drives users of social media to disseminate information they come across.
 
-Previous studies on retweeting analysis have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{macskassy2011people,feng2013retweet}. 
+Previous studies on retweeting analysis have shown that an enriched user model gives coherent and consistent explanation for retweeting analysis \cite{macskassy2011people,feng2013retweet}. 
 Specifically, researchers have tried to model users from four types of information:
 profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Whom you connect}") \cite{pennacchiotti2011machine}.
-Especially topics encapsulated in rich linguistic content of a user have been proved consistently dependable for behavior analysis \cite{petrovic2011rt}.
-However no studies have considered how to model the subjective aspect (``\textbf{what's your opinions}") when modelling a user.
-In this paper, we propose a novel method to model sujectivity of a user(we name it subjectivity model) by combining both the topics and opinions.
+Especially, interests of a user, i.e. topics encapsulated in User-Generated Content (UGC), have been proved consistently dependable for behavior analysis \cite{petrovic2011rt}. 
+However, to our best knowledge, few studies have considered the subjective aspect (``\textbf{what's your opinions}") when modelling a user. 
+In this paper, we propose a novel method to model subjectivity of users (defined as subjectivity model) by combining both the topics and opinions.
 
-Social media is a platform where different opinions are presented by allowing users gennerate contents on topics they are interested in. 
-The subjectivity of a user is encoded in the User-Generated Content (UGC) on Twitter. 
+Users of social media usually present their opinions by gennerating subjective content on topics they are interested in. 
+The subjectivity of a user is encoded in the UGC on Twitter. 
 Therefore, we explore the tweets a user has published to establish the subjectivity model. 
-For the retweeting analysis problem, we assume the probability a user retweets a message could be evaluated with subjectivity similarity measurement. 
-We design a novel weighting function to measure the subjectivity similarity, and propose three subjectivity similarities among a tweet, its author and followers to analyze the motivation of retweeting behaviors.
-Expertiments on Twitter dataset show that retweeting behaviors are correlated with all three subjectivity similarities, our subjectivity model outperforms topic-based user model for retweeting prediction, and the subjectivity similarities significantly improve the performance of an off-the-shelf predicting model considering other factors.
+To meet the challenges of data sparsity and computational complexity, we design an algorithm to build the subjectivity model by making use of the local network structure and homophily of social network.
+For the retweeting analysis problem, we assume that the probability a user retweets a message could be evaluated by a subjectivity similarity measurement. 
+Therefore, we put forward a new way to measure the subjectivity similarity, and use three subjectivity similarities among tweets, authors and followers to predict retweeting behavior. 
+Expertiment results show that retweeting behaviors are correlated with all three subjectivity similarities, the subjectivity model outperforms topic-based model for retweeting prediction, and the performance of an off-the-shelf predicting model is significantly improve by combining with our model.
 
-The rest of the paper is organized as follows: we give the definition and establishment details of the proposed subjectivity model in the next section, and in section 3 the subjectivity similarity is defined and specified for the retweeting analysis problem, experiments of quantitative evaluation is carried out in section 4, the related works are described in section 5 and Section 6 summarizes the paper and points out future work.
+The rest of the paper is organized as follows: firstly we give the definition and establishment details of the proposed subjectivity model, then the subjectivity similarity is defined and specified for the retweeting analysis problem, following are experiments of quantitative evaluation, the related works are described next, and we summarizes the paper and points out future work finally.
 
@@
 
-Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historic behaviors and remarks \cite{engbert2007agency}. 
+Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historicalal behaviors and remarks \cite{engbert2007agency}. 
 Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their linguistic contents \cite{stein2005subjectivity}.
-How to computationally model the subjectivity of a user is still a challenging problem. 
+However, how to computationally model the subjectivity of a user is still an open challenge. 
 The advent of online social media such as Twitter has given a new layout to the challenge.  
 Twitter allows users to show their personal subjectivity by publishing short messages, which provides researchers with data resources to model the subjectivity of users.
-First of all, we give a formal definition of the subjectivity model under the context of Twitter.
+Therefore, we give a formal definition of the subjectivity model under the context of Twitter.
 
@@
 
-Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of following relationships between users.
-For each user $ u \in V $, there is a tweets collection $ M_{u} $ denotes his message history.
-We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ to evaluate their opinions towards these topics.
-For the ``subjectivity'' of a user $ u  \in V $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
+Let $G=\left( V,E \right) $ denote a social network on Twitter, where $ V $ is a set of users, and $ E\subset V\times V $ is a set of follow relationships between users.
+For each user $ u \in V $, there is a tweets collection $ M_{u} $ denoting his message history.
+We assume that there is a topic space $ T $ containing all topics users in $ V $ talk about, and a sentiment valence space $ S $ to evaluate their opinions towards these topics.
+For the ``subjectivity'' of a user $ u  \in V $, we refer to both topics and opinions articulated in his tweets collection $ M_{u} $.  
 \begin{definition}[Subjectivity Model]
-The subjectivity model $ P \left( u \right) $ of user $ u $, is the combination of topics $\left\lbrace  t_{i} \right\rbrace $ the user talks about in topic space $T$ and the user's opinions ${o_{i}}$ towards each topic evaluated in sentiment valence space $ O $.
+The subjectivity model $ P \left( u \right) $ of user $ u $, is the combination of topics $\left\lbrace  t \right\rbrace $ the user talks about in topic space $T$ and his opinions $\left\lbrace O_{t}\right\rbrace $ towards each topic distributed over sentiment valence space $ S $.
 \begin{equation}
 \label{usermodel}
-P \left( u \right) = \lbrace \left( t_{i}, w_{u} \left( t_{i} \right), d_{u,t_{i}} \left( o_{i} \right) \right) \,\vert  t_{i} \in T, \, o_{i} \in O \rbrace
+P \left( u \right) = \lbrace \left( t, w_{u} \left( t \right), \lbrace d_{u,t} \left( s \right)|s \in S \rbrace \right) |  t \in T \rbrace
 \end{equation}
@@
 \begin{itemize}
-\item with respect to user $ u $, for each topic $t_{i} \in T$, its weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, subject to $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
-\item opinion of the user towards topic $t_{i}$ is modelled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
+\item with respect to user $ u $, for each topic $t \in T$, its weight $ w_{u} \left( t \right)$ represents the distribution of the user's interests on it, subject to $ \sum_{t=1}^{|T|}w_{u} \left( t \right)=1 $.
+\item opinion of the user towards topic $t$ is modelled as a topic-dependent sentiment distribution over sentiment valence space $ S $, $O_{t}=\lbrace d_{u,t} \left( s \right)|s \in S \rbrace $, subject to $ \sum_{s=1}^{|S|} d_{u,t} \left( s \right)=1$.
 \end{itemize}
 \end{definition}
-Figure~\ref{fig0} is a visualized subjectivity model of a user in a $ [0,100] $ topics space and a $ [0,8] $ sentiment valence space. 
-\begin{figure}[htb]
+Figure~\ref{fig0} is a visualized subjectivity model of a user in a $ [0,100] $ topic space and a $ [0,8] $ sentiment valence space. 
+\begin{figure}[t]
 %\centering
-\includegraphics[width=3.8in,height=2.0in]{fig1.pdf}
-\caption{The left subgraph denotes two topics a user tweets about with weights $ \left( w_{u}\left( t_{23} \right)=0.43, w_{u}\left( t_{86} \right)=0.57\right)  $.
-the right subgraph denotes opinions towards two topics: for topic 23, $ ( d_{u,t_{23}} \left( o_{2} \right)=0.1, d_{u,t_{23}} \left( o_{4} \right)=0.5,d_{u,t_{23}} \left( o_{5} \right)=0.3,d_{u,t_{23}} \left( o_{6} \right)=0.1) $; for topic 86, $ \left( d_{u,t_{86}} \left( o_{4} \right)=0.66, d_{u,t_{86}} \left( o_{5} \right)=0.34 \right) $.}
+\includegraphics[width=3.5in,height=1.8in]{fig1.pdf}
+\caption{Subjectivity model example.
+The left subgraph denotes interests distribution on topic 23 and 86: $ ( w_{u}\left( 23 \right)=0.43, w_{u}\left( 86 \right)=0.57)  $.
+The right subgraph denotes opinions towards two topics: $ O_{23}=( d_{u,23} \left( 2 \right)=0.1, d_{u,23} \left( 4 \right)=0.5,d_{u,23} \left( 5 \right)=0.3,d_{u,23} \left( 6 \right)=0.1) $, $ O_{86}=( d_{u,86} \left( 4 \right)=0.66, d_{u,86} \left( 5 \right)=0.34 ) $.}
 \label{fig0}
 \end{figure}
+
+Specially, the topics and opinions of a tweet can also be represented by the subjectivity model in the form of  Equation~\ref{usermodel}.
+Therefore we assume that there is also a subjectivity model for a tweet, and will not differentiate it from the subjectivity model of a user in this paper.
 
@@
 
-The definition of a subjectivity model is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from the message histories of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$
+The definition of the subjectivity model is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from the message histories of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$.
 
@@
 
-Topic analysis for all users in a global network on Twitter is a nontrivial task. 
-There are millions of users and billions of tweets associated with these users. The effectiveness and efficiency of the topic analysis algorithm is a big problem.
-However, the ``follow'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily'', which has been observed in many social networks \cite{mcpherson2001birds}.
+Topic analysis for all users in a global network on Twitter is a non-trivial task. 
+There are hundreds of millions of users and billions of tweets associated with these users. The effectiveness and efficiency of the topic analysis algorithm is a challenge.
+However, the follow relationship on Twitter is a strong indicator of a phenomenon called ``homophily'', which has been observed in many social networks \cite{mcpherson2001birds}.
 Homophily implies that a user follows another user because of sharing common interests. 
-According to the principle of homophily, we put forwards the concept of \textbf{Local Topic Space} by combining topic analysis and network topology on Twitter: 
+According to the principle of homophily, we put forwards the concept of \textbf{local topic space} by combining topic analysis with network topology on Twitter: 
 \begin{definition}[Local Topic Space]
 \label{local}
-Let $G=\left( V,E \right) $ denotes global social network, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
+In a global social network $G=\left( V,E \right) $, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
 to denote $ u $'s $ \tau $-ego network, where $ \tau $-ego network means subnetwork formed by $ u $'s $ \tau $-hop 
 friends in the network $ G $, and $ \tau \geqslant 1 $ is a tunable integer parameter to control the scale of the ego network. 
-In the $ \tau $-ego network of $ u $, all users concentrate on limited topics derived from the content generated by them, and these topics form a local topic space $ T_{u} $.
+For the $ \tau $-ego network of $ u $, all users' interests are assumed concentrate on limited topics derived from their UGC, and these topics form a local topic space $ T_{u} $.
 \end{definition}
@@
 Previous studies have tried to identify topics from tweets by finding key words \cite{chen2010short}, extracting  entities \cite{abel2011analyzing} or linking tweets to external knowledge categories \cite{macskassy2011people}.
-Works also show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} are more effective in identifying topics from short and informal social media language \cite{hong2010empirical}, so we adopt the user-level LDA model for topic analysis.
-However, the LDA model is adapted to our local topic space assumption, and the relatively tiny size and topic homophily of an ego network lower the impact of data sparsity and degrade the calculation complexity of LDA.
+However, works show that topic model such as Latent Dirichlet Allocation (LDA) \cite{blei2003latent} is more effective in identifying topics from short and informal social media language \cite{hong2010empirical}.
+Therefore we adopt the user-level LDA model for topic analysis, which regards all tweets of a user as one document of LDA.
+The LDA model is adapted to our local topic space assumption, and the relatively tiny size and topic concentration of users in an ego network lower the impact of data sparsity, and degrade the computational difficulty of LDA.
 
@@
 
-In the Natural Language Processing area, opinion mining or sentiment analysis is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}.
-Opinions are often regulated as sequential discrete values to represent sentiment strength (for example: 0 stands for negative and 1 for positive).
-Sentiment analysis researches have dived into the social media language and provided effective sentiment analysis tools \cite{thelwall2010sentiment,hu2013unsupervised}.
-In this work,we just make use of the off-the-shelf work of sentiment analysis.
-The SentiStrength package has been built to cope with sentiment analysis in short informal text of social media \cite{thelwall2010sentiment}. 
-It assigns two values to each tweet standing for sentiment strengths: a positive and a negative sentiment measurement, with $ \left[ -5,-1 \right]  $ denoting negative and $ \left[ 1,5 \right]  $ denoting positive sentiment strength, which can be used to catch fine opinion distributions in a user's subjectivity model.
-For the convenience of distribution calculation, we map the output of SentiStrength to a single value in sentiment valence space $ \left[ 0, 8 \right] $ as follows:
+In the Natural Language Processing domain, opinion mining or sentiment analysis is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}.
+Opinions are often regulated as sequential discrete values to represent sentiment strength.
+Researches on the sentiment analysis of social media have provided effective techniques and tools \cite{thelwall2010sentiment,hu2013unsupervised}.
+In this work,we just make use of the off-the-shelf work, i.e.
+SentiStrength \cite{thelwall2010sentiment}.
+SentiStrength assigns two values to each tweet standing for sentiment strengths: a negative value within $ \left[ -5,-1 \right]  $ denoting negative strength, and a positive value within $ \left[ 1,5 \right]  $ denoting  positive strength.
+The $ \left[ -5,5 \right] $ sentiment valence space can be used to catch fine opinion distributions in the subjectivity model.
+For the convenience of calculation, we map the output of SentiStrength to a single value in sentiment valence space $ \left[ 0, 8 \right] $ as follows:
 \begin{equation}
@@
 \end{equation}
-where $ p $ denotes the positive sentiment strength and $ n $ denotes negative sentiment strength.
+where $ p $ denotes the positive strength and $ n $ denotes the negative strength.
 
@@
 
-As Definition~\ref{local} describes, a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $ for a user $ u $ can be extracted from global network. 
-Then the subjectivity model of each user $ u \in G_{u} $ can be concreted within the ego network. 
-$ M_{u}=\left\lbrace m_{i} \vert i \in \left[ 1, \cdots, N \right]  \right\rbrace$ denotes tweets set published by user $ u $.
-A Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ can be constructed using LDA topic model with a single document representing all concatenated tweets in $ M_{u} $.
-The topic model is built with the parameter $ \theta_{u} $\ representing the distribution of user $ u $ over topics he talks about.
+As Definition~\ref{local} describes, a $ \tau $-ego network $ G_{u}^{\tau}=\left( U,E_{u} \right)  $ for a user $ u $ can be extracted from global network. 
+Then the subjectivity model of each user $ u \in U $ can be concreted within the ego network. 
+Let $ M_{u}$ denote tweets collection published by user $ u $, and $ M=\lbrace M_{u} |u \in U \rbrace$ denote all tweets collections of users in $ G_{u}^{\tau} $.
+A topic model $P\left(\theta,\beta | M \right) $ can be constructed with user-level LDA model, of which the parameter $\theta$ reprents user-topic distribution and $\beta$ reprents topic-vocabulary distribution.
+All topics of the topic model form a local topic space $ T_{u} $.
+The parameter $ \theta_{u} $ represents the topic distribution of user $ u $ over $ T_{u} $.
 Simultaneously SentiStrength is applied to each tweet $ m \in M_{u} $ and outputs sentiment strength $ s_{m} $.
-subjectivity model of user $ u $ is built as follows:
+The subjectivity model $P\left( u\right)  $ is established as follows:
 \begin{itemize}
-\item Firstly, the corresponding parameter $ \theta_{u} $ of topic model for user $ u $ can be regarded as his topic distribution in the Local Topic Space $ T_{u} $, and the topics he talks about are $ Z_{u}= \left\lbrace z \vert p\left( z \vert \theta_{u}\left( z \right)  \right)>0 \right\rbrace $.
-\item Secondly, the topic model is applied to each tweet $ m $ to identify topics it talks about, denoted as $ Z_{m} =\left\lbrace z_{m} \vert p\left( z_{m} \vert \theta, \beta, Z_{u} \right)>0 \right\rbrace $.
-\item Thirdly, the opinion distribution of user $ u $ towards topic $ t \in Z_{u} $ could be calculated as: 
+\item Step 1, the parameter $ \theta_{u} $ naturally corresponds to interests distribution of user $ u $ in the local topic space $ T_{u} $, and the topics $ u $ talks about are $ Z_{u}= \left\lbrace t \vert p\left( t \vert \theta_{u}\left( t \right)  \right)>0 , t \in T_{u}\right\rbrace $.
+\item Step 2, the topic model is applied to each tweet $ m $ to identify topics it talks about, denoted as $ Z_{m} =\left\lbrace t \vert p\left( t \vert \theta, \beta \right)>0 , t \in T_{u} \right\rbrace $.
+\item Step 3, the opinion distribution of user $ u $ towards topic $ t \in Z_{u} $ can be calculated as: 
 \begin{equation}
 \label{opinionall}
-d_{u,t}\left( o \right) = \left\lbrace \dfrac{N_{o}}{\sum_{o \in O} N_{o}} \vert O=\left[ 0,8 \right] \right\rbrace 
+O_{t}= \left\lbrace d_{u,t}\left( o\right)= \dfrac{N_{o}}{\sum_{o \in O} N_{o}} |o \in O, O=\left[ 0,8 \right] \right\rbrace 
 \end{equation}
-where $ N_{o} $ is the number of times user $ u $ expresses an opinion towards topic $ t $ with sentiment strength $ o $, which could be calculated as:
+where $ N_{o} $ is the number of times user $ u $ expresses an opinion towards topic $ t $ with sentiment strength $ o $, which can be calculated as:
 \begin{equation}
@@
 
+As a special case, we can also establish a subjectivity model $ P\left( m \right)  $ for a tweet $ m $ with only step 2 and 3.
+Note that the opinion distribution for each topic $ t $ of the tweet is $(d_{m,t}\left( s_{m}\right)= 1.0 )$.
+
 \section{Retweeting Analysis With Subjectivity Model}
 
-Many factors have been proved to affect retweeting behavior \cite{suh2010want,macskassy2011people,comarela2012understanding}, however few researches have investigated the subjective motivation of a user to retweet a message.
-Apart from the context constraints, a tweet is more likely to be retweeted by a user who find its content worth to. 
-Therefore, we are not interested in modelling the tweet by itself as other researches \cite{naveed2011searching,pfitzner2012emotional}, but the underlying reasons why a user want to disseminate it based on his subjective initiative.
-We assume that if a tweet is published, all followers of its author will receive it in time, and followers are likely to retweet it if they find it worthwhile. 
-Under such assumption, we investigate the retweeting problem within a 1-ego network for the author of target tweets. 
-In the ego network, the relation among the tweet, its author and followers can be illustrated as Figure~\ref{fig1}.
+Apart from the context constraints such as network topology, a tweet is more likely to be retweeted by a user who finds its content worth to. 
+Therefore, we are not interested in modelling the tweet by itself as other researchers \cite{naveed2011searching,pfitzner2012emotional}, but understanding the underlying reasons that a user disseminates the tweet based on his subjective initiative.
+We assume that if a tweet is published by the author, all followers will read it in time. 
+Under such assumption, we investigate the problem within a 1-ego network for the author of target tweet. 
+In the ego network, the relations among a tweet, the author and followers are illustrated as Figure~\ref{fig1}.
 \begin{figure}[htb]
@@
 \centering
-\includegraphics[width=1.8in,height=1.6in]{ego.pdf}
+\includegraphics[width=1.5in,height=1.1in]{ego.pdf}
 %\vspace{-4em}
@@
 
-The retweeting analysis problem can be formulated as follows:
-For each target tweet $ m $, let $ F $ denotes the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denotes a tweet collection $ u $ has published.
-For each follower $ u_{f} \in F $, we can define a quadruple $ <u_{f}, u_{a}, m, r_{f}>  $: 
+The retweeting analysis problem can be formulated as following:
+For a target tweet $ m $, let $ F $ denote the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denote a tweet collection $ u $ has published.
+For each follower $ u \in F $, we can define a quadruple $ <u, u_{a}, m, r_{f}>  $: 
 \begin{itemize}
-\item $ r_{f} $ is a binary label indicating whether $ m $ is retweeted by $ u_{f} $.
+\item $ r_{f} $ is a binary label indicating if $ m $ is retweeted by $ u $.
 \item Firstly our work focuses on building subjectivity model $ P\left( u \right)  $ for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace $ in the ego network with all tweets collections $ M=\left\lbrace M_{u} | u \in F \cup \left\lbrace u_{a} \right\rbrace  \right\rbrace  $.
-\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjectivity similarities between tweet $ m $, its author $ u_{a} $ and follower $ u_{f} $.
+\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjectivity similarities between tweet $ m $, its author $ u_{a} $ and follower $ u $.
 \end{itemize}
@@
 
-We assume that if the tweet content and the subjectivity of a user are similar enough in terms of topics and opinions, the user will have a very high probability to adopt retweeting behavior. 
-With the subjectivity models estabilshed for the author and followers, the subjective decision-making procedure can be simulated by calculating the subjectivity similarity between the tweet and users.
-In this section, we define a novel similarity measurement to quantify the subjectivity similarity, which can be divided into topic similarity and opinion similarity. 
-For the calculating convenience, the tweet $ m $ is analyzed and a ``subjectivity model'' is established for  $ m $ according to the procedure for users. 
-Thus the subjectivity similarity calculation for tweet and user is identical with subjectivity similarity calculation between users.
+It is assumed that if a tweet is similar enough with the subjectivity of a user in terms of topics and opinions, the user will have a very high probability to decide to retweet it. 
+With the subjectivity models estabilshed for the users and tweet, the subjective decision-making process can be simulated by calculating the subjectivity similarity between the tweet and users. 
+In this section, we define a novel similarity measurement to quantify the subjectivity similarity, which consists of topic similarity and opinion similarity.
 
@@
 
-The similarity between two topic distributions can be calculated with methods such as the cosine distance \cite{cha2007comprehensive} or the Jensen-Shannon Divergence \cite{weng2010twitterrank} with satisfactory results.
-We adopt a cosine distance to measure the topic similarity because it performs better than other measurements in our research settings. It is defined as:
+The similarity between two topic distributions can be calculated with methods such as the cosine distance \cite{cha2007comprehensive} or the Jensen-Shannon Divergence \cite{weng2010twitterrank}.
+We adopt the cosine distance to measure the topic similarity because it performs better than other measurements in our research settings. It is defined as:
 \begin{equation}
@@
 
-Opinion in subjectivity model is treated  as a distribution over sentiment valence space with each entry of the distribution representing the proportion of the corresponding value in the overall sentiment values.
+Opinion in the subjectivity model is treated  as a distribution over sentiment valence space with each entry of the distribution representing the proportion of the corresponding value in the overall sentiment values.
 However, values in the sentiment valence space are not independent. 
 They are sequential and represent strength of the sentiment.
-Illustrated as Table~\ref{tab1}, $ user_{1} $ holds most negative opinion on a topic(with 100\% sentiment value 0), while $ user_{2} $(100\% positive sentiment value 7) and $ user_{3} $(100\% positive sentiment value 8) hold positive opinion.
-If cosine similarity measurement is adopted to calculate opinion similarity, all similarities are 0.
-In fact $ user_{2} $ is more similar with $ user_{3} $ than $ user_{1} $ because they both hold positive opinion and their sentiment distance is much less than $ user_{1} $
-\begin{table}[h]
+Illustrated as Table~\ref{tab1}, opinion $ O_{t}^{1} $ is the most negative towards topic $ t $ (100\% of strength value 0), while opinion $ O_{t}^{2} $ (100\% of strength value 7) and $ O_{t}^{3} $ (100\% of strength value 8) are both positive.
+If the cosine similarity measurement is adopted to calculate opinion similarity, all similarities among them are 0.
+In fact $ O_{t}^{2} $ is more similar with $ O_{t}^{3} $ than $O_{t}^{1} $ because they both hold positive opinion and their sentiment distance is much less than $ O_{t}^{1} $.  
+Therefore, opinion similarity can't be calculated simply as the topic distributions. 
+To accurately catch opinion similarity, we propose a novel method by combining both sentiment distance and distribution similarity.
+The opinion similarity between two opinions on the same topic $ t $ can be calculated as: 
+\begin{equation}
+\label{opinionsim}
+sim_{opinion}^{t}(O_{t}^{1},O_{t}^{2})=\dfrac{8-|\sum_{i=0}^{8}d_{i}^{1}v_{i}-\sum_{i=0}^{8}d_{i}^{2}v_{i}|}{8}
+\end{equation}
+where $ d_{i} $ denotes the $ i^{th} $ entry of opinion distribution vector, and $ v_{i} $ denotes corresponding sentiment strength value. 
+\begin{table}[t]
 \scriptsize
 \centering
-\caption{Illustration of opinion similarity calculation}
+\caption{Illustration of opinion similarity}
 \label{tab1}
@@
 \hline
-$user_{1}$ & 1.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
+$O_{t}^{1}$ & 1.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
 \hline
-$user_{2}$ & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1.0 & 0.0 \\
+$O_{t}^{2}$ & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1.0 & 0.0 \\
 \hline
-$user_{3}$ & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1.0 \\
+$O_{t}^{3}$ & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1.0 \\
 \hline
@@
 \end{table} 
-Therefore, opinion similarity can't be calculated simply as the similarity between two distributions. 
-To accurately catch opinion similarity, we propose a novel method by combining both sentiment distance and distribution similarity.
-The opinion similarity between two users or a tweet and a user on topic $ t $ can be calculated as: 
+The similarities of opinions in Table~\ref{tab1} calculated with Equation~\ref{opinionsim} are $ sim(O_{t}^{1},O_{t}^{3})=0 $, $ sim(O_{t}^{2},O_{t}^{3})=7/8 $ and $ sim(O_{t}^{1},O_{t}^{2})=1/8 $, which are consistent with intuitive understanding.
+
+Accordingly, overall opinion similarity between two subjectivity models can be calculated as normalized similarity of all opinion similarities on common topics. 
 \begin{equation}
-sim_{opinion}^{t}(O_{1},O_{2})=\dfrac{8-|\sum_{i=0}^{8}d_{i}v_{i}-\sum_{j=0}^{8}d_{j}v_{j}|}{8}
+sim_{opinion}(u_{1},u_{2})=\dfrac{\sum_{t=1}^{|T|}sim_{opinion}^{t}(O_{t}^{1},O_{t}^{2})}{|T|}
 \end{equation}
-where $ d_{i} $ denotes the $ i^{th} $ entry of opinion distribution vector, and $ v_{i} $ denotes corresponding sentiment strength value.
-Accordingly, overall opinion similarity on all topics can be calculated as normalized similarity of all opinion similarities on common topics. 
-\begin{equation}
-sim_{opinion}(u_{1},u_{2})=\dfrac{\sum_{t=1}^{|T|}sim_{opinion}^{t}(O_{1},O_{2})}{|T|}
-\end{equation}
-where $ T $ denotes the common topics between two users or a tweet and a user, which can be regarded as the intersection between their topic-of-interests.
+where $ T $ denotes the common topics between two subjectivity models, which can be regarded as the intersection between their topic sets $ Z_{u_{1}} $ and $ Z_{u_{2}} $ described in the section of subjectivity model establishment.
 
-\subsubsection{subjectivity similarity}
+\subsubsection{Subjectivity Similarity}
 
@@
 \begin{equation}
-Sim_{sub} \left( t,u \right) = \lambda * sim_{topic}+\left( 1-\lambda \right)*sim_{opinion}
+\label{subsim}
+Sim_{sub} \left( m,u \right) = \lambda * sim_{topic}+\left( 1-\lambda \right)*sim_{opinion}
 \end{equation}
 where $ \lambda $ is the coefficient used to control the proportions of topic similarity and opinion similarity in the holistic subjectivity similarity. 
-A user cares more about topics with a larger $ \alpha $, and cares more about opinions with a samller $ \lambda $. 
-A personalized $ \lambda $ can be learned from the retweeting history of a user, which enable us to catch subtle retweeting habit for each user and improve retweeting prediction performance of our model.
+A user cares more about topics with a larger $ \lambda $, and cares more about opinions with a samller $ \lambda $. 
+A personalized $ \lambda $ can be learned from the retweeting history of a user, which enable us to catch subtle retweeting habit and improve retweeting prediction performance for each user.
 
@@
 
-The motivation of retweeting behavior is complicated, which involves the target tweet, its author and followers who is following its author with relations illustrated as Figure~\ref{fig1}. 
-The idea behind this work is that taking into account opinions towards interests can yield benefits in explaining the subjective motivation of retweeting behavior. 
-Specifically, given a tweet $ m $, we consider this question from three aspects: 
-(i) how similar is the tweet to the subjectivity of a user in terms of topics and opinions, i.e.
-$ sim_{sub} \left( m,u \right) $, (ii) who is the like-minded people for its author among all followers considering similarity of subjectivity, i.e.
-$ sim_{sub}\left( u_{a},u \right)  $, and (iii) whether the tweet is novel or original judged from its similarity with subjectivity of its author, i.e.
+The motivation of retweeting behavior is complicated, which involves the target tweet, its author and followers who is following its author, with their relations illustrated as Figure~\ref{fig1}. 
+The idea behind this work is that taking opinions towards interests into account can yield benefits in explaining the subjective motivation of retweeting behavior. 
+Specifically, given a tweet $ m $, the author $ u_{a} $ and any one of the followers $ u $, we consider the probability of user $ u $ to rewteet $ m $ from three aspects: 
+(i) how similar is the tweet $ m $ to the subjectivity of user $ u $ in terms of topics and opinions, i.e.
+$ sim_{sub} \left( m,u \right) $, (ii) how like-minded are the author $ u_{a} $ and user $ u $ considering their similarity of subjectivity, i.e.
+$ sim_{sub}\left( u_{a},u \right) $, and (iii) how original is the tweet $ m $ judged from its similarity with the subjectivity of its author $ u_{a} $, i.e.
 $ sim_{sub}\left( m,u_{a} \right)  $.
 From the point of motivation, a user might retweet a message if its content is approximate to his subjectivity, its author is a like-minded friend and it is original from inner subjectivity of its author.
-In next section we carry out a set of experiments to demonstrate such motivation with the three subjectivity similarities.
+In next section we carry out a set of experiments to inspect and verify the impact of such motivation on retweeting behavior.
 
@@
 \subsection{Dataset and Settings}
-We adopt the Twitter dataset of previous work \cite{Luo:2013RMF}, which was created using Twitter API \footnote{\url{https://dev.twitter.com/}}. 
-To form the dataset, 500 target English tweets published from September 14th, 2012 to October 1st, 2012 were monitored to find who would retweet it in the next day. 
-Also each tweet was chosen as starting point to collect at least recent 200 tweets for its author and followers.
-Overall, there are 4,5531 followers, 6,277,736 tweets, and 5214 followers who have retweeted at least one target tweet during the monitored period. 
-3,0876 users were extract who have retweeted at least 20 times in their recent tweets to build their subjectivity model and study their retweeting motivations. 
-In order to determine the optimized values of $ \lambda $ for each of the 3,0876 users in subjectivity similarities($ sim_{sub} \left( m,u \right) $, $ sim_{sub}\left( u_{a},u \right)  $, $ sim_{sub}\left( m,u_{a} \right)  $), we implemented a \textit{mini-batch gradient descent} algorithm with the user's retweeting history.
-As a result, all three subjectivity similarities are optimized to reflect the personalized retweeting habits of each user.
+We adopt the Twitter dataset of previous work \cite{Luo:2013RMF}. 
+To form the dataset, 500 target English tweets published from September 14th, 2012 to October 1st, 2012 were monitored to find who would retweet it in the next days. 
+Besides, each target tweet was set as starting point to collect at least 200 historical tweets for its author and followers.
+Overall, there are 3,0876 users who have retweeted at least 20 times in their historical tweets, 5214 of which retweet at least one target tweet during the monitored period.
+To avoid the bias introduced by dataset imbalance, an evaluation dataset was constructed by taking 5,214 retweeters as positive instances, and randomly sampling 5,214 non-retweeters as negative instances.
+All users in the evaluation dataset were separated into the 1-ego network of their target tweet's author to establish their subjectivity model.
+For subjectivity similarity, a \textit{mini-batch gradient descent} algorithm was implemented to optimize the coefficient $ \lambda $ in Equation~\ref{subsim} for each user with his retweeting history.
+Therefore, all $ \lambda $s of three subjectivity similarities ($ sim_{sub} \left( m,u \right) $, $ sim_{sub}\left( u_{a},u \right)  $, $ sim_{sub}\left( m,u_{a} \right)  $) were optimized to reflect the personalized retweeting habit.
+As a result, the optimized $ \lambda $s are used to calculate three subjectivity similarities for each user of the evaluation dataset with their own target tweets, which are used to study their retweeting behaviors.
 
-\subsection{Correlation of Subjectivity and Retweeting Behavior}
+\subsection{Correlation Test}
 
-The first step of demonstrating our assumption is to assessing the existence of a correlation between subjectivity similarity and retweeting behavior. 
-To verify such correlation, we adopt a statistical hypothesis test called Analysis of Variance (ANOVA) \cite{fisher1970statistical}. 
+First of all we want to assess the existence of a correlation between subjectivity similarity and retweeting behavior. 
+To verify such correlation, a statistical hypothesis test called Analysis of Variance (ANOVA) \cite{fisher1970statistical} is used. 
 ANOVA tests the \textit{null hypothesis} that samples in two or more groups are derived from the same population by estimating the variance of their means. 
 This test fits our goal of testing whether the retweeters and non-retweeters have the same subjectivity similarity means. 
-The ANOVA method produces two output values: the \textit{F-ratio} and the \textit{p-value}. 
+ANOVA test produces two output values: the \textit{F-ratio} and the \textit{p-value}. 
 If the difference between the means is due to chance, the expected value of the \textit{F-ratio} is 1.00, otherwise it is larger than 1.00. 
-If ANOVA yields a p-value lower than the significance level $ \alpha $, the \textit{null hypothesis} is rejected, which means the results is considered statistically significant. 
+If the p-value is lower than the significance level $ \alpha $, the \textit{null hypothesis} is rejected, which means the results is considered statistically significant. 
 The significance level is conventionally used at 0.01.
-At the same time, we carry out the test by varying the number of topics in LDA as 50, 100, 150 and 200 to determine impact of topic number. 
-The results are listed in Table~\ref{tab2}, The bold-faced entries mean that the \textit{p-value} is lower than the target significance level $ \alpha = 0.01 $.
-\begin{table}[h]
+At the same time, we carry out the test by varying the topic number of LDA for topic analysis as 50, 100, 150 and 200 to determine the impact of topic number. 
+The results are listed in Table~\ref{tab2}, The bold-faced entries mean that the \textit{p-value} is lower than significance level $ \alpha = 0.01 $.
+\begin{table}[htb]
 \scriptsize
 \centering
-\caption{ANOVA test for three subjectivity similarities}
+\caption{ANOVA results for subjectivity similarities}
 \label{tab2}
@@
 \hline
-\multirow{2}{*}{100} & \textit{F} & \textbf{22.356} & \textbf{12.240} & \textbf{14.664} \\
+\multirow{2}{*}{100} & \textit{F} & \textbf{43.892} & \textbf{31.145} & \textbf{28.466} \\
+\cline{2-5}
+  & \textit{p} &  $\mathbf{8.65e^{-11}}$  & $\mathbf{3.55e^{-08}}$ & $\mathbf{1.32e^{-09}}$\\
+\hline
+\multirow{2}{*}{150} & \textit{F} & \textbf{22.356} & \textbf{12.240} & \textbf{14.664} \\
 \cline{2-5}
   & \textit{p} &  $\mathbf{2.43e^{-08}}$  & $\mathbf{6.25e^{-06}}$ & $\mathbf{8.46e^{-07}}$\\
-\hline
-\multirow{2}{*}{150} & \textit{F} & \textbf{43.892} & \textbf{31.145} & \textbf{28.466} \\
-\cline{2-5}
-  & \textit{p} &  $\mathbf{8.65e^{-11}}$  & $\mathbf{3.55e^{-08}}$ & $\mathbf{1.32e^{-09}}$\\
 \hline
@@
 
-Note that for the number of topics 100 and 150, all similarities yield \textit{p-values} below $ \alpha $ and \textit{F-ratio} above 1.00.
-This suggests that subjectivity similarities can be good indicators for modeling retweeting behavior.
-For the rest experiments, we simply set the number of topic as 100 for LDA.
+Note that for the topic numbers of 100 and 150, all similarities yield \textit{p-values} below $ \alpha $ with \textit{F-ratio} above 1.00.
+This suggests that the subjectivity similarities could be useful features for modeling retweeting behavior.
+For the rest experiments, we set the topic number as 100 for LDA model.
 
-\subsection{Comparison With Other Models}
-\label{Comparison}
+\subsection{Performance Evaluation}
 
-In this section, we compare our model against other content-based user models such as TF-IDF model(modelling user with bag-of-words) \cite{Luo:2013RMF}, entity-based model(model user with entities extracted from the tweets) and hashtag-based model(model user with hashtags used in the tweets) \cite{abel2011analyzing}.
+To evaluate the performance of retweeting behavior prediction, we firstly compare our model against other topic-based models including TF-IDF model (modelling user interests with bag-of-words), entity-based model (modelling user interests with entities extracted from the UGC) and hashtag-based model(modelling user interests with hashtags used in the UGC) \cite{abel2011analyzing}.
+The cosine distance is used as similarity measurement for these models as topic similarity in our model for comparison.
 
-To avoid the bias introduced by imbalance of dataset,a dataset was constructed by taking 5,214 retweeters who retweet at least one target tweet as positive instances, and randomly sampling 5,214 negative instances from the 2,5662 followers who do not retweet any target tweet.
-The balanced dataset of all positive and negative instances was randomly divided into five parts for 5-fold cross-validation. 
-The logistic regression classifier of Scikit-learn machine learning package \cite{scikit-learn} is used for training and testing.
-The accuracy measurement is our evaluation metric, and the result is listed in Table~\ref{tab3}.
+In addition, subjectivity model tries to catch the subjective motivation of users based on their UGC, whereas other important factors associated with retweeting behavior are not considered, such as network topology and metadata of users.
+Therefore, our model is also compared with the method of Luo \emph{et al.}~\shortcite{Luo:2013RMF} (marked as ``LUO''), in which diffenent factors that might affect rewteeting behaviors have been considered.
+In their work they use four feature families: ``Retweet History''(follower who have retweeted a user before is likely to retweet again), ``Follower Status''(the number of tweets, followers, friends, listed times and verified state), ``Follower Active Time''(interaction with other users) and ``Follower Interests''(TF-IDF bag-of-words model for user interests).
+Based on the results of Comparative experiment, we also carry out combining experiments to demonstrate that performance of their method can be improved by using our model instead of bag-of-words model.
 \begin{table}[h]
+\scriptsize
 \centering
-\caption{Comparison of Accuracy Performance  for Different Models.
-Significant improvement over hashtag model with $ \ast $, TF-IDF model with $ \dagger $ and entity model with $ \ddagger $ ($p < 0.05$).}
+\caption{Accuracy performance. A significant improvement over baseline with $ \ast $ and LUO' model with $ \ddagger $ ($p < 0.05$).}
 \label{tab3}
-\begin{tabular}{|l|l|}
+\begin{tabular}{|l|l|l|l|}
 \hline
-Feature & Accuracy(\%) \\
+Feature & Accuracy(\%) & Feature & Accuracy(\%)\\
 \hline
-TF-IDF & 62.85   \\
-entity & 68.76  \\
-hashtag & 59.12  \\
-$ sim_{sub} \left( m,u \right) $ & 73.88   $\ast \quad \dagger \quad \ddagger $\\
-$ sim_{sub}\left( u_{a},u \right)  $ & 70.04   $\ast \quad \dagger $\\
-$ sim_{sub}\left( m,u_{a} \right)  $ & 69.64   $\ast \quad \dagger $\\
-$ sim_{all}  $ & \textbf{75.64}   $\ast \quad \dagger \quad \ddagger $\\
+RB & 60.85 & & \\
+TF-IDF & 62.85   $\ast$ & LUO & 71.76 $ \ast  $\\
+entity & 68.76  $\ast$ & LUO+entity & 72.15 $\ast$\\
+hashtag & 59.12  & LUO+hashtag & 68.44 $\ast$\\
+$ sim_{sub} \left( m,u \right) $ & 73.88   $\ast  \quad \ddagger $ &LUO+$ sim_{sub} \left( m,u \right)$ & 74.04  $ \ast \quad \ddagger $\\
+$ sim_{sub}\left( u_{a},u \right)  $ & 70.04   $\ast  $ & LUO+$ sim_{sub}\left( u_{a},u \right)$ & 70.27  $ \ast $\\
+$ sim_{sub}\left( m,u_{a} \right)  $ & 69.64   $\ast  $ & LUO+$ sim_{sub}\left( m,u_{a} \right)$ & 71.86  $ \ast $\\
+$ sim_{all}  $ & \textbf{75.64}   $\ast \quad \ddagger $ & LUO+$ sim_{all}  $ & \textbf{78.15}  $ \ast \quad \ddagger $\\
 \hline
@@
 
-The best performance (75.64\%) is achieved by the $ sim_{all}  $, for which We feed all three subjectivity similarities into classifier to test the impact of their combination.
-The perfromance of TF-IDF model(60.85\%) is moderate.  
-Entity-based model (68.76\%) is very close to  $ sim_{sub}\left( u_{a},u \right)$ (70.04\%) and $ sim_{sub}\left( m,u_{a} \right)  $ (69.64\%), and their difference is not significant.
-While for hashtag-based model, its accuracy is the lowest (59.12\%), the reason might lie in a very low usage of hashtag in users' tweets. 
-The performance of $ sim_{sub} \left( m,u \right) $(73.88\%) is better than others except for $ sim_{all}  $.
-The results above show that subjectivity model can better help predicting retweeting behavior than other content-based user models.
+The evaluation dataset is randomly divided into five parts for 5-fold cross-validation. 
+The logistic regression classifier of Scikit-learn machine learning package \cite{scikit-learn} is used for training and testing.
+It is noted that followers who previously had a history of retweeting might do this in the future, so we set a baseline (marked as ``RB''), which simply predicts users who have retweeted the author previously as the retweeters of target tweet.
+The accuracy is taken as our evaluation metric, and the results are listed in Table~\ref{tab3}, in which the compariative results are listed in the left part and the combining results in the right part.
 
-\subsubsection{Evaluation Considering Other Factors}
-\label{combining}
-Subjectivity model tries to catch the subjective motivation of users based on their UGC, whereas other important factors associated with retweeting behavior are not considered, such as network topology and metadata of the user, etc.
-In this section, we firstly compare the performance of our method with model of Luo \emph{et al.}~\shortcite{Luo:2013RMF}.
-In their work they use four feature families: ``Retweet History''(follower who retweeted a user before is likely to retweet the user again), ``Follower Status''(the number of tweets, followers, friends, listed times and verified state), ``Follower Active Time''(interaction with other users) and ``Follower Interests''(bag-of-words model for users).
-Then we demonstrate that performance of their method could be improved by using our subjectivity model instead of bag-of-words model in their feature set. 
-We use the same classifier, dataset and settings as last section. The feature set of Luo \emph{et al.}~\shortcite{Luo:2013RMF} is marked as ``LUO''.
-In addition,as we note that followers who previously had a history of retweeting might do this in the future.
-we set a baseline (marked as ``RB''), which simply predicts followers who have retweeted the author's previous tweets as retweeters of target tweet.
-The result is listed in Table~\ref{tab4}.
-\begin{table}[h]
-\centering
-\caption{Prediction Accuracy of Different Models. Significant improvement over baseline with $ \ast $ and LUO' model with $ \ddagger $ ($p < 0.05$).}
-\label{tab4}
-\begin{tabular}{|l|l|}
-\hline
-Feature Set & Accuracy(\%) \\
-\hline
-RB & 60.85  \\
-LUO & 71.76 $ \ast  $\\
-$ sim_{sub} \left( m,u \right) $ & 73.88 $ \ast \quad \ddagger $\\
-$ sim_{sub}\left( u_{a},u \right)  $ & 70.04 $ \ast  $\\
-$ sim_{sub}\left( m,u_{a} \right)  $ &69.64 $ \ast  $\\
-$ sim_{all}  $ & 75.64 $ \ast  \quad \ddagger $\\
-LUO+$ sim_{sub} \left( m,u \right)$ & 74.04  $ \ast \quad \ddagger $ \\
-LUO+$ sim_{sub}\left( u_{a},u \right)$ & 70.27  $ \ast $ \\
-LUO+$ sim_{sub}\left( m,u_{a} \right)$ & 71.86  $ \ast $ \\
-LUO+$ sim_{all}  $ & \textbf{78.15}  $ \ast \quad \ddagger $ \\
-\hline
-\end{tabular}
-\end{table}
+Firstly, all models except the hashtag-based model outperform the baseline (60.85\%) significantly.
+While for hashtag-based model, its accuracy is the lowest (59.12\%), the reason might lie in a very low usage of hashtag in a user's tweets.
 
-The accuracy of baseline is 60.85\%, and two prediction methods (``LUO'' and our model) both outperform the baseline significantly. 
-$ sim_{sub} \left( m,u \right) $ and $ sim_{all}  $ outperform ``LUO'' significatantly.
+Secondly, in the comparative results, $ sim_{sub} \left( m,u \right) $ and $ sim_{all}  $ outperform ``LUO'' (71.76\%) significatantly.
+The best performance is achieved by the $ sim_{all}  $ (75.64\%), for which we feed all three subjectivity similarities into the logistic classifier to test the impact of their combination. 
+The perfromance of TF-IDF model (62.85\%) is only better than baseline. 
+The entity-based model (68.76\%) is very close to  $ sim_{sub}\left( u_{a},u \right)$ (70.04\%) and $ sim_{sub}\left( m,u_{a} \right)  $ (69.64\%), and the difference is not significant.
 
-After combining the ``LUO'' feature set with subjectivity similarities, the accuracy are changing. 
-$ sim_{sub} \left( m,u \right) $ gives a significant improvement (LUO+$ sim_{sub} \left( m,u \right) $, 2.12\% improvement) over ``LUO'' , which indicates that subjectivity similarity between tweet and followers can be considered as the underlying reason that elicits retweeting behavior.
-Adding other two subjectivity similarities ( $ sim_{sub}\left( u_{a},u \right)$ and $ sim_{sub}\left( m,u_{a} \right)$) can not improve performance significantly. 
-But noticing that, the most significant improvement(LUO+$ sim_{all}  $, 6.39\% improvement) is achieved by combining all three subjectivity similarities, which verifies our assumption that a user is more prone to retweet a message with similar subjectivity, like-minded author and original content.
+Finally, in the combining evaluation experiment, for which the TF-TDF model of ``LUO'' feature set is replaced with other models, the results are diverse.
+$ sim_{sub} \left( m,u \right) $ gives a significant improvement (LUO+$ sim_{sub} \left( m,u \right) $, 2.12\% improvement) over ``LUO'', but other two subjectivity similarities and the entity-based model can not improve performance significantly.
+The performance is even degraded after combining with the hashtag-based model.
+But noticing that, the most significant improvement(LUO+$ sim_{all}  $, 6.39\% improvement) is achieved by combining with all subjectivity similarities.
+
+The results above show that subjectivity model can better help predicting retweeting behavior than other models and can be regarded as a better way to model the users for retweeting behavior analysis.
 
@@
 User modelling provides insights into user's online behaviors. 
-Hannon \emph{et al.}~\shortcite{hannon2010recommending} proposed that Twitter users can be modeled by tweets contents and the relation of Twitter social networks, while content-based approach can find similar users who are "distant" without following relations.
-Macskassy and Michelson~\shortcite{macskassy2011people} discovered user's topic-of-interest by leveraging Wikipedia as external knowledge to determine a common set of high-level categories that covers entities in tweets.
-Ramage \emph{et al.}~\shortcite{ramage10microblogs} made use of topic models to analyze Twitter contents at the level of individual, showing improved performance on tasks such as post filtering and user recommendation.
-Xu \emph{et al.}~\shortcite{xu2012modeling} proposed a mixture model which incorporated three important factors, namely breaking news, friends' timeline and user interest, to explain user posting behavior.
-Pennacchiotti and Popescu~\shortcite{pennacchiotti2011machine} proposed a most comprehensive method to model Twitter user for user classification, confirming the value of in-depth features by exploiting the UGC.
+Hannon \emph{et al.}~\shortcite{hannon2010recommending} proposed that users can be modeled by tweets contents and the relation of social networks, while content-based model can find similar users who are "distant" without following relations.
+Macskassy and Michelson~\shortcite{macskassy2011people} discovered user interests by leveraging Wikipedia as external knowledge to determine a common set of high-level categories that covers entities in tweets.
+Ramage \emph{et al.}~\shortcite{ramage10microblogs} made use of topic models to analyze tweet contents at the level of individual, showing improved performance on tasks such as post filtering and user recommendation.
+Xu \emph{et al.}~\shortcite{xu2012modeling} proposed a mixture model which incorporated three important factors, namely breaking news, friends' timeline and user interests, to explain user posting behavior.
+Pennacchiotti and Popescu~\shortcite{pennacchiotti2011machine} proposed a most comprehensive method to model Twitter users for user classification, confirming the value of in-depth features by exploiting the UGC.
 A large body of studies have analyzed characteristics of retweeting \cite{macskassy2011people,Luo:2013RMF}, examining factors that lead to increased retweetability \cite{suh2010want,comarela2012understanding} and designing models to estimate the probability of being retweeted \cite{petrovic2011rt,jenders2013analyzing,pfitzner2012emotional}.
-However, none of the above works have considered the subjectivity of users, who are subjective initiative individuals in behavior-taking.
-We have fisrtly proposed a novel subjectivity model for users' retweeting behavior analysis.
+However, all of the above works neglect the subjectivity of users, which is the underlying reason for the decision-making of subjective initiative individuals.
+We have fisrtly proposed a novel subjectivity model for retweeting behavior analysis.
 
 \section{Conclusion}
-In this paper, from the point of motivation, we postulate that online behaviors of social media users are impacted by their subjectivity.
-Therefore, we propose a novel model by combining topics and opinions to model the subjectivity of users, which we name as subjectivity model.
-We design an algorithm for the establishment of subjectivity model, and to make it more efficiently, we consider only the users in an ego network instead of global network and propose a Local Topic Space concept according to the homophily principle.
-We design novel subjectivity similarity measurement in terms of topic simlarity and opinion similarity.
-The subjectivity model is applied to the retweeting behavior analysis with three subjecivity similarities among a tweet, its author and followers.
-Experiment results demonstrate the effectiveness of our model for the retweeting analysis problem and show that subjectivity model is able to reach better understanding of retweeting behavior.
+In this paper, from the point of motivation, we postulate that the online behaviors of social media users are affected by their subjectivity.
+Therefore, a novel subjectivity model has been proposed by combining topics and opinions to model the subjectivity of users.
+Also an algorithm has been designed to establish the subjectivity model.
+To make the algorithm more efficiently, only the users of an ego network are considered and a local topic space is proposed according to the homophily principle.
+A novel subjectivity similarity measurement has been put forward in terms of topic simlarity and opinion similarity.
+The subjectivity model is applied to the retweeting analysis with three subjecivity similarities among tweets, authors and followers.
+Experiment results demonstrate the effectiveness of the proposed model in the retweeting analysis problem and show that subjectivity model is able to reach better understanding of retweeting behavior.
 
@@
 
+\bibliography{subjectivity}
 \bibliographystyle{aaai}
-\bibliography{subjectivity}
-
 \end{document}

### 2014-02-05 retweet_aaai.tex
version review

@@
 In this paper, we focus on retweeting behavior, which is one of the key mechanisms of information dissemination on Twitter.
-To understand the motivation of retweeting behavior, previous studies have committed to modelling interests of users with topics derived from UGC, but few have investigated opinions of users. 
+To understand the motivation of retweeting behavior, previous studies have committed to modelling interests of users with topics derived from UGC, but few have considered opinions of users. 
 Inspired by psychological research, we propose a novel subjectivity model by combining both topics and opinions articulated in UGC. 
@@
 However, to our best knowledge, few studies have considered the subjective aspect (``\textbf{what's your opinions}") when modelling a user. 
-In this paper, we propose a novel method to model subjectivity of users (defined as subjectivity model) by combining both the topics and opinions.
+In this paper, we propose a novel method to model subjectivity of users and tweets as well (defined as subjectivity model) by combining both the topics and opinions.
 
@@
 %\centering
-\includegraphics[width=3.5in,height=1.8in]{fig1.pdf}
+\includegraphics[width=3.3in,height=1.2in]{fig1.pdf}
 \caption{Subjectivity model example.
-The left subgraph denotes interests distribution on topic 23 and 86: $ ( w_{u}\left( 23 \right)=0.43, w_{u}\left( 86 \right)=0.57)  $.
-The right subgraph denotes opinions towards two topics: $ O_{23}=( d_{u,23} \left( 2 \right)=0.1, d_{u,23} \left( 4 \right)=0.5,d_{u,23} \left( 5 \right)=0.3,d_{u,23} \left( 6 \right)=0.1) $, $ O_{86}=( d_{u,86} \left( 4 \right)=0.66, d_{u,86} \left( 5 \right)=0.34 ) $.}
+The left subgraph denotes interests distribution on topic 2, 32 and 83: $ (  w_{u}\left( 2 \right)=0.08,w_{u}\left( 32 \right)=0.48, w_{u}\left( 83 \right)=0.44)  $.
+The right subgraph denotes opinions towards topics: $ O_{2}=( d_{u,2} \left( 4 \right)=0.5, d_{u,2} \left( 5 \right)=0.5)$, $O_{32}=(d_{u,32} \left( 4 \right)=1.0) $, $ O_{83}=( d_{u,83} \left( 4 \right)=0.5, d_{u,83} \left( 5 \right)=0.5 ) $.}
 \label{fig0}
@@
 
-Specially, the topics and opinions of a tweet can also be represented by the subjectivity model in the form of  Equation~\ref{usermodel}.
-Therefore we assume that there is also a subjectivity model for a tweet, and will not differentiate it from the subjectivity model of a user in this paper.
+Specially, the content of a tweet can also be represented with the subjectivity model because the topics and opinions of a tweet can be modeled as Equation~\ref{usermodel}.
 
@@
 where $ d_{i} $ denotes the $ i^{th} $ entry of opinion distribution vector, and $ v_{i} $ denotes corresponding sentiment strength value. 
-\begin{table}[t]
+\begin{table}[b]
+\setlength{\abovecaptionskip}{0pt}
 \scriptsize
@@
 \begin{table}[htb]
+\setlength{\abovecaptionskip}{0pt}
 \scriptsize
@@
 
+A vivid description about the subjectivity model and its ability in explaining the retweeting behavior can be given with an example. 
+The subjectivity models of a target tweet, its author, and two followers (one retweeter, one non-retweeter) are shown as Figure~\ref{fig2}. 
+The tweet talks about topic 14 of the local topic space, and the opinion is neutral. 
+\begin{figure}[t]
+\setlength{\belowcaptionskip}{-5pt} 
+\centering%,bb=0 0 1280 960
+\includegraphics[width=3.0in,height=4.0in]{example.pdf}
+\caption{Retweeting anlysis examples.}
+\label{fig2}
+\end{figure}
+%Figure~\ref{fig3} shows top words of the 14th topic, the tweets of author and followers with word cloud\footnote{We use TagCrowd (\url{http://tagcrowd.com/}) to produce word cloud.}.
+%\begin{figure}[htb]
+%%\setlength{\belowcaptionskip}{-0.2cm} 
+%\centering
+%\includegraphics[width=3.5in,height=2.2in]{text_cloud.pdf}
+%\caption{Word cloud of 14th topic, publisher and followers}
+%\label{fig3}
+%\end{figure}
+%Content of the tweet is:\\
+%\textit{Tweet: ``Sometimes the right person for you was there all along. You just didn't see it because the wrong one was blocking the sight''} \\
+The historical tweets of the author concentrate on the topic 14, and his opinions are mainly neutral.
+The retweeter has published 195 tweets about two topics (topic 14, 52) and his opinion towards the topic 14 is mainly neutral. 
+While the non-retweeter has also talked about two topics (14th and 56th topic) with 158 tweets, but he is mainly interested in 14th topic, and his opinion is positive. 
+Although the non-retweeter is more similar with both the tweet and author in terms of topic, the retweeter is more similar for subjectivity because his opinion is more approximate with both the tweet and author.
+The example verifies that the subjectivity model can help better understanding the retweeting behavior by modelling not only topics but also opinions.
+
 \subsection{Performance Evaluation}
@@
 \begin{table}[h]
+\setlength{\abovecaptionskip}{0pt}
 \scriptsize
@@
 The results above show that subjectivity model can better help predicting retweeting behavior than other models and can be regarded as a better way to model the users for retweeting behavior analysis.
-
 %\subsection{Case Study}
@@
 %In this section we give a vivid description about the subjectivity model and its ability in explaining the retweeting behavior with an example. 
-%The topic and opinion of one target tweet, subjectivity models for its author, and two followers (one retweet it while the other does not) are shown as Figure~\ref{fig2}. 
-%The right part of each sub-figure illustrates topic distribution and the left part illustrates opinion distribution. 
-%It is clear that the tweet talks about the 14th topic of the local topic space. 
-%\begin{figure*}[htb]
+%The subjectivity models of one target tweet, its author, and two followers (one retweeter one non-retweeter) are shown as Figure~\ref{fig2}. 
+%
+%It is clear that the tweet talks about the 14th topic of the local topic space, and the opinion is neutral. 
+%\begin{figure}[t]
 %%\setlength{\belowcaptionskip}{-0.2cm} 
 %\centering%,bb=0 0 1280 960
-%\includegraphics[width=6.0in,height=3.5in]{tweets10.pdf}
-%%\vspace{-4em}
+%\includegraphics[width=3.2in,height=5.0in]{example.pdf}
 %\caption{subjectivity model examples.}
 %\label{fig2}
-%\end{figure*}
-%Figure~\ref{fig3} shows top words of the 14th topic, the tweets of author and followers with word cloud\footnote{We use TagCrowd (\url{http://tagcrowd.com/}) to produce word cloud.}.
-%\begin{figure}[htb]
-%%\setlength{\belowcaptionskip}{-0.2cm} 
-%\centering
-%\includegraphics[width=3.5in,height=2.2in]{text_cloud.pdf}
-%%\vspace{-3em}
-%\caption{Word cloud of 14th topic, publisher and followers}
-%\label{fig3}
 %\end{figure}
-%Content of the tweet is:\\
-%\textit{Tweet: ``Sometimes the right person for you was there all along. You just didn't see it because the wrong one was blocking the sight''} \\
-%The topic of this tweet is about ``love between people'' and the opinion is neutral, which is in accordance with the 14th topic word cloud in Figure~\ref{fig3} and sub-figure of tweet in Firgure~\ref{fig2}.
-%The author concentrates on the 14th topic, and his opinions are mainly neutral (as Figure~\ref{fig2},~\ref{fig3} show).
-%As for two followers, the ``retweeter'', has published tweets about two topics (the 14th and 52nd topic) uniformly and his opinions towards the two topics are mainly neutral.
-%While the ``unretweeter'', has also talked about two topics (14th and 56th topic), but he is mainly interested in 14th topic and has positive opinion.
-%Although two followers have same interest (the 14th topic), their different opinions elicit their different decisions, which verify the subjectivity model can help better understand the retweeting motivation by modelling not only topics but opinions.
+%%Figure~\ref{fig3} shows top words of the 14th topic, the tweets of author and followers with word cloud\footnote{We use TagCrowd (\url{http://tagcrowd.com/}) to produce word cloud.}.
+%%\begin{figure}[htb]
+%%%\setlength{\belowcaptionskip}{-0.2cm} 
+%%\centering
+%%\includegraphics[width=3.5in,height=2.2in]{text_cloud.pdf}
+%%\caption{Word cloud of 14th topic, publisher and followers}
+%%\label{fig3}
+%%\end{figure}
+%%Content of the tweet is:\\
+%%\textit{Tweet: ``Sometimes the right person for you was there all along. You just didn't see it because the wrong one was blocking the sight''} \\
+%The author concentrates on the 14th topic, and his opinions are mainly neutral.
+%As for two followers, the retweeter, has published tweets about two topics (the 14th and 52nd topic) uniformly and his opinions towards the two topics are mainly neutral. 
+%While the non-retweeter, has also talked about two topics (14th and 56th topic), but he is mainly interested in 14th topic and has positive opinion. 
+%Although two followers have common interest (the 14th topic), their different opinions elicit their different decisions, which verify the subjectivity model can help better understand the retweeting behavior by modelling not only topics but opinions.
 
@@
 \section{Conclusion}
-In this paper, from the point of motivation, we postulate that the online behaviors of social media users are affected by their subjectivity.
-Therefore, a novel subjectivity model has been proposed by combining topics and opinions to model the subjectivity of users.
+Motivated by the psychological research, this paper postulates that the online behaviors of social media users are affected by their subjectivity.
+Therefore, a novel subjectivity model has been proposed by combining topics and opinions to model the subjectivity of the users and tweets as well.
 Also an algorithm has been designed to establish the subjectivity model.
 To make the algorithm more efficiently, only the users of an ego network are considered and a local topic space is proposed according to the homophily principle.
-A novel subjectivity similarity measurement has been put forward in terms of topic simlarity and opinion similarity.
-The subjectivity model is applied to the retweeting analysis with three subjecivity similarities among tweets, authors and followers.
+A novel subjectivity similarity measurement is put forward in terms of topic simlarity and opinion similarity.
+The subjectivity model has been applied to the retweeting analysis with three subjecivity similarities among tweets, authors and followers.
 Experiment results demonstrate the effectiveness of the proposed model in the retweeting analysis problem and show that subjectivity model is able to reach better understanding of retweeting behavior.

### 2014-04-15 response.txt
response

We are very excited to have been given the opportunity to respond to reviews of our manuscript, We carefully considered comments offered by the three reviewers. We want to extend our appreciation for taking the time and effort necessary to provide such insightful guidance. Herein, we respond and explain how we revise the paper based on those comments and recommendations.
Responses to the comments of Reviewer #1 
1. [I don't see it as being impactful or of general interest to the AI community.] 
 Response: We apologize for the confusion caused because we haven't state the motivation and significance of our work clearly. In fact, we have investigated the reason why one diffuses information by modelling the subjectivity of a person with state-of-the-art AI researches. Specifically, we adopt topic model and sentiment analysis techniques of NLP to find latent clues such as topics and opinions from user-generated content, and use machine learning algorithms to train and predict based on the data we collect from Twitter. But the data may not constraint to social media, the model we have proposed can be adapted to other resources which can be used to mine the interests and opinions of users. The comment is very valuable and reminds us to make it more clear in the revision of the paper. 
2. [The clarity of the paper had some problems.]
Response:Thank you very much for such insightful comment and the problems are fixed during the revision of our paper.

Responses to the comments of Reviewer #2 
[several problems in the section where the subjectivity similarity is presented and defined.]
Response: Thank you for listing all the problems. In the revision, we have fixed all of them, and answered all the questions in our paper. 
In the topic similarity in (6), theta_m and theta_u are parameters learnt by LDA model representing topic distributions of users m and u;
In opinion similarity (7), d_i is the i^{th} entry of opinion distribution vector, and v_i denotes corresponding sentiment strength value, in the example of opinion distribution O^2, d_7=1.0, v_7=7;
The subjectivity similarity (9) is the general definition of subjectivity similarity among tweets, authors and followers, where parameters u and m may represent tweets, or authors, or followers;
In the Retweeting analysis paragraph, the sim_{sub} functions with  parameters represent subjectivity similarity between tweet and author, between tweet and a follower, and between author and a follower.

Responses to the comments of Reviewer #3
[the paper lacks comparison with Topic Sentiment Mixture (TSM) models.]
Response:This is a great point, We have cited this model in the related works, which is a very interesting work on sentiment analysis, and proved very useful especially in blogsphere. However, we didn't clearly clarify the diffrent between our model and TSM.
We will refine our paper to make the comparison more clear as follow.Sentiment analysis of tweets is more complicated than blogs or reviews. While TSM model try to train a general word-sentiment distribution model to determine the sentiment toward a topic, sentiment of a tweet is determined not only by normal words but also by the special characteristics of Twitter language such as emoticon, capitalized words，repeated letters, exclamation mark, which can not be easily modeled with probabilistic distribution, but can be modeled by transforming them to rules as Sentistrength has done. So we think that our method can better adapt to Twitter language and output more precise sentiment of a tweet. Besides, we want to get a more fine-grained sentiment to reflect the subtle opinion similarity, and the TSM model can only give relative coverage of the neurtral, positive, and negative opinions. But it is a good suggestion for our future research to realize our model in a mixture way as TSM by combining the characteristics of tweets, and we will compare such a model with TSM model.

### 2014-04-15 response_0321.txt
response

We appreciate the thorough reviews by the reviewers. Here are our responses:
Responses to Review 1:
1.The motivation of this research is to develop a new AI approach to investigate why one diffuses. Specifically, we adopt the topic model and sentiment analysis techniques in NLP to find latent clues such as  topics and opinions from user-generated contents, and use machine learning algorithms to train and predict on the data collected from Twitter. Obviously, this method we have proposed can be applied not only to social media, but also to other resources such as comments and news to mine the interests and opinions of users. These are impactful or of general interest to the AI community. We will further clarify the motivation more clearly in the revision of the manuscript.
2.For the problems of clarity, We will carefully revise the manuscript to make it clear.

Responses to Review 2:
1.We will fix and explain all the problems about the subjectivity similarity in the revision. 
Specifically, in (6), theta_m and theta_u are parameters learnt by LDA model representing topic distributions of users m and u;
In (7), d_i is the i^{th} entry of opinion distribution, and v_i denotes corresponding sentiment strength value, in the example of opinion distribution O^2, d_7=1.0, v_7=7;
The (9) is the general definition of subjectivity similarity among tweets, authors and followers, where u and m may represent tweets, or authors, or followers;
In the Retweeting analysis paragraph, sim_{sub} with different parameters represent different subjectivity similarity between tweet and author, between tweet and a follower, and between author and a follower;
sim_all represents all three subjectivity similarities used in the classifier.
2. All the spelling errors will be corrected in the revision.

Responses to Review 3:
Sentiment of tweets is determined not only by normal words but also by the special characteristics of Twitter languages such as emoticon, capitalized words, repeated letters and exclamation mark, etc. They can not be easily modelled with probabilistic distribution. TSM tries to learn a general word-sentiment distribution to model the sentiment of blogs, which may not work well for tweets. However, rule-based sentiment analysis methods can catch subtle sentiment of tweets by transforming these characteristics to rules. Therefore, we construct our model by combining the results of a LDA topic model and a rule-based sentiment classifier. TSM is a major approach that is closest to our work, we will cite and analysis it in our manuscript. And We will pursue it in the near future to carry out series of experiments to compare it with our method.

### 2014-04-15 response_0322-f.txt
response

We appreciate the detailed comments by the reviewers. Here are our responses:

Responses to Review 1:

1. We agree that the motivation of the research need to be more clearly explained.The motivation of this research is to develop a novel approach to investigate why one diffuses information. Specifically, we adopt the topic model and sentiment analysis techniques in NLP to find latent clues such as topics and opinions from user-generated contents, and use machine learning algorithms to train and predict on the data collected from Twitter. The proposed method can be applied not only to social media, but also to other resources such as user comments to mine the interests and opinions of users. Thus, the work is expected to be impactful or of general interest to the AI community. We will further clarify the motivation more clearly in the revision of the manuscript.
2.For the problems of clarity, We will carefully revise the manuscript to make it clear.

Responses to Review 2:

1.We agree that the explanation of the subjectivity similarity definition need to be revised to make it more clear in the revision. We will fix the problems and clarify some details as indicated by the reviewer.  
Specifically, in (6), theta_m and theta_u are parameters learnt by LDA model representing topic distributions of users m and u;
In (7), d_i is the i^{th} entry of opinion distribution, and v_i denotes corresponding sentiment strength value, in the example of opinion distribution O^2, d_7=1.0, v_7=7;
 (9) is the general definition of subjectivity similarity among tweets, authors and followers, where u and m may represent tweets, or authors, or followers;
In the retweeting analysis paragraph, sim_{sub} with different parameters represent different subjectivity similarity between tweet and author, between tweet and a follower, and between author and a follower;
sim_all represents all three subjectivity similarities used in the classifier.

2. All the spelling errors will be corrected in the revision.

Responses to Review 3:
Sentiment of tweets is determined not only by normal words but also by various special characteristics of Twitter languages such as emoticon, capitalized words, repeated letters and exclamation mark, etc. Those features cannot be easily modeled by a probabilistic distribution. TSM tries to learn a general word-sentiment distribution to model the sentiment of blogs, which may not work well for tweets. However, rule-based sentiment analysis methods can catch some subtle sentiment of tweets by transforming these characteristics into rules. Therefore, we construct our model by combining the results of a LDA topic model and a rule-based sentiment classifier. TSM is a major approach that is closest to our work, we will cite and review it in our revision. And We will pursue it in the near future to carry out series of experiments to compare it with our method.

### 2014-04-15 response_f.txt
response

After carefully considering comments offered by the three reviewers, We want to extend our appreciation for taking the time and effort necessary to provide such insightful guidance.
Responses to the comments of Reviewer #1 
1. [I don't see it as being impactful or of general interest to the AI community.] 
 Response: We apologize for the confusion caused because we haven't state the motivation and significance of our work clearly. In fact, we have investigated the reason why one diffuses information by modelling the subjectivity of a person with state-of-the-art AI researches. Specifically, we adopt topic model and sentiment analysis techniques of NLP to find latent clues such as topics and opinions from user-generated content, and use machine learning algorithms to train and predict on the data collected from Twitter. But the data may not constraint to social media, the model we have proposed can be adapted to other resources which can be used to mine the interests and opinions of users. The comment is very valuable and reminds us to make it more clear in the revision of the paper. 
2. [The clarity of the paper had some problems.]
Response:Thank you very much for such insightful comment and the problems are fixed during the revision of our paper.

Responses to the comments of Reviewer #2 
1.[problems in the section where the subjectivity similarity is presented and defined.]
Response: Thank you for listing all the problems. We have fixed all of them, and answered all the questions about the similarity in the revision.
2.[minor comments for spelling errors]
Response: Thank you for pointing out all the spelling errors, we have corrected all of them.

Responses to the comments of Reviewer #3
[the paper lacks comparison with Topic Sentiment Mixture (TSM) models.]
Response:This is a great point, we have cited TSM model in the related works, which is a very interesting work on topic related sentiment analysis in blogsphere. However, there is some difference between our work and TSM. We will refine our paper to make the comparison more clear as follows. Sentiment analysis of tweets is more complicated than blogs. While TSM try to train a general word-sentiment distribution model to determine the sentiment, sentiment of tweets is determined not only by normal words but also by the special characteristics of Twitter languages such as emoticon, capitalized words，repeated letters and exclamation mark, which can not be easily modeled with probabilistic distribution, but can be modeled by transforming them to rules as Sentistrength has done. So we think that our method can better adapt to Twitter and output more precise sentiment of tweets. Besides, we want to get a more fine-grained sentiment to reflect the subtle opinion similarity, and the TSM model can only give relative coverage of the neurtral, positive, and negative opinions. But it is good suggestion for our future research to construct our model in the way as TSM by combining the characteristics of tweets, and we will compare such a model with TSM model.

### 2014-04-15 response_kw.txt
response

Thank you for your detailed comments. We would like to response to some questions raised in the reviews as follows.

Responses to the comments in Review 1:
We agree that the work could be motivated better. The major challenge tackled in the paper is to diffuse Web information (from Twitter) by modelling the subjectivity of a user with state-of-the-art technologies from natural language processing (NLP). Specifically, we adopt topic model and sentiment analysis techniques in NLP to find latent clues such as topics and opinions from user-generated content, and use machine learning algorithms to train and predict on the data collected from Twitter. But the data may not constraint to social media. Actually, the model we have proposed can be adapted to other data resources and can be used in mining the interests and opinions of users.
We will improve the presentation following your comments.

Responses to the comments in Review 2:
We have fixed all of them, and answered all the questions about the similarity in the revision

Responses to the comments in Review 3:
TSM cited in the paper is a major approach that is closest to our work.
The TSM paper focuses on blogs but sentiment analysis of tweets is more challenging than that of blogs. While TSM try to train a general word-sentiment distribution model to determine the sentiment, sentiment of tweets is determined not only by normal words but also by the special characteristics of Twitter languages such as emoticon, capitalized words, repeated letters and exclamation mark, etc. They can not be easily modelled with probabilistic
distribution, but can be modelled by transforming them to rules as Sentistrength has done. So we think that our method is more suitable for Twitter and can catch more precise sentiment of tweets. Besides, we want to get a more fine-grained sentiment to reflect the subtle opinion similarity, but TSM model can only give relative coverage of neutral, positive, and negative opinions. It is an interesting idea to construct our model in the way as TSM by 
combining the characteristics of tweets, and we will compare such a model with TSM model. We will pursue it in the near future.

wrl：

We appreciate the thorough reviews be the reviewers. Here are our responses:

Responses to the comments of Reviewer #1
1. [I don't see it as being impactful or of general interest to the AI
community.]
Response: Thanks for your comments. The motivation of this research is develop a new AI approach to investigate why one diffuses. Specifically, we adopt the topic model and sentiment analysis techniques in NLP to find latent clues such as topics and opinions from user-generated contents, and use machine learning algorithms to train and predict on the data collected from Twitter. Obviously, this method we have proposed can be applied not only to social media, but also to  other resources such as to mine the interests and opinions of users. These are impactful or of general interest to the AI community. We will further clarify the motivation in the revision of the manuscript.
2. [The clarity of the paper had some problems.]
Response:  We will carefully revise the manuscript to make it clear.
Responses to the comments of Reviewer #2
1.[problems in the section where the subjectivity similarity is
presented and defined.]
Response:We have fixed all the problems listed by the reviewer about the similarity in the revision.
2.[minor comments for spelling errors]
Response: Thank you for pointing out all the spelling errors, which will be corrected in the revision.
Responses to the comments of Reviewer #3
[the paper lacks comparison with Topic Sentiment Mixture (TSM) models.]
Response: This is a great point, we have cited TSM model in the related
works, which is a very interesting work on topic related sentiment
analysis in blogsphere. However, there is some difference between our
work and TSM. We will refine our paper to make the comparison more clear
as follows. Sentiment analysis of tweets is more complicated than blogs.
While TSM trie to train a general word-sentiment distribution model to
determine the sentiment, sentiment of tweets is determined not only by
normal words but also by the special characteristics of Twitter
languages such as emoticon, capitalized words, repeated letters and
exclamation mark, which can not be easily modeled with a probabilistic
distribution, but can be modeled by transforming them to rules as
Sentistrength has done. Thus,we think that our method can better adapt to
Twitter and output more precise sentiment of tweets. Besides, we want to
get a more fine-grained sentiment to reflect the subtle opinion
similarity, and the TSM model can only give relative coverage of the
neutral, positive, and negative opinions. But it is good suggestion for
our future research to construct our model in the way as TSM by
combining the characteristics of tweets, and we will compare such a
model with TSM model.
